---
title: "Create Defense Services Dataset"
author: "Greg Sanders"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, July 11, 2019"

---



```{r setup}
#*************************************Required Libraries******************************************
require(dplyr)
require(grid)
require(reshape2)
require(stringr)
require(ggplot2)
library(Hmisc)
library(readr)
library(csis360)
library(arm)
library(reshape2)
library(tidyverse)


#*************************************Options*****************************************************
options(error=recover)
options(warn=1)

#*************************************Lookup Files*****************************************************

source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")
source("https://raw.githubusercontent.com/CSISdefense/Crisis-Funding/master/Scripts/ContractCleanup.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/lookups.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/helper.r")

```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..




First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


## Data Transformations and Summary
```{r Prune}

load(file="../data/clean/defense_contract_complete.RData")


def_serv<-def %>% filter(PSR %in% c("Services"))
def_serv<-def_serv[def_serv$MinOfSignedDate>=as.Date("2008-01-01") & def_serv$MinOfSignedDate<=as.Date("2015-12-31"),]
rm(def)
def_serv<-transition_variable_names_service(def_serv)

#   


# summary(def_serv$UnmodifiedContractBaseAndAllOptionsValue)
# def_serv$UnmodifiedContractBaseAndAllOptionsValue[def_serv$override_unmodified_ceiling==TRUE]<-NA
# summary(def_serv$UnmodifiedContractBaseAndExercisedOptionsValue)
# def_serv$UnmodifiedContractBaseAndExercisedOptionsValue[def_serv$override_unmodified_base==TRUE]<-NA
# summary(def_serv$ChangeOrderBaseAndAllOptionsValue)
# summary(def_serv$ChangeOrderCeilingGrowth)
# def_serv$ChangeOrderBaseAndAllOptionsValue[def_serv$override_change_order_growth==TRUE]<-NA
# def_serv$ChangeOrderCeilingGrowth[def_serv$override_change_order_growth==TRUE]<-NA
save(def_serv,file="../data/clean/defense_services_complete.RData")
```

### Base 
```{r Base}
load(file="../data/clean/defense_services_complete.RData")
    def_serv  <-read_and_join_experiment( def_serv  ,
                                        "Contract.sp_ContractExercisedOptions.txt",
                                        path="",
                                        directory="..\\data\\semi_clean\\",
                                        by=c("CSIScontractID"),
                                        # add_var=c("AnyUnmodifiedUnexercisedOptions",
                                        #           "AnyUnmodifiedUnexercisedOptionsWhy",
                                        #           "UnmodifiedBase",
                                        #           "SteadyScopeOptionGrowthAlone",
                                        #           "SteadyScopeOptionRescision",
                                        #           "AdminOptionModification"),
                                        new_var_checked=FALSE,
                                        create_lookup_rdata=TRUE,
                                        lookup_char_as_factor=TRUE)
  

colnames(def_serv)[colnames(def_serv)=="SteadyScopeOptionRescinded"]<-"SteadyScopeOptionRescision"
colnames(def_serv)[colnames(def_serv)=="ln_base"]<-"l_Base"


  sumcheck<-abs(def_serv$UnmodifiedBase+
  def_serv$ChangeOrderOptionModification+
  def_serv$SteadyScopeOptionGrowthAlone+
    def_serv$SteadyScopeOptionGrowthMixed+
    def_serv$SteadyScopeOptionRescision+
    def_serv$AdminOptionModification+
    def_serv$EndingOptionModification+
    def_serv$OtherOptionModification-
    ifelse(is.na(def_serv$SumOfbaseandexercisedoptionsvalue),
           0,def_serv$SumOfbaseandexercisedoptionsvalue))>1

if(any(sumcheck==TRUE)){
  write.csv(file="..\\output\\exercised_options_sumcheck_failures.csv",
    def_serv[sumcheck,] %>% dplyr::select(CSIScontractID,
                               UnmodifiedBase,
                               ChangeOrderOptionModification,
                               SteadyScopeOptionGrowthAlone,
                               SteadyScopeOptionGrowthMixed,
                               SteadyScopeOptionRescision,
                               AdminOptionModification,
                               EndingOptionModification,
                               OtherOptionModification,
                               SumOfbaseandexercisedoptionsvalue)
  )
  if(any(sumcheck&def_serv$UnmodifiedBase>0))
    stop("Exercised Option Checksum failure.")
  else warning("Checksum failure for entries with na unmodified")
}
rm(sumcheck)

def_serv$n_OptGrowth <- def_serv$SteadyScopeOptionGrowthAlone +
  ifelse(def_serv$SteadyScopeOptionRescision+def_serv$SteadyScopeOptionGrowthMixed+def_serv$AdminOptionModification<0,
         def_serv$SteadyScopeOptionRescision+def_serv$SteadyScopeOptionGrowthMixed+def_serv$AdminOptionModification,0)+1
def_serv$n_OptGrowth[def_serv$n_OptGrowth<=1 & def_serv$SteadyScopeOptionGrowthAlone>0]<-NA
def_serv$n_OptGrowth[def_serv$SteadyScopeOptionGrowthAlone==0]<-1
summary(def_serv$n_OptGrowth)
save(def_serv,file="../data/clean/defense_services_complete.RData")

```


### Entity

```{r Entity}
load(file="../data/clean/defense_services_complete.RData")

# #****This should be in dataset building, not transform.
    def_serv<-read_and_join_experiment( def_serv,
                                                   "Contract.sp_ContractEntityID.txt",
                                                   path="",
                                                   directory="..\\data\\semi_clean\\",
                                                   by=c("CSIScontractID"),
                                                   add_var=c("EntityID","UnmodifiedEntityID"),
                                                   new_var_checked=FALSE,
                                        create_lookup_rdata=TRUE)
    def_serv$EntityID[is.na(def_serv$EntityID)]<-
      def_serv$UnmodifiedEntityID[is.na(def_serv$EntityID)]
  save(def_serv,file="../data/clean/defense_services_complete.RData")
```



### Crisis
```{r Crisis}    
load(file="../data/clean/defense_services_complete.RData")
load("..\\data\\clean\\fed_transformed.rdata")
fed <- fed %>% group_by() %>% dplyr::select(CSIScontractID,Crisis)
def_serv<-left_join(def_serv,fed,by="CSIScontractID")
summary(factor(def_serv$Crisis))
rm(fed)
#About 25.4k inexplicably missing
# summary(def_serv[is.na(def_serv$Crisis),])
# 
# debug(transform_contract)
# # head(def_serv)
save(def_serv,file="../data/clean/defense_services_complete.RData")
```


### Transform
```{r Transform}
load(file="../data/clean/defense_services_complete.RData")
debug(transform_contract)
def_serv<-transform_contract(def_serv)
#
#
discrete_percent_plot(def_serv,"CBre")
discrete_percent_plot(def_serv,"Term")
# 
# 
# 
# summary(def_serv$Unmodifieddef_servBaseAndAllOptionsValue)
# summary(def_serv$Action.Obligation)
# 

save(file="../data/clean/transformed_def_serv.Rdata",def_serv)
```
   
Should be transferred into transform contract at some point

### Exercised Options

#### Option Outcome

 
```{r OptOutcome}}

    
load(file="../data/clean/transformed_def_serv.Rdata")



#Need to pull in ceiling breach again to get the variants. Ideally we move this over to vendor at some point.
  colnames(def_serv)[colnames(def_serv)=="UnmodifiedCeiling_Then_Year"]<-"UnmodifiedCeiling"
 #Ceiling Variables
  def_serv<-input_contract_ceiling_breach(def_serv,
                                          file="Contract.SP_ContractCeilingBreachCustomer.txt")
  colnames(def_serv)[colnames(def_serv)=="UnmodifiedCeiling"]<-"UnmodifiedCeiling_Then_Year"
  
  
  

  #Determine original and updated space available 
def_serv$OptSpaceOriginal<-def_serv$UnmodifiedCeiling_Then_Year-def_serv$UnmodifiedBase_Then_Year
summary(def_serv$OptSpaceOriginal)

def_serv$OptSpaceUpdated<-def_serv$UnmodifiedCeiling_Then_Year+def_serv$ChangeOrderCeilingGrowth+
  def_serv$AdminCeilingModification+def_serv$SteadyScopeCeilingModification+def_serv$OtherCeilingModification-
  def_serv$UnmodifiedBase_Then_Year
summary(def_serv$OptSpaceUpdated)
#Not included in the update ceiling.
#ChangeOrderCeilingRescision
#EndingCeilingModification+
#OtherCeilingModification+

def_serv$OptSpaceUpdated[def_serv$OptSpaceOriginal>def_serv$OptSpaceUpdated  &
                           !is.na(def_serv$OptSpaceOriginal) & !is.na(def_serv$OptSpaceUpdated )] <-
  def_serv$OptSpaceOriginal[def_serv$OptSpaceOriginal>def_serv$OptSpaceUpdated  &
                           !is.na(def_serv$OptSpaceOriginal) & !is.na(def_serv$OptSpaceUpdated )]

#Proportion of options
def_serv$ExerOriginal<-(def_serv$n_OptGrowth_Then_Year-1)/def_serv$OptSpaceOriginal
def_serv$ExerOriginal[def_serv$ExerOriginal>1]<-1
def_serv$ExerOriginal[def_serv$AnyUnmodifiedUnexercisedOptions==0]<-NA
summary(def_serv$ExerOriginal)

def_serv$ExerUpdate<-(def_serv$ChangeOrderOptionModification+
                        def_serv$SteadyScopeOptionGrowthAlone+
                        def_serv$SteadyScopeOptionGrowthMixed+
                        def_serv$SteadyScopeOptionRescision+
                        def_serv$AdminOptionModification+
                        def_serv$OtherOptionModification
                      )/def_serv$OptSpaceUpdated
def_serv$ExerUpdate[def_serv$ExerUpdate>1]<-1
def_serv$ExerUpdate[def_serv$ExerUpdate<0]<-0
def_serv$ExerUpdate[def_serv$AnyUnmodifiedUnexercisedOptions==0]<-NA
summary(def_serv$ExerUpdate)

#Excludes def_serv$EndingOptionModification+
    
def_serv$Exer<-ifelse(def_serv$ExerUpdate>def_serv$ExerOriginal,def_serv$ExerUpdate,def_serv$ExerOriginal)
summary(def_serv$Exer)



if(any(duplicated(names(def_serv)))) stop("Duplicate names in def_serv")
save(file="../data/clean/transformed_def_serv.Rdata",def_serv)

```

#### Option Alternate

```{r AlternateSomeCriteria}
load(file="../data/clean/transformed_def_serv.Rdata")
def_serv$b_AllOpt<-ifelse(def_serv$Exer>0.95,1,0)
summary(def_serv$b_AllOpt)

def_serv$b_SomeOpt_Strict<-ifelse(def_serv$n_OptGrowth_Then_Year>1,1,0)
def_serv$b_SomeOpt_Strict[def_serv$AnyUnmodifiedUnexercisedOptions==0]<-NA
def_serv$CeilGrowth<-def_serv$OptSpaceUpdated-def_serv$OptSpaceOriginal
def_serv$b_SomeOpt<-def_serv$b_SomeOpt_Strict
def_serv$b_SomeOpt[def_serv$ChangeOrderOptionModification+
                        def_serv$SteadyScopeOptionGrowthAlone+
                        def_serv$SteadyScopeOptionGrowthMixed+
                        def_serv$SteadyScopeOptionRescision+
                        def_serv$AdminOptionModification+
                        def_serv$OtherOptionModification>def_serv$CeilGrowth]<-1
summary(def_serv$b_SomeOpt)
summary(def_serv$b_SomeOpt_Strict)

if(any(def_serv$b_SomeOpt==0 & def_serv$Exer>=1))
   warning("Somehow a contract that does not meet the some criteria has reach 100% exercised.")
def_serv$b_AllOpt[def_serv$b_SomeOpt==0]<-0
summary(def_serv$b_AllOpt)

def_serv$OptExer<-factor(NA, levels=c(
        "Initial Base=Ceiling","Not Some Options","Some Options","Some and All Options"
      ))
def_serv$OptExer[(def_serv$AnyUnmodifiedUnexercisedOptions==1)& def_serv$b_SomeOpt==0]<-"Not Some Options"
      def_serv$OptExer[def_serv$AnyUnmodifiedUnexercisedOptions==1& def_serv$b_SomeOpt==1]<-"Some Options"
      def_serv$OptExer[def_serv$AnyUnmodifiedUnexercisedOptions==1&
                     def_serv$b_SomeOpt==1 & def_serv$b_AllOpt==1]<-"Some and All Options"
      def_serv$OptExer[def_serv$AnyUnmodifiedUnexercisedOptions==0]<-"Initial Base=Ceiling"
      def_serv$OptExer[def_serv$UnmodifiedBase_Then_Year>def_serv$UnmodifiedCeiling_Then_Year]<-NA
      


summary(def_serv$Opt)      
summary(def_serv$OptExer)

if(any(duplicated(names(def_serv)))) stop("Duplicate names in def_serv")
save(file="../data/clean/transformed_def_serv.Rdata",def_serv)
```

### Calendar Year Deflating
```{r CalendarYearDeflating}
load(file="../data/clean/transformed_def_serv.Rdata")

cal_deflator<-remove_bom(read.csv("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/economic/Lookup_Calendar_Deflator.csv"))
cal_deflator<-cal_deflator %>% dplyr::select(Calendar_Year,BEA18)


#Average salary
def_serv$CensusYear<-factor(def_serv$StartCY)
summary(def_serv$CensusYear)
levels(def_serv$CensusYear)<-list("2007"=c("2008","2009","2010","2011","2012"),
                                 "2012"=c("2013","2014","2015","2016","2017"))
def_serv$CensusYear<-as.numeric(as.character(def_serv$CensusYear))

if("BEA18" %in% colnames(def_serv)) def_serv <- def_serv  %>% dplyr::select(-BEA18)
def_serv<-dplyr::left_join(def_serv, cal_deflator,
          by=c("CensusYear"="Calendar_Year"))
def_serv$US6_avg_sal_lag1Const<-def_serv$US6_avg_sal_lag1/def_serv$BEA18


def_serv$l_US6_avg_sal_lag1Const<-na_non_positive_log(def_serv$US6_avg_sal_lag1Const)
      def_serv$cln_US6sal<-arm::rescale(def_serv$l_US6_avg_sal_lag1Const)

def_serv <- def_serv  %>% dplyr::select(-BEA18,CensusYear)
colnames(def_serv)[colnames(def_serv)=="US6_avg_sal_lag1"]<-"US6_avg_sal_lag1_then_year"
colnames(def_serv)[colnames(def_serv)=="cl_US6_avg_sal_lag1"]<-"cl_US6_avg_sal_lag1_then_year"


#def6_obl_lag1Const
def_serv<-dplyr::left_join(def_serv, cal_deflator,
          by=c("StartCY"="Calendar_Year"))

def_serv$def6_obl_lag1Const<-def_serv$def6_obl_lag1/def_serv$BEA18
def_serv <- def_serv  %>% dplyr::select(-BEA18)
def_serv$l_def6_obl_lag1Const<-na_non_positive_log(def_serv$def6_obl_lag1Const)
      def_serv$cl_def6_obl_lag1Const<-arm::rescale(def_serv$l_def6_obl_lag1Const)

colnames(def_serv)[colnames(def_serv)=="def6_obl_lag1"]<-"def6_obl_lag1_then_year"
colnames(def_serv)[colnames(def_serv)=="cl_def6_obl_lag1"]<-"cl_def6_obl_lag1_then_year"
#Removing l_s just to reduce size. They can be derived easily.

# def_serv<-def_serv[!colnames(def_serv) %in% colnames(def_serv)[grep("^l_",colnames(def_serv))]]

if(any(duplicated(names(def_serv)))) stop("Duplicate names in def_serv")
save(file="../data/clean/transformed_def_serv.Rdata",def_serv)
```

### Office Diversity NAICS 
```{r OfficeDiversityNAICS}

load(file="../data/clean/transformed_def_serv.Rdata")

length(unique((def_serv$Office)))
length(unique((def_serv$Agency)))
length(unique((def_serv$NAICS)))
length(unique((def_serv$NAICS3)))





#********** NAICS - Office hhi
if(!"office_naics_hhi_k" %in% colnames(def_serv)){
  annual_office_naics_hhi <- read.csv("..//data//clean//annual_office_naics_hhi.csv",
                                      header = TRUE, row.names = "X") %>% 
    dplyr::select(-c("obligatedAmount","numberOfContracts"))
  
  #Pulling in join annual_office_naics_hhi
  def_serv <- def_serv %>%
    mutate("StartFY_lag1" = StartFY - 1) %>%
    left_join(annual_office_naics_hhi, by = c("Office" = "ContractingOfficeCode", "StartFY_lag1" = "Fiscal_year")) %>%
    dplyr::select(-c("StartFY_lag1"))
  rm(annual_office_naics_hhi)
  
  #Pulling in join avg_office_naics_hhi
  avg_office_naics_hhi <- read.csv("..//data//clean//average_office_naics_hhi.csv", header = TRUE, row.names = "X") %>% 
    dplyr::select(-c("obligatedAmount","numberOfContracts"))
  def_serv <- def_serv %>%
    left_join(avg_office_naics_hhi, by = c("Office" = "ContractingOfficeCode"))
  rm(avg_office_naics_hhi)
  
  #Imputing missing
    summary(def_serv$office_naics_hhi_obl)
  def_serv$office_naics_hhi_obl[is.na(def_serv$office_naics_hhi_obl)]<-def_serv$avg_office_naics_hhi_obl[is.na(def_serv$office_naics_hhi_obl)]
  summary(def_serv$office_naics_hhi_k)
  def_serv$office_naics_hhi_k[is.na(def_serv$office_naics_hhi_k)]<-def_serv$avg_office_naics_hhi_k[is.na(def_serv$office_naics_hhi_k)]
  
  def_serv$cl_office_naics_hhi_obl <- arm::rescale(na_non_positive_log(def_serv$office_naics_hhi_obl))
  def_serv$cln_OffFocus <- arm::rescale(na_non_positive_log(def_serv$office_naics_hhi_k))
  def_serv<- def_serv %>% dplyr::select(-c(avg_office_naics_hhi_obl,avg_office_naics_hhi_k))
}


#********8 Invoice rate  for PSC
# def_serv$l_CFTE<-log(def_serv$CFTE_Rate_1year)

if(any(duplicated(names(def_serv)))) stop("Duplicate names in def_serv")
save(file="../data/clean/transformed_def_serv.Rdata",def_serv)



```