---
title: "Create Defense Services Dataset"
author: "Greg Sanders"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, July 11, 2019"
---



```{r setup}
#*************************************Required Libraries******************************************
require(dplyr)
require(grid)
require(reshape2)
require(stringr)
require(ggplot2)
library(Hmisc)
library(readr)
library(csis360)
library(arm)
library(reshape2)
library(tidyverse)


#*************************************Options*****************************************************
options(error=recover)
options(warn=1)

#*************************************Lookup Files*****************************************************

Path<-"https://github.com/CSISdefense/R-scripts-and-data/blob/master/"
# Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"~\\FPDS\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")
source("https://raw.githubusercontent.com/CSISdefense/Crisis-Funding/master/Scripts/ContractCleanup.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/lookups.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/helper.r")

```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..




First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


## Data Transformations and Summary
```{r Prune}

load(file="../data/clean/defense_contract_complete.RData")



def_serv<-def %>% filter(PSR %in% c("Services"))
def_serv<-def_serv[def_serv$MinOfSignedDate>=as.Date("2008-01-01") & def_serv$MinOfSignedDate<=as.Date("2015-12-31"),]
rm(def)
#   


# summary(def_serv$UnmodifiedContractBaseAndAllOptionsValue)
# def_serv$UnmodifiedContractBaseAndAllOptionsValue[def_serv$override_unmodified_ceiling==TRUE]<-NA
# summary(def_serv$UnmodifiedContractBaseAndExercisedOptionsValue)
# def_serv$UnmodifiedContractBaseAndExercisedOptionsValue[def_serv$override_unmodified_base==TRUE]<-NA
# summary(def_serv$ChangeOrderBaseAndAllOptionsValue)
# summary(def_serv$ChangeOrderCeilingGrowth)
# def_serv$ChangeOrderBaseAndAllOptionsValue[def_serv$override_change_order_growth==TRUE]<-NA
# def_serv$ChangeOrderCeilingGrowth[def_serv$override_change_order_growth==TRUE]<-NA
save(def_serv,file="../data/clean/defense_services_complete.RData")
```

### Base 
```{r Base}
load(file="../data/clean/defense_services_complete.RData")
    def_serv  <-read_and_join_experiment( def_serv  ,
                                        "Contract.sp_ContractExercisedOptions.txt",
                                        path="",
                                        directory="..\\data\\semi_clean\\",
                                        by=c("CSIScontractID"),
                                        # add_var=c("AnyUnmodifiedUnexercisedOptions",
                                        #           "AnyUnmodifiedUnexercisedOptionsWhy",
                                        #           "UnmodifiedBase",
                                        #           "SteadyScopeOptionGrowthAlone",
                                        #           "SteadyScopeOptionRescision",
                                        #           "AdminOptionModification"),
                                        new_var_checked=FALSE,
                                        create_lookup_rdata=TRUE,
                                        lookup_char_as_factor=TRUE)
  

colnames(def_serv)[gitcolnames(def_serv)=="SteadyScopeOptionRescinded"]<-"SteadyScopeOptionRescision"


  sumcheck<-abs(def_serv$UnmodifiedBase+
  def_serv$ChangeOrderOptionModification+
  def_serv$SteadyScopeOptionGrowthAlone+
    def_serv$SteadyScopeOptionGrowthMixed+
    def_serv$SteadyScopeOptionRescision+
    def_serv$AdminOptionModification+
    def_serv$EndingOptionModification+
    def_serv$OtherOptionModification-
    ifelse(is.na(def_serv$SumOfbaseandexercisedoptionsvalue),
           0,def_serv$SumOfbaseandexercisedoptionsvalue))>1

if(any(sumcheck==TRUE)){
  write.csv(file="..\\output\\exercised_options_sumcheck_failures.csv",
    def_serv[sumcheck,] %>% dplyr::select(CSIScontractID,
                               UnmodifiedBase,
                               ChangeOrderOptionModification,
                               SteadyScopeOptionGrowthAlone,
                               SteadyScopeOptionGrowthMixed,
                               SteadyScopeOptionRescision,
                               AdminOptionModification,
                               EndingOptionModification,
                               OtherOptionModification,
                               SumOfbaseandexercisedoptionsvalue)
  )
  if(any(sumcheck&def_serv$UnmodifiedBase>0))
    stop("Ceiling Modification Checksum failure.")
  else warning("Checksum failure for entries with na unmodified")
}
rm(sumcheck)

def_serv$n_OptGrowth <- def_serv$SteadyScopeOptionGrowthAlone +
  ifelse(def_serv$SteadyScopeOptionRescision+def_serv$SteadyScopeOptionGrowthMixed+def_serv$AdminOptionModification<0,
         def_serv$SteadyScopeOptionRescision+def_serv$SteadyScopeOptionGrowthMixed+def_serv$AdminOptionModification,0)+1
def_serv$n_OptGrowth[def_serv$n_OptGrowth<=1 & def_serv$SteadyScopeOptionGrowthAlone>0]<-NA
def_serv$n_OptGrowth[def_serv$SteadyScopeOptionGrowthAlone==0]<-1
summary(def_serv$n_OptGrowth)
save(def_serv,file="../data/clean/defense_services_complete.RData")

```


### Entity

```{r Entity}
load(file="../data/clean/defense_services_complete.RData")

# #****This should be in dataset building, not transform.
    def_serv<-read_and_join_experiment( def_serv,
                                                   "Contract.sp_ContractEntityID.txt",
                                                   path="",
                                                   directory="..\\data\\semi_clean\\",
                                                   by=c("CSIScontractID"),
                                                   add_var=c("EntityID","UnmodifiedEntityID"),
                                                   new_var_checked=FALSE,
                                        create_lookup_rdata=TRUE)
    def_serv$EntityID[is.na(def_serv$EntityID)]<-
      def_serv$UnmodifiedEntityID[is.na(def_serv$EntityID)]
  save(def_serv,file="../data/clean/defense_services_complete.RData")
```



### Crisis
```{r Crisis}    
load(file="../data/clean/defense_services_complete.RData")
load("..\\data\\clean\\fed_transformed.rdata")
fed <- fed %>% group_by() %>% dplyr::select(CSIScontractID,Crisis)
def_serv<-left_join(def_serv,fed,by="CSIScontractID")
summary(factor(def_serv$Crisis))
rm(fed)
#About 25.4k inexplicably missing
# summary(def_serv[is.na(def_serv$Crisis),])
# 
# debug(transform_contract)
# # head(def_serv)
save(def_serv,file="../data/clean/defense_services_complete.RData")
```


### Transform
```{r Transform}
load(file="../data/clean/defense_services_complete.RData")
def_serv<-transform_contract(def_serv)
#
#
discrete_percent_plot(def_serv,"CBre")
discrete_percent_plot(def_serv,"Term")
# 
  summary_discrete_plot(def_serv,"Level1_Category")
# 
# 
# summary(def_serv$Unmodifieddef_servBaseAndAllOptionsValue)
# summary(def_serv$Action.Obligation)
# 
save(file="../data/clean/transformed_def_serv.Rdata",def_serv)
```
   
Should be transferred into transform contract at some point


### Office Diversity NAICS 
```{r UnnecessaryNAICS}
load(file="../data/clean/transformed_def_serv.Rdata")
cal_deflator<-remove_bom(read.csv("https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/economic/Lookup_Calendar_Deflator.csv"))

#Average salary
def_serv$CensusYear<-factor(def_serv$StartCY)
summary(def_serv$CensusYear)
levels(def_serv$CensusYear)<-list("2007"=c("2008","2009","2010","2011","2012"),
                                 "2012"=c("2013","2014","2015","2016","2017"))
def_serv$CensusYear<-as.numeric(as.character(def_serv$CensusYear))
cal_deflator<-cal_deflator %>% dplyr::select(Calendar_Year,BEA18)

def_serv<-dplyr::left_join(def_serv, cal_deflator,
          by=c("CensusYear"="Calendar_Year"))
colnames(def_serv)
def_serv$US6_avg_sal_lag1Const<-def_serv$US6_avg_sal_lag1/def_serv$BEA18


def_serv$l_US6_avg_sal_lag1Const<-na_non_positive_log(def_serv$US6_avg_sal_lag1Const)
      def_serv$cl_US6_avg_sal_lag1Const<-arm::rescale(def_serv$l_US6_avg_sal_lag1Const)

def_serv <- def_serv  %>% dplyr::select(-BEA18)
colnames(def_serv[colnames(def_serv)=="US6_avg_sal_lag1"])<-"US6_avg_sal_lag1_then_year"
colnames(def_serv[colnames(def_serv)=="cl_US6_avg_sal_lag1"])<-"cl_US6_avg_sal_lag1_then_year"
#def6_obl_lag1Const
def_serv<-dplyr::left_join(def_serv, cal_deflator,
          by=c("StartCY"="Calendar_Year"))
summary(def_serv$BEA18)

def_serv$def6_obl_lag1Const<-def_serv$def6_obl_lag1/def_serv$BEA18
def_serv <- def_serv  %>% dplyr::select(-BEA18)
def_serv$l_def6_obl_lag1Const<-na_non_positive_log(def_serv$def6_obl_lag1Const)
      def_serv$cl_def6_obl_lag1Const<-arm::rescale(def_serv$l_def6_obl_lag1Const)

colnames(def_serv[colnames(def_serv)=="def6_obl_lag1"])<-"def6_obl_lag1_then_year"
colnames(def_serv[colnames(def_serv)=="cl_def6_obl_lag1"])<-"cl_def6_obl_lag1_then_year"
#Removing l_s just to reduce size. They can be derived easily.

# def_serv<-def_serv[!colnames(def_serv) %in% colnames(def_serv)[grep("^l_",colnames(def_serv))]]


#********************Still not done***************************
#Def NAICS size
#Salary
#Both require calendar year deflators

# summary(def_serv$Action.Obligation)
# def_serv<-deflate(def_serv,
#                    money_var = "Action.Obligation",
#                    deflator_var="OMB.2019",
#                   fy_var="StartFY",
#                  path="C:/Users/gsand/Repositories/Lookup-Tables/"
# )
# def_serv<-deflate(def_serv,
#                    money_var = "Ceil",
#                    deflator_var="OMB.2019",
#                   fy_var="StartFY",
#                  path="C:/Users/gsand/Repositories/Lookup-Tables/"
# )
# def_serv$l_Ceil<-na_non_positive_log(def_serv$Ceil.OMB.2019)
# def_serv$cl_Ceil<-arm::rescale(def_serv$l_Ceil)


# def_serv<-def_serv[def_serv$PSR %in% c("Services"),]
# summary(factor(def_serv$OCO_GF))
# colnames(def_serv)[colnames(def_serv)=="Office"]<-"ContractingOfficeCode"
# 
# colnames(def_serv)[colnames(def_serv)=="StartFY"]<-"fiscal_year"
# def_serv<-read_and_join_experiment( def_serv,
#                                     "Office.sp_OfficeHistoryCapacityLaggedConst.txt",
#                                     path="",
#                                     directory="..\\data\\semi_clean\\",
#                                     by=c("ContractingOfficeCode","fiscal_year"),
#                                     add_var=c("office_obligatedamount_1year",
#                                               "office_numberofactions_1year",
#                                               "office_PBSCobligated_1year",
#                                               "office_obligatedamount_7year"),
#                                     new_var_checked=FALSE)
# def_serv<-read_and_join_experiment( def_serv,
#                                           "Office.sp_ProdServOfficeHistoryLaggedConst.txt",
#                                           path="",
#                                           directory="..\\data\\semi_clean\\",
#                                           by=c("ContractingOfficeCode","fiscal_year","ProductOrServiceCode"),
#                                           add_var=c("office_psc_obligatedamount_7year"),
#                                           new_var_checked=FALSE,
#                                     col_types="ccddddc")
# def_serv<-read_and_join_experiment( def_serv,
#                                           "Office.sp_EntityIDofficeHistoryLaggedConst.txt",
#                                           path="",
#                                           directory="..\\data\\semi_clean\\",
#                                           by=c("EntityID","ContractingOfficeCode","fiscal_year"),
#                                           add_var=c("office_entity_paircount_7year","office_entity_numberofactions_1year",
#                                                     "office_entity_obligatedamount_7year"),
#                                           new_var_checked=FALSE)
# def_serv<-read_and_join( def_serv,
#                            "ProductOrServiceCode.ProdServHistoryCFTEcoalesceLaggedConst.txt",
#                            path="",
#                            directory="..\\data\\semi_clean\\",
#                            by=c("fiscal_year","OCO_GF","ProductOrServiceCode"),
#                            add_var=c("CFTE_Rate_1year"),
#                            new_var_checked=FALSE)
#   colnames(def_serv)[colnames(def_serv)=="fiscal_year"]<-"StartFY"
# colnames(def_serv)[colnames(def_serv)=="ContractingOfficeCode"]<-"Office"





# deflate <- function(
#   data,
#   money_var = "Amount",
#   fy_var = "Fiscal_Year",
#   deflator_file = "Lookup_Deflators.csv",
#   deflator_var="OMB20_GDP18",
#   path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
#   directory="economic/",
#   deflator_dropped=TRUE
# )



length(unique((def_serv$ContractingOfficeCode)))
length(unique((def_serv$Agency)))
length(unique((def_serv$NAICS)))
length(unique((def_serv$NAICS3)))





#********** NAICS - Office hhi
annual_office_naics_hhi <- read.csv("..//data//clean//annual_office_naics_hhi.csv", header = TRUE, row.names = "X") %>% 
  dplyr::select(-c("obligatedAmount","numberOfContracts"))

#Pulling in join annual_office_naics_hhi
def_serv <- def_serv %>%
  mutate("StartFY_lag1" = StartFY - 1) %>%
  left_join(annual_office_naics_hhi, by = c("Office" = "ContractingOfficeCode", "StartFY_lag1" = "Fiscal_year")) %>%
  dplyr::select(-c("StartFY_lag1"))
rm(annual_office_naics_hhi)

#Pulling in join avg_office_naics_hhi
avg_office_naics_hhi <- read.csv("..//data//clean//average_office_naics_hhi.csv", header = TRUE, row.names = "X") %>% 
  dplyr::select(-c("obligatedAmount","numberOfContracts"))
def_serv <- def_serv %>%
  left_join(avg_office_naics_hhi, by = c("Office" = "ContractingOfficeCode"))
rm(avg_office_naics_hhi)

#Imputing missing
summary(def_serv$office_naics_hhi_obl)
def_serv$office_naics_hhi_obl[is.na(def_serv$office_naics_hhi_obl)]<-def_serv$avg_office_naics_hhi_obl[is.na(def_serv$office_naics_hhi_obl)]
summary(def_serv$office_naics_hhi_k)
def_serv$office_naics_hhi_k[is.na(def_serv$office_naics_hhi_k)]<-def_serv$avg_office_naics_hhi_k[is.na(def_serv$office_naics_hhi_k)]

def_serv$cl_office_naics_hhi_obl <- arm::rescale(na_non_positive_log(def_serv$office_naics_hhi_obl))
def_serv$cl_office_naics_hhi_k <- arm::rescale(na_non_positive_log(def_serv$office_naics_hhi_k))
def_serv<- def_serv %>% dplyr::select(-c(avg_office_naics_hhi_obl,avg_office_naics_hhi_k))



#********** Performance Based Services Contracting
# def_serv$l_pPBSC<-log(def_serv$pPBSC+1)

#********** Office experience in PSC
# def_serv$l_pOffPSC<-log(def_serv$pOffPSC+1)

#********** Vendor Market Share
# def_serv$l_pMarket<-log(def_serv$pMarket+1)



#********* Number of actions between vendor and office
# def_serv$l_CA<-log(def_serv$office_entity_numberofactions_1year+1)

#********8 Invoice rate  for PSC
# def_serv$l_CFTE<-log(def_serv$CFTE_Rate_1year)

save(file="../data/clean/transformed_def_serv.Rdata",def_serv)
```