---
title: "empty_model_multilevel_check"
author: "Greg Sanders"
date: "August 15, 2018"
output: html_document
---


# Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(Hmisc)
library(sjstats)
library(optimx)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/DIIGstat.r")
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/NAICS.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

## Load in data
```{r Sample}
 load(file="..//data//clean//def_sample.Rdata")
# save(serv_smp,smp1m,file="../data//def_sample.Rdata")



# complete<-!is.na(def$b_Term)&
#   !is.na(def$b_CBre)&
#   !is.na(def$n_Comp)&
#   !is.na(def$l_Ceil)&
#   !is.na(def$l_Days)&
#   !is.na(def$Veh) &
#   !is.na(def$n_Fixed)&
#   !is.na(def$b_Intl)&
#   !is.na(def$b_UCA)&
#   !is.na(def$NAICS)&
#   !is.na(def$NAICS2)&
#   !is.na(def$cl_def6_HHI_lag1)&
#   !is.na(def$US6_avg_sal_lag1)
# # 
# serv_smp<-def[complete,]
# #8818392  to 8818392
# 13057769 to 8335209
# nrow(def[!complete,])/nrow(def)
# sum(def[!complete,]$Action.Obligation,na.rm=TRUE)/sum(def$Action.Obligation,na.rm=TRUE)
# 
# smp1m<-serv_smp[sample(nrow(serv_smp),1000000),]
# serv_smp<-serv_smp[sample(nrow(serv_smp),250000),]
# save(file="data//def_sample.Rdata",serv_smp,smp1m)

# levels(serv_smp$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))
# levels(smp1m$Intl)<- list("Just U.S."=c("Just U.S."), 
#                                 "Any Intl."=c("Any International"))


```

#ICC Testing
## NAICS
### NAICS level 6
```{r NAICSlevel6}
load(file="..//data//clean//naics_empty_models.rdata")

if(!exists("naics06_term"))
naics06_term <- glmer(data=serv_smp,
                 b_Term ~ (1 | NAICS)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_term)

if(!exists("naics06_cbre"))
naics06_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | NAICS)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,naics06_cbre)

if(!exists("naics06_opt"))
naics06_opt <- lmer(data=serv_opt,
                 l_OptGrowth ~ (1 | NAICS)
                  )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,naics06_opt)

```

### NAICS level 3
```{r NAICSlevel3}

if(!exists("naics03_term"))
  naics03_term <- glmer(data=serv_smp,
                        b_Term ~ (1 | NAICS3)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics03_term)

if(!exists("naics03_cbre"))
  naics03_cbre <- glmer(data=serv_smp,
                        b_CBre ~ (1 | NAICS3)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics03_cbre)

if(!exists("naics03_opt"))
  naics03_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | NAICS3)
                        )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,naics03_opt)
```


### NAICS 3/6
```{r NAICSlevel36}

if(!exists("naics36_term"))
  naics36_term <- glmer(data=serv_smp,
                        b_Term ~ (1 | NAICS3/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_term)

if(!exists("naics36_cbre"))
  naics36_cbre <- glmer(data=serv_smp,
                        b_CBre ~ (1 | NAICS3/NAICS)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cbre)

if(!exists("naics36_opt"))
  naics36_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | NAICS3/NAICS)
                        )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_opt)
```




### Compare NAICS

```{r Empty_Compare_CBre}

save(naics03_cbre,naics03_term,naics03_opt,
     naics06_cbre,naics06_term,naics06_opt,
     naics36_cbre,naics36_term,naics36_opt,
     file="../data//clean//naics_empty_models.rdata")


get_icc(naics03_cbre)
get_icc(naics06_cbre)
get_icc(naics36_cbre)
```
NAICS6 alone explains the most variance. However, Combining NAICS 3 and NAICS 6 seems has similar value and  offer the most balance. For CBre, the three level options are unhelpful.
```{r Empty_Compare_Term}
get_icc(naics03_term)
get_icc(naics06_term)
get_icc(naics36_term)
```
For termination a largely similar patern holds, but instead it's instead levels 4 and 6 that provide the best balance, but 3 and 6 isn't far behind.
```{r Empty_Compare_opt}
get_icc(naics03_opt)
get_icc(naics06_opt)
get_icc(naics36_opt)

```
The ideal levels varies some depending on the output variable. On the whole NAICS 3 and NAICS 6 combined seem to explain comparatively high levels of variance when summed and are reasonably balanced between the two levels.

Fiscal year generally has more explanatory power than calendar year.

## Product Or Service Codes
### Product Or Service Code
```{r ProdServ}
# load(file="../data/clean/psc_empty_models.rdata")


if(!exists("psc_cbre"))
psc_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | ProdServ)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,psc_cbre)


if(!exists("psc_term"))
psc_term <- glmer(data=serv_smp,
                 b_Term ~ (1 | ProdServ)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,psc_term)

if(!exists("psc_opt"))
psc_opt<- lmer(data=serv_opt,
                 l_OptGrowth ~ (1 | ProdServ)
                  )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,psc_opt)


```
34% for Ceiling Breaches and 22% for Terminations, not a bad start.

### Crisis Product Or Service Area
```{r CrisisProductOrServiceArea}
serv_smp$CrisisProductOrServiceArea
if(!exists("cpsa_cbre"))
cpsa_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | CrisisProductOrServiceArea)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_cbre)

if(!exists("cpsa_term"))
cpsa_term <- glmer(data=serv_smp,
                 b_Term ~ (1 | CrisisProductOrServiceArea)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_term)


if(!exists("cpsa_opt"))
cpsa_opt<- lmer(data=serv_opt,
                 l_OptGrowth ~ (1 | CrisisProductOrServiceArea)
                  )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_opt)


# 
# 
#   if("ProdServ" %in% colnames(serv_smp)){
#     serv_smp$ProdServ[serv_smp$ProdServ==""]<-NA
#     serv_smp$ProductOrServiceCode<-as.character(serv_smp$ProdServ)
#   }
# 
#   if("ProductOrServiceCode" %in% colnames(serv_smp)){
#     serv_smp<-read_and_join( serv_smp,
#                                       "ProductOrServiceCodes.csv",
#                                       path="https://raw.githubusercontent.com/CSISdefense/Lookup-Tables/master/",
#                                       directory="",
#                                       by="ProductOrServiceCode",
#                                       add_var=c("Simple",
#                                                 "ProductServiceOrRnDarea",
#                                                 "ProductOrServiceArea",
#                                                 "HostNation3Category",
#                                                 "CrisisProductOrServiceArea",
#                                                 "ProductOrServiceCodeText"
#                                       ),
#                                       new_var_checked=FALSE)
# 
#     serv_smp$ProductServiceOrRnDarea<-factor(serv_smp$ProductServiceOrRnDarea)
#     serv_smp$ProductOrServiceArea<-factor(serv_smp$ProductOrServiceArea)
#     serv_smp$HostNation3Category<-factor(serv_smp$HostNation3Category)
#     serv_smp$CrisisProductOrServiceArea<-factor(serv_smp$CrisisProductOrServiceArea)
#     serv_smp$ProductOrServiceCodeText<-factor(serv_smp$ProductOrServiceCodeText)
#     
  # }


```
23% for Ceiling Breaches and 18% for Terminations. In particular for terminations, these high level categories seem to capture much of the differences without needing as much detail.

### Service / Commdity / Construction
```{r PSR}
colnames(serv_smp)[colnames(serv_smp)=="HostNation3Category"]<-"ServCommCons"
colnames(serv_opt)[colnames(serv_opt)=="HostNation3Category"]<-"ServCommCons"




if(!exists("ServCommCons_cbre"))
ServCommCons_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | ServCommCons)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,ServCommCons_cbre)


if(!exists("ServCommCons_term"))
ServCommCons_term <- glmer(data=serv_smp,
                 b_Term ~ (1 | ServCommCons)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,ServCommCons_term)


if(!exists("ServCommCons_opt"))
ServCommCons_opt<- lmer(data=serv_opt,
                 l_OptGrowth ~ (1 | ServCommCons)
                  )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,ServCommCons_opt)


```





### CPSA/ProdServ
Three levels
```{r Area_Code}


if(!exists("cpsa_psc_cbre"))
cpsa_psc_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | CrisisProductOrServiceArea/ProdServ)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_cbre)


if(!exists("cpsa_psc_term"))
cpsa_psc_term <- glmer(data=serv_smp,
                 b_Term ~ (1 | CrisisProductOrServiceArea/ProdServ)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_term)


if(!exists("cpsa_psc_opt"))
cpsa_psc_opt<- lmer(data=serv_opt,
                 l_OptGrowth ~ (1 | CrisisProductOrServiceArea/ProdServ)
                  )#)#, family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_opt)


```
Oddly, crisis product or service area just doesn't seem to add anything to the 


### Compare ProdServ

```{r Empty_Compare_CBre}




save(psc_cbre,psc_term,psc_opt,
     cpsa_cbre,cpsa_term,cpsa_opt,
     ServCommCons_cbre,ServCommCons_term,ServCommCons_opt,
     cpsa_psc_cbre,cpsa_psc_term,cpsa_psc_opt,
     # ssc_psc_cbre,ssc_psc_term,
     file="..//data//clean//psc_empty_models.rdata")


get_icc(psc_cbre)
get_icc(cpsa_cbre)
get_icc(ServCommCons_cbre)
get_icc(cpsa_psc_cbre)

      stargazer::stargazer(psc_cbre,cpsa_cbre,ServCommCons_cbre,
                           cpsa_psc_cbre,type="text",
                     digits=2)
```
ServCommCons/ProductServiceCode easily explains the most about the model.
```{r Empty_Compare_Term}
get_icc(psc_term)
get_icc(cpsa_term)
get_icc(ServCommCons_term)
get_icc(cpsa_psc_term)

      stargazer::stargazer(psc_term,cpsa_term,ServCommCons_term,
                           cpsa_psc_term,type="text",
                     digits=2)


```
CrisisProductOrSericeArea doesn't add much value versus ProdServ alone but ServCommCons adds none.

```{r Empty_Compare_opt}
get_icc(psc_opt)
get_icc(cpsa_opt)
get_icc(ServCommCons_opt)
get_icc(cpsa_psc_opt)

      stargazer::stargazer(psc_opt,cpsa_opt,ServCommCons_opt,
                           cpsa_psc_opt,type="text",
                     digits=2)


```
Proceeding with CrisisProductOrServiceArea/ProdServ for Term and CrisisProductOrServiceArea/ProdServ for CBre


The ideal levels varies some depending on the output variable. On the whole ProdServ 3 and ProdServ 6 combined seem to explain comparatively high levels of variance when summed and are reasonably balanced between the two levels.

Fiscal year generally has more explanatory power than calendar year.

## Combining PSC and NAICS
### NAICS 3/6 + CPSA/ProdServ
```{r NAICSlevel36_and_CPSAprodserv}
# load(file="..//data//clean//psc_naics_empty_models.rdata")
if(!exists("naics36_plus_cpsa_psc_term"))
  naics36_plus_cpsa_psc_term <- glmer(data=serv_smp,
                        b_Term ~ (1 | NAICS3/NAICS) +(1| CrisisProductOrServiceArea/ProdServ)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_plus_cpsa_psc_term)

if(!exists("naics36_plus_cpsa_psc_cbre"))
  naics36_plus_cpsa_psc_cbre<- glmer(data=serv_smp,
                        b_CBre ~ (1 | NAICS3/NAICS) +(1| CrisisProductOrServiceArea/ProdServ)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_plus_cpsa_psc_cbre)

if(!exists("naics36_plus_cpsa_psc_opt"))
  naics36_plus_cpsa_psc_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | NAICS3/NAICS) +(1| CrisisProductOrServiceArea/ProdServ)
                        )#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_plus_cpsa_psc_opt)
```


### NAICS 3/6 / CPSA
```{r NAICSlevel36_CPSA}

if(!exists("naics36_cpsa_term"))
  naics36_cpsa_term<- glmer(data=serv_smp,
                        b_Term ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_term)

if(!exists("naics36_cpsa_cbre"))
  naics36_cpsa_cbre<- glmer(data=serv_smp,
                        b_CBre ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_cbre)

if(!exists("naics36_cpsa_opt"))
  naics36_cpsa_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)
                        )#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_opt)


```


### CPSA /PSC / NAICS 3
```{r Area_Code}


if(!exists("cpsa_psc_naices3_cbre"))
cpsa_psc_naices3_cbre <- glmer(data=serv_smp,
                 b_CBre ~ (1 | CrisisProductOrServiceArea/ProdServ/NAICS3)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_naices3_cbre)


if(!exists("cpsa_psc_naics3_term "))
cpsa_psc_naics3_term  <- glmer(data=serv_smp,
                 b_Term ~ (1 | CrisisProductOrServiceArea/ProdServ/NAICS3)
                  , family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_naics3_term)


if(!exists("cpsa_psc_naics3_opt"))
  cpsa_psc_naics3_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | CrisisProductOrServiceArea/ProdServ/NAICS3)
                        )#, family=binomial(link="logit"))
get_icc(display=TRUE,cpsa_psc_naics3_opt)


```

### Compare NAICS and ProdServ

```{r Empty_Compare_CBre}




save(naics36_plus_cpsa_psc_term,naics36_plus_cpsa_psc_cbre,naics36_plus_cpsa_psc_opt,
     naics36_cpsa_term,naics36_cpsa_cbre,naics36_cpsa_opt,
     cpsa_psc_naices3_cbre,cpsa_psc_naics3_term,cpsa_psc_naics3_opt,
     file="..//data//clean//psc_naics_empty_models.rdata")


get_icc(naics36_cbre)
get_icc(cpsa_psc_cbre)
get_icc(naics36_plus_cpsa_psc_cbre)
get_icc(naics36_cpsa_cbre)
get_icc(cpsa_psc_naices3_cbre)


      stargazer::stargazer(naics36_cbre,
                           cpsa_psc_cbre,
                           naics36_plus_cpsa_psc_cbre,
                           naics36_cpsa_cbre,
                           cpsa_psc_naices3_cbre,
                           type="text",
                     digits=2)
```

For ceiling breaches, NAICS does much better and including product or service codes as a seperate set degrades the performance fo the model.

```{r Empty_Compare_term}


get_icc(naics36_term)
get_icc(cpsa_psc_term)
get_icc(naics36_plus_cpsa_psc_term)
get_icc(naics36_cpsa_term)
get_icc(cpsa_psc_naics3_term)



      stargazer::stargazer(naics36_term,
                           cpsa_psc_term,
                           naics36_plus_cpsa_psc_term,
                           naics36_cpsa_term,
                           cpsa_psc_naics3_term,type="text",
                     digits=2)
```
For termination, adding PSC slightly improves the performance of the model,. 


```{r Empty_Compare_opt}


get_icc(naics36_opt)
get_icc(cpsa_psc_opt)
get_icc(naics36_plus_cpsa_psc_opt)
get_icc(naics36_cpsa_opt)
get_icc(cpsa_psc_naics3_opt)



      stargazer::stargazer(naics36_opt,
                           cpsa_psc_opt,
                           naics36_plus_cpsa_psc_opt,
                           naics36_cpsa_opt,
                           cpsa_psc_naics3_opt,type="text",
                     digits=2)
```


Adding both NAICS3/NAICS6+CPSA/PSC consistently beats just NAICS3/NAICS6/CPSA, but the margin isn't  huge and I'm a bit hesitant to have  two potentially redundant set of multilevel models. The partial exception is Opts where PSC just catches much more than NAICS, but the margin is about 2000 smaller than the margin in the other direction for the other models and consistency seems worth maintaining.

## Start Year

### Calendar Year
```{r StartCY}
# load(file="../data//clean//when_empty_models.rdata")

if(!exists("StartCY_term"))
  StartCY_term <- glmer(data=serv_smp,
                        b_Term ~ (1 | StartCY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_term)

if(!exists("StartCY_cbre"))
  StartCY_cbre <- glmer(data=serv_smp,
                        b_CBre ~ (1 | StartCY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_cbre)

if(!exists("StartCY_opt"))
  StartCY_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | StartCY)
                        )#, family=binomial(link="logit"))
get_icc(display=TRUE,StartCY_opt)

```

The ICC is highest for ceiling breaches and is backloaded, with 2015 and 2016 having lower than usual odds. This is likely an artifact of those years having fewer completed longer contracts. That said, this should be largely compensated for with the inclusion of initial duration. If this proves challenges to manage, it may be worth considering dropping 2016. 

### Fiscal Year

```{r StartFY}
# load(file="../data//clean//when_empty_models.rdata")

if(!exists("StartFY_term"))
  StartFY_term <- glmer(data=serv_smp,
                        b_Term ~ (1 | StartFY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartFY_term)

if(!exists("StartFY_cbre"))
  StartFY_cbre <- glmer(data=serv_smp,
                        b_CBre ~ (1 | StartFY)
                        , family=binomial(link="logit"))
get_icc(display=TRUE,StartFY_cbre)

if(!exists("StartFY_opt"))
  StartFY_opt <- lmer(data=serv_opt,
                        l_OptGrowth ~ (1 | StartFY)
                        )#, family=binomial(link="logit"))
get_icc(display=TRUE,StartFY_opt)
coef(StartFY_opt)
```


### NAICS and Calendar Year
```{r NAICS_StartCY}

if(!exists("NAICS_StartCY_term"))
  NAICS_StartCY_term <- glmer(data=serv_smp,
                              b_Term ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_term)

if(!exists("NAICS_StartCY_cbre"))
  NAICS_StartCY_cbre <- glmer(data=serv_smp,
                              b_CBre ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_cbre)

if(!exists("NAICS_StartCY_opt"))
  NAICS_StartCY_opt <- lmer(data=serv_opt,
                              l_OptGrowth ~  (1 | NAICS3/NAICS) + (1 | StartCY)
                              )#, family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_StartCY_opt)

```

### NAICS/CPSA and Calendar Year
```{r NAICS_StartCY}

if(!exists("NAICS_cpsa_StartCY_term"))
  NAICS_cpsa_StartCY_term <- glmer(data=serv_smp,
                              b_Term ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartCY_term)

if(!exists("NAICS_cpsa_StartCY_cbre"))
  NAICS_cpsa_StartCY_cbre <- glmer(data=serv_smp,
                              b_CBre ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartCY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartCY_cbre)

if(!exists("NAICS_cpsa_StartCY_opt"))
  NAICS_cpsa_StartCY_opt <- lmer(data=serv_opt,
                              l_OptGrowth ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartCY)
                              )#, family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartCY_opt)

```


### NAICS/CPSA and Fiscal Year
```{r NAICS_StartFY}

if(!exists("NAICS_cpsa_StartFY_term"))
  NAICS_cpsa_StartFY_term <- glmer(data=serv_smp,
                              b_Term ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartFY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartFY_term)

if(!exists("NAICS_cpsa_StartFY_cbre"))
  NAICS_cpsa_StartFY_cbre <- glmer(data=serv_smp,
                              b_CBre ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartFY)
                              , family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartFY_cbre)

if(!exists("NAICS_cpsa_StartFY_opt"))
  NAICS_cpsa_StartFY_opt <- lmer(data=serv_opt,
                              l_OptGrowth ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartFY)
                              )#, family=binomial(link="logit"))
get_icc(display=TRUE,NAICS_cpsa_StartFY_opt)

```
### Compare Signed Dates
```{r Empty_Compare_When}

save(StartCY_cbre,StartCY_term,StartCY_opt,
     # SignedMonth_cbre,SignedMonth_term,SignedMonth_opt,
     # NestedMonth_cbre,NestedMonth_term,NestedMonth_opt,
     NAICS_StartCY_cbre,NAICS_StartCY_term,NAICS_StartCY_opt,
     NAICS_cpsa_StartCY_cbre,NAICS_cpsa_StartCY_term,NAICS_cpsa_StartCY_opt,
     NAICS_cpsa_StartFY_cbre,NAICS_cpsa_StartFY_term,NAICS_cpsa_StartFY_opt,
     file="../data//clean//when_empty_models.rdata")

get_icc(naics36_cbre)
get_icc(StartCY_cbre)
get_icc(StartFY_cbre)
# get_icc(SignedMonth_cbre)
# get_icc(NestedMonth_cbre)
get_icc(NAICS_StartCY_cbre)
get_icc(NAICS_cpsa_StartCY_cbre)
get_icc(NAICS_cpsa_StartFY_cbre)


stargazer::stargazer(naics36_cbre,
                           naics36_cpsa_cbre,
                           StartCY_cbre,
                     StartFY_cbre,
                           NAICS_StartCY_cbre,
                           NAICS_cpsa_StartCY_cbre,
                     NAICS_cpsa_StartFY_cbre,type="text",
                     digits=2)

get_icc(naics36_term)
get_icc(StartCY_term)
get_icc(StartFY_term)
# get_icc(SignedMonth_term)
# get_icc(NestedMonth_term)
get_icc(NAICS_StartCY_term)
get_icc(NAICS_cpsa_StartCY_term)
get_icc(NAICS_cpsa_StartFY_term)

stargazer::stargazer(naics36_term,
                           naics36_cpsa_term,
                           StartCY_term,
                     StartFY_term,
                           NAICS_StartCY_term,
                           NAICS_cpsa_StartFY_term,
                           NAICS_cpsa_StartCY_term,
                     type="text",
                     digits=2)


get_icc(naics36_opt)
get_icc(StartCY_opt)
get_icc(StartFY_opt)
# coef(StartCY_opt)
# get_icc(SignedMonth_opt)
# get_icc(NestedMonth_opt)
get_icc(NAICS_StartCY_opt)
get_icc(NAICS_cpsa_StartCY_opt)
get_icc(NAICS_cpsa_StartFY_opt)

coef(StartCY_opt)


      stargazer::stargazer(naics36_opt,
                           naics36_cpsa_opt,
                           StartCY_opt,
                           StartFY_opt,
                           NAICS_StartCY_opt,
                           NAICS_cpsa_StartCY_opt,
                           NAICS_cpsa_StartFY_opt,type="text",
                     digits=2)

```

Start year adds little. Leaving it out.

##Customer
### Office
```{r Office}
# load(file="../data//clean//who_empty_models.rdata")
if(!exists("Office_term"))
  Office_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | Agency:Office)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Office_term)

if(!exists("Office_cbre"))
  Office_cbre <- glmer(data=serv_smp,
                       b_CBre ~ (1 | Agency:Office)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Office_cbre)

if(!exists("Office_opt"))
  Office_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | Agency:Office)
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,Office_opt)

```

### Agency
```{r Agency}
if(!exists("Agency_term"))
  Agency_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | Agency)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Agency_term)

if(!exists("Agency_cbre"))
  Agency_cbre <- glmer(data=serv_smp,
                       b_CBre ~ (1 | Agency)
                       , family=binomial(link="logit"))
get_icc(display=TRUE,Agency_cbre)

if(!exists("Agency_opt"))
  Agency_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | Agency)
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,Agency_opt)

```


### Nested Office
```{r NestedOffice}
if(!exists("NestedOffice_term"))
  NestedOffice_term <- glmer(data=serv_smp,
                             b_Term ~ (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_term)

if(!exists("NestedOffice_cbre"))
  NestedOffice_cbre <- glmer(data=serv_smp,
                             b_CBre ~ (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_cbre)

if(!exists("NestedOffice_opt"))
  NestedOffice_opt <- lmer(data=serv_opt,
                             l_OptGrowth ~ (1 | Agency/Office)
                             )#, family=binomial(link="logit"))
get_icc(display=TRUE,NestedOffice_opt)

```


### NAICS 36 Office
```{r naics36_serv_smpOffice}
if(!exists("naics 36_Office_term"))
  naics36_Office_term <- glmer(data=serv_smp,
                             b_Term ~  (1 | NAICS3/NAICS) +  (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_term)
# 
if(!exists("naics36_Office_cbre"))
  naics36_Office_cbre <- glmer(data=serv_smp,
                             b_CBre ~  (1 | NAICS3/NAICS)+  (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_cbre)

if(!exists("naics36_Office_opt"))
  naics36_Office_opt <- lmer(data=serv_opt,
                             l_OptGrowth ~  (1 | NAICS3/NAICS)+ (1 | Agency/Office)
                             )#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_Office_opt)

```

### NAICS 36 CPSA  Office
```{r naics36_cpsa_Office}
if(!exists("naics naics36_cpsa_Office_term"))
  naics36_cpsa_Office_term <- glmer(data=serv_smp,
                             b_Term ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_Office_term)
# 
if(!exists("naics36_cpsa_Office_cbre"))
  naics36_cpsa_Office_cbre <- glmer(data=serv_smp,
                             b_CBre ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_Office_cbre)

if(!exists("naics36_cpsa_Office_opt"))
  naics36_cpsa_Office_opt <- lmer(data=serv_opt,
                             l_OptGrowth ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | Agency/Office)
                             )#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_Office_opt)

```



### NAICS 36 CPSA   FY When Office
```{r naics36_cpsa_When_Office}
if(!exists("naics naics36_cpsa_When_Office_term"))
  naics36_cpsa_When_Office_term <- glmer(data=serv_smp,
                             b_Term ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea) + (1 | StartFY) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_When_Office_term)
# 
if(!exists("naics36_cpsa_When_Office_cbre"))
  naics36_cpsa_When_Office_cbre <- glmer(data=serv_smp,
                             b_CBre ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+ (1 | StartFY) + (1 | Agency/Office)
                             , family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_When_Office_cbre)

if(!exists("naics36_cpsa_When_Office_opt"))
  naics36_cpsa_When_Office_opt <- lmer(data=serv_opt,
                             l_OptGrowth ~  (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+ (1 | StartFY) + (1 | Agency/Office)
                             )#, family=binomial(link="logit"))
get_icc(display=TRUE,naics36_cpsa_When_Office_opt)

```

### Compare Who
```{r Empty_Compare_Who_Term}

save(Office_cbre,Office_term,Office_opt,
     Agency_cbre,Agency_term,Agency_opt,
     NestedOffice_cbre,NestedOffice_term,NestedOffice_opt,
     naics36_Office_cbre,naics36_Office_term,naics36_Office_opt,
     naics36_cpsa_Office_cbre,naics36_cpsa_Office_term,naics36_cpsa_Office_opt,
     naics36_cpsa_When_Office_cbre,naics36_cpsa_When_Office_term,naics36_cpsa_When_Office_opt,
     file="../data//clean//who_empty_models.rdata")

get_icc(naics36_cbre)
get_icc(Office_cbre)
get_icc(Agency_cbre)
get_icc(NestedOffice_cbre)
get_icc(naics36_Office_cbre)
get_icc(naics36_cpsa_Office_cbre)
get_icc(naics36_cpsa_When_Office_cbre)

stargazer::stargazer(naics36_cbre,
                           Office_cbre,
                           Agency_cbre,
                     NestedOffice_cbre,
                     naics36_Office_cbre,
                     naics36_cpsa_Office_cbre,
                           naics36_cpsa_When_Office_cbre,type="text",
                     digits=2)

debug(summary_residual_compare)
summary_residual_compare(naics36_Office_term,naics46_Office_term,naics36_Office_cbre,naics46_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics06_Office_term,naics36_Office_term,naics06_Office_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics36_Office_term,naics36_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics236_term,naics36_cbre,naics236_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics36_Office_term,naics36_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
```


```{r Empty_Compare_Who_term}


get_icc(naics36_term)
get_icc(Office_term)
get_icc(Agency_term)
get_icc(NestedOffice_term)
get_icc(naics36_Office_term)
get_icc(naics36_cpsa_Office_term)
get_icc(naics36_cpsa_When_Office_term)

stargazer::stargazer(naics36_term,
                           Office_term,
                           Agency_term,
                     NestedOffice_term,
                     naics36_Office_term,
                     naics36_cpsa_Office_term,
                           naics36_cpsa_When_Office_term,type="text",
                     digits=2)
```

```{r Empty_Compare_Who_opt}

get_icc(naics36_opt)
get_icc(Office_opt)
get_icc(Agency_opt)
get_icc(NestedOffice_opt)
get_icc(naics36_Office_opt)
get_icc(naics36_cpsa_Office_opt)
get_icc(naics36_cpsa_When_Office_opt)

stargazer::stargazer(naics36_opt,
                           Office_opt,
                           Agency_opt,
                     NestedOffice_opt,
                     naics36_Office_opt,
                     naics36_cpsa_Office_opt,
                           naics36_cpsa_When_Office_opt,type="text",
                     digits=2)

```
There is some contradiction in which model best serves this category. For Comp, the nested office has the largest summed ICC, but for term this results in an failure to converge and a 0 ICC for agency. Agency:Office alone is respectable for all three so that is used in the combination attempt.




## Where

### Place
```{r PlaceCountry}
# load(file="Output//where_empty_models.rdata")

if(!exists("PlaceCountry_cbre"))
  PlaceCountry_cbre <- glmer(data=serv_smp,
                       b_CBre ~ (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_cbre)

if(!exists("PlaceCountry_term"))
  PlaceCountry_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_term)



if(!exists("PlaceCountry_opt"))
  PlaceCountry_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | PlaceCountryISO3)
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,PlaceCountry_opt)

```



### NAICS 36 Office Place
```{r PlaceCountry_naics_36_Office}
# load(file="Output//where_empty_models.rdata")

if(!exists("PlaceCountry_naics_36_Office_cbre"))
  PlaceCountry_naics_36_Office_cbre <- glmer(data=serv_smp,
                       b_CBre ~   (1 | NAICS3/NAICS)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_Office_cbre)

if(!exists("PlaceCountry_naics_36_Office_term"))
  PlaceCountry_naics_36_Office_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | NAICS3/NAICS)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_Office_term)



if(!exists("PlaceCountry_naics_36_Office_opt"))
  PlaceCountry_naics_36_Office_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | NAICS3/NAICS)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,PlaceCountry_naics_36_Office_opt)


```


### NAICS 36 cpsa_Office Place
```{r PlaceCountry_naics_36_cpsa_Office}
# load(file="Output//where_empty_models.rdata")

if(!exists("PlaceCountry_naics_36_cpsa_Office_cbre"))
  PlaceCountry_naics_36_cpsa_Office_cbre <- glmer(data=serv_smp,
                       b_CBre ~   (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_cbre)

if(!exists("PlaceCountry_naics_36_cpsa_Office_term"))
  PlaceCountry_naics_36_cpsa_Office_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_term)



if(!exists("PlaceCountry_naics_36_cpsa_Office_opt"))
  PlaceCountry_naics_36_cpsa_Office_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_opt)


```

### NAICS 36 cpsa_Office When Place
```{r PlaceCountry_naics_36_cpsa_Office_When}
# load(file="Output//where_empty_models.rdata")

if(!exists("PlaceCountry_naics_36_cpsa_Office_When_cbre"))
  PlaceCountry_naics_36_cpsa_Office_When_cbre <- glmer(data=serv_smp,
                       b_CBre ~   (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)+ (1 | StartFY) 
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_cbre)

if(!exists("PlaceCountry_naics_36_cpsa_Office_When_term"))
  PlaceCountry_naics_36_cpsa_Office_When_term <- glmer(data=serv_smp,
                       b_Term ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)+ (1 | StartFY) 
                       , family=binomial(link="logit"),
     control = glmerControl(optimizer = "optimx", calc.derivs = FALSE,
     optCtrl = list(method = "nlminb", starttests = FALSE, kkt = FALSE)))

get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_When_term)



if(!exists("PlaceCountry_naics_36_cpsa_Office_When_opt"))
  PlaceCountry_naics_36_cpsa_Office_When_opt <- lmer(data=serv_opt,
                       l_OptGrowth ~ (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  (1 | Agency/Office) + (1 | PlaceCountryISO3)+ (1 | StartFY) 
                       )#, family=binomial(link="logit"))
get_icc(display=TRUE,PlaceCountry_naics_36_cpsa_Office_When_opt)


```

### Compare Where
```{r Empty_Compare_Where_Term}

save(PlaceCountry_cbre,PlaceCountry_term,PlaceCountry_opt,
     PlaceCountry_naics_36_Office_opt,
     PlaceCountry_naics_36_cpsa_Office_opt,
     PlaceCountry_naics_36_cpsa_Office_When_opt,
     file="../data//clean//where_empty_models.rdata")


get_icc(naics36_When_Office_cbre)
get_icc(naics36_cpsa_When_Office_cbre)
get_icc(naics36_cpsa_Office_cbre)
get_icc(PlaceCountry_cbre)
get_icc(PlaceCountry_naics_36_Office_cbre)
get_icc(PlaceCountry_naics_36_cpsa_Office_cbre)
get_icc(PlaceCountry_naics_36_cpsa_Office_When_cbre)


stargazer::stargazer(naics36_When_Office_cbre,
                     naics36_cpsa_Office_cbre,
                           naics36_cpsa_When_Office_cbre,
                           PlaceCountry_cbre,
                     PlaceCountry_naics_36_Office_cbre,
                           PlaceCountry_naics_36_cpsa_Office_cbre,
                           PlaceCountry_naics_36_cpsa_Office_When_cbre,
                     type="text",
                     digits=2)

debug(summary_residual_compare)
summary_residual_compare(naics36_Office_term,naics46_Office_term,naics36_Office_cbre,naics46_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics06_Office_term,naics36_Office_term,naics06_Office_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics36_Office_term,naics36_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics236_term,naics36_cbre,naics236_cbre,bins=10,suppress_vif=TRUE)
summary_residual_compare(naics36_term,naics36_Office_term,naics36_cbre,naics36_Office_cbre,bins=10,suppress_vif=TRUE)
```


```{r Empty_Compare_Where_term}

get_icc(naics36_When_Office_term)
get_icc(naics36_cpsa_When_Office_term)
get_icc(naics36_cpsa_Office_term)
get_icc(PlaceCountry_term)
get_icc(PlaceCountry_naics_36_Office_term)
get_icc(PlaceCountry_naics_36_cpsa_Office_term)
get_icc(PlaceCountry_naics_36_cpsa_Office_When_term)


stargazer::stargazer(naics36_When_Office_term,
                     naics36_cpsa_Office_term,
                           naics36_cpsa_When_Office_term,
                           PlaceCountry_term,
                     PlaceCountry_naics_36_Office_term,
                           PlaceCountry_naics_36_cpsa_Office_term,
                           PlaceCountry_naics_36_cpsa_Office_When_term,
                     type="text",
                     digits=2)


```

```{r Empty_Compare_Where_opt}


get_icc(naics36_When_Office_opt)
get_icc(naics36_cpsa_When_Office_opt)
get_icc(naics36_cpsa_Office_opt)
get_icc(PlaceCountry_opt)
get_icc(PlaceCountry_naics_36_Office_opt)
get_icc(PlaceCountry_naics_36_cpsa_Office_opt)
get_icc(PlaceCountry_naics_36_cpsa_Office_When_opt)


stargazer::stargazer(naics36_When_Office_opt,
                     naics36_cpsa_Office_opt,
                           naics36_cpsa_When_Office_opt,
                           PlaceCountry_opt,
                     PlaceCountry_naics_36_Office_opt,
                           PlaceCountry_naics_36_cpsa_Office_opt,
                           PlaceCountry_naics_36_cpsa_Office_When_opt,
                     type="text",
                     digits=2)
```