---
title: "Exercised Option Exaination"
author: "Greg Sanders"
date: "July 7, 2019"
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
---


#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(texreg)
library(reshape2)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40
memory.limit()

```

```{r vargraphs: ExercisedOptions}
#load("../data/clean/transformed_def_serv.Rdata")
load(file="..\\data\\semi_clean\\opt_pre_clean.rdata")
  

#File Pre-processed and Loaded
#W912UM <- def_serv %>% filter(Office=="W912UM")
#W912UMtrans<-read.delim(file="..\\data\\semi_clean\\W912UM_trans.csv", sep=",")
#W912UMtrans<-remove_bom(W912UMtrans)
#opt_preclean<-def_serv %>% filter(ExercisedOptions>1)
#opt_preclean$q_OptGrowth<-Hmisc::cut2(opt_preclean$p_OptGrowth-1,c(0,1e-10,1,10))
summary(opt_preclean$q_OptGrowth)
#save(W912UM,W912UMtrans,opt_preclean,file="..\\data\\semi_clean\\opt_pre_clean.rdata")


summary(opt_preclean$ExercisedOptions)
summary(opt_preclean$UnmodifiedBaseandExercisedOptionsValue)
```



# Before Cleaning
```{r OptionsOutlier_pre}

summary(Hmisc::cut2(opt_preclean$p_OptGrowth-1,c(1,
                                                 5,
                                          10,
                                          100
                                          )))
nrow(opt_preclean %>% filter((p_OptGrowth-1)>100 & UnmodifiedBaseandExercisedOptionsValue<=0))
nrow(opt_preclean %>% filter((p_OptGrowth-1)>10 & (UnmodifiedBaseandExercisedOptionsValue+ExercisedOptions)<UnmodifiedContractBaseAndAllOptionsValue.Then.Year))
summary(opt_preclean$Ceil[(opt_preclean$p_OptGrowth-1)>10 & opt_preclean$UnmodifiedBaseandExercisedOptionsValue>0])
summary(opt_preclean$Ceil[(opt_preclean$p_OptGrowth-1)>100 & opt_preclean$UnmodifiedBaseandExercisedOptionsValue>0])
opt_preclean$Why_Outlier<-NA
opt_preclean$Why_Outlier[opt_preclean$UnmodifiedBaseandExercisedOptionsValue<=0]<-"No Unmodified Base"
opt_preclean$Why_Outlier[is.na(opt_preclean$Why_Outlier)&
                   opt_preclean$Action_Obligation.Then.Year*2>=opt_preclean$UnmodifiedBaseandExercisedOptionsValue+
                   opt_preclean$ExercisedOptions]<-
  "Obligations at least half Base+Opt"
opt_preclean$Why_Outlier[is.na(opt_preclean$Why_Outlier)&
                   opt_preclean$Office=="W912UM"]<-
  "Korean Office W912UM"
opt_preclean$Why_Outlier[is.na(opt_preclean$Why_Outlier)&((opt_preclean$UnmodifiedBaseandExercisedOptionsValue + opt_preclean$ExercisedOptions) < opt_preclean$UnmodifiedContractBaseAndAllOptionsValue.Then.Year)] <- "Base + Growth < Unmodified Ceiling"
opt_preclean$Why_Outlier[is.na(opt_preclean$Why_Outlier)&
                   opt_preclean$ExercisedOptions>=2.5e8]<-
  ">=$250M, Insepect"
opt_preclean$Why_Outlier[is.na(opt_preclean$Why_Outlier)&
                   opt_preclean$p_OptGrowth-1>10]<-
  "Other Unexplained 10x Options Growth"

opt_preclean$Why_Outlier<-factor(opt_preclean$Why_Outlier, levels = c("No Unmodified Base", "Obligations at least half Base+Opt", "Korean Office W912UM", "Base + Growth < Unmodified Ceiling", ">=$250M, Insepect", "Other Unexplained 10x Options Growth"))

summary(opt_preclean$Why_Outlier[(opt_preclean$p_OptGrowth-1)>10])
summary(opt_preclean$Why_Outlier)


p_outlier_summary<-opt_preclean %>% filter(p_OptGrowth-1>10) %>% group_by(Why_Outlier) %>%
  dplyr::summarise(nContract=length(ExercisedOptions),
    SumOfExercisedOptions=sum(ExercisedOptions),
                   MaxOfExercisedOptions=max(ExercisedOptions),
                   SumOfAction_Obligation.Then.Year=sum(Action_Obligation.Then.Year))


n_outlier_summary<-opt_preclean %>% filter(ExercisedOptions>2.5e8) %>% group_by(Why_Outlier) %>%
  dplyr::summarise(nContract=length(ExercisedOptions),
    SumOfExercisedOptions=sum(ExercisedOptions),
                   MaxOfExercisedOptions=max(ExercisedOptions),
                   SumOfAction_Obligation.Then.Year=sum(Action_Obligation.Then.Year))


summary(Hmisc::cut2(opt_preclean$ExercisedOptions,c(1e3,
                                          1e6,
                                          1e7,
                                          1e8,
                                          2.5e8,
                                          1e9,
                                          1e10,
                                          2e10
                                          )))

summary(opt_preclean$Ceil[opt_preclean$ExercisedOptions>=1e6])
summary(opt_preclean$Ceil[opt_preclean$ExercisedOptions>=1e9])

write.csv(file="..\\Data\\semi_clean\\p_opt_outliers.csv",opt_preclean %>% filter((p_OptGrowth-1)>10 & Why_Outlier != "Base + Growth < Unmodified Ceiling"),row.names = FALSE)
write.csv(file="..\\Data\\semi_clean\\n_opt_outliers.csv",opt_preclean %>% filter(ExercisedOptions>=2.5e8 & Why_Outlier != "Base + Growth < Unmodified Ceiling"),row.names = FALSE)
```
Examining cases of large options growth, `r nrow(opt_preclean %>% filter(p_OptGrowth-1>10))` contracts experienced greater than 10 fold growth. An increase of that size strains credulity, even in high risk defense contracting. While by no means impossible, the more likely explaination is a misrecorded base.

The study team broke down the outliers into three categories:
`r knitr::kable(p_outlier_summary)`
* No Unmodified Base: Contracts with an initial base <=0. These are eliminated from the sample as missing data.
* Obligations at least half Base+Opt: For this category, total obligations of the contract were at least half the value of the initial base plus options growth under exercised options. These contracts have had spending that massively exceeded their original base, so the growth in absolute terrms seems plausible. This category accounts for the majority of outlier spending and an overwhelming majority of all exercised options growth amongst outliers (but less than 10% of total exercised options growth when compared to the full sample).
* Finally a few score contrats have unexplained growth, but remain below the $10M threshold. The quantity and magnitude of these contracts is not sufficient to risk the overall model.

This examination left the study team less confident in percentage growth as a metric, especially in extreme cases, while increasing the study team's confidence in measures of growth in absoute term. In the worst case, simply removing all of the unexplained over  10 million contracts from the sample would reduce the number of contracts by a tiny amount and reduce the spending accounted for by  `r sum(opt_preclean$Action_Obligation.Then.Year[opt_preclean$Why_Outlier ==">=$250M, Insepect"& (opt_preclean$p_OptGrowth-1)>10] ,na.rm=TRUE)`.

Shifting the focus to all contracts with absolute growth of at least 250 million, there are far fewer contracts that account for far less money.
`r knitr::kable(n_outlier_summary)`

## Options Growth
```{r OptionsGrowthGraphs}

(
ggplot(opt_preclean, aes(x=UnmodifiedBaseandExercisedOptionsValue,y=p_OptGrowth-1)) +#,color=q_OptGrowth
  geom_point(alpha=0.25,shape=".")+
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+scale_y_log10()+
  #+
  geom_vline(xintercept = c(1,10,100))+#+geom_vline(xintercept = 0.1)+
# facet_wrap(~Ceil,scales="free_y")+#+, space="free_y"
  labs(title="Distribution of Exercised Options",
       y="Percent of Options Growth from Base",
       x="Unmodified Contract Base")#,
       # fill="Termination Completion"
)


(
ggplot(opt_preclean, aes(x=UnmodifiedBaseandExercisedOptionsValue,y=ExercisedOptions)) +#,color=q_OptGrowth
  geom_point(alpha=0.25,shape=".")+
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+scale_y_log10()+
  #+
  geom_vline(xintercept = c(1,10,100))+#+geom_vline(xintercept = 0.1)+
# facet_wrap(~Ceil,scales="free_y")+#+, space="free_y"
  labs(title="Distribution of Exercised Options",
       y="Absolute Options Growth from Base",
       x="Unmodified Contract Base")#,
       # fill="Termination Completion"
)

(
ggplot(opt_preclean, aes(x=UnmodifiedBaseandExercisedOptionsValue+ExercisedOptions,y=Action_Obligation.Then.Year)) +#,color=q_OptGrowth
  geom_point(alpha=0.25,shape=".")+
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+scale_y_log10()+
  #+
#   geom_vline(xintercept = c(1,10,100))+#+geom_vline(xintercept = 0.1)+
# # facet_wrap(~Ceil,scales="free_y")+#+, space="free_y"
   labs(title="Distribution of Exercised Options",
#        y="Percent of Options Growth from Base",
        x="Unmodified Contract Base + Exercised Options")#,
#        # fill="Termination Completion"
)

summary(opt_preclean$ExercisedOptions)



(
ggplot(opt_preclean, aes(x=p_OptGrowth-1,fill=q_OptGrowth)) +
  geom_histogram(bins=100)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+
  #+
  geom_vline(xintercept = c(1,10,100))+#+geom_vline(xintercept = 0.1)+
facet_wrap(~Ceil,scales="free_y")+#+, space="free_y"
  labs(title="Distribution of Exercised Options",
       y="Contract Count",
       x="Percent of Options Growth from Base")#,
       # fill="Termination Completion"
)






(
ggplot(opt_preclean, aes(x=ExercisedOptions,fill=q_OptGrowth)) +
  geom_histogram(bins=100)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+
  #+
  geom_vline(xintercept = 1)+#+geom_vline(xintercept = 0.1)+
#facet_grid(NoPreTermObl~.,scales="free_y", space="free_y")+
   labs(title="Distribution of Contracts by Exercised Options Growth")#,
  #      y="Contract Count",
  #      x="Percent of Obligations After Day of Termination",
  #      fill="Termination Completion"
)

(
ggplot(opt_preclean, aes(x=ExercisedOptions,fill=q_OptGrowth)) +
  geom_histogram(bins=100)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_log10()+
  #+
  geom_vline(xintercept = 1)+
facet_wrap(~Ceil,scales="free_y")+#+, space="free_y"
#+geom_vline(xintercept = 0.1)+
#facet_grid(NoPreTermObl~.,scales="free_y", space="free_y")+
   labs(title="Distribution of Contracts by Exercised Options Growth, Grouped by Ceiling")#,
  #      y="Contract Count",
  #      x="Percent of Obligations After Day of Termination",
  #      fill="Termination Completion"
)


```

## >250 Inspect
```{r gt250m}
inspect250<-opt_preclean %>% filter(Why_Outlier==">=$250M, Insepect")
inspect250$CSIScontractID
inspect250trans<-read.delim(file="..\\data\\semi_clean\\gt250k_n_exercised_opt_outliers.txt", sep="\t")


#gt250k_n_exercised_opt_outliers.txt

```
No contracts with unexplained >=\$250M absolute growth exist in the dataset.  4 such contracts demonstrate absolute growth >=\$250M, but are coded instead as 'Obligations at least half Base+Opt.'  Manual inspection of these makes clear that the growth identified is legitimate, and should be included in the dataset.

## Other Unexplained x10 Inspect
The contracts coded as 'other unexplained' above were inspected manually given their relative scarcity.  Several were found to contain suspect transactions that were later corrected, meaning these contracts should be dropped from our sample, which will occur through use of the CSIS360 repository, and the lookup table "override_lookup.Rda".