---
title: "Terminations and Closures"
output: html_document
---

```{r setup, include=FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(texreg)
library(reshape2)
library(readr)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/lookups.r")
source("https://raw.githubusercontent.com/CSISdefense/R-scripts-and-data/master/helper.r")
source("https://raw.githubusercontent.com/CSISdefense/Crisis-Funding/master/Scripts/ContractCleanup.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40

```


# Overall Citeria
## Importing data

```{r CloseOutAll}

# criteria<-read_delim(file="..\\data\\semi_clean\\Contract.SP_ContractSampleCriteriaDetailsCustomer.txt",
#                      delim="\t",na=c("","NA","NULL"))

criteria$StartFY<-year(criteria$MinOfSignedDate)+ifelse(month(criteria$MinOfSignedDate)>=10,1,0)
criteria<-criteria %>% filter(StartFY>=2007 & StartFY<2016)
criteria<-standardize_variable_names(criteria)

criteria$LastCurrentCompletionDate<-na_nonsense_dates(criteria$LastCurrentCompletionDate)





criteria<-csis360::read_and_join_experiment(criteria,
                            lookup_file = "Contract.SP_ContractCloseOutExamination.txt",
                            path="..\\",
                            dir="Data\\semi_clean\\",
                            by="CSIScontractID",
                            new_var_checked = FALSE
                            # skip_check_var=c("IsClosed" ,
                            #                  "MaxClosedDate",
                            #                  "ObligatedAfterMaxClosedDate")
)



criteria<-csis360::read_and_join_experiment(criteria,
                            lookup_file = "Contract.SP_ContractTerminationExamination.txt",
                            path="..\\",
                            dir="Data\\semi_clean\\",
                            by="CSIScontractID",
                            new_var_checked = FALSE
                            # skip_check_var=c("IsClosed" ,
                            #                  "MaxClosedDate",
                            #                  "ObligatedAfterMaxClosedDate")
)

criteria$Term<-"Unterminated"
criteria$Term[!is.na(criteria$MaxTerminatedDate)]<-"Terminated"
criteria$Term<-factor(criteria$Term)


criteria$Include2015<-"No"
criteria$Include2015[criteria$StartFY<=2015 & 
                       #For unclosed out contracts both current completion and last signed should bebefore  2016
                       (criteria$MaxBoostDate<=as.Date("2016-09-30")| is.na(criteria$MaxBoostDate))&
                      (criteria$LastCurrentCompletionDate<=as.Date("2016-09-30")
                     #For closed out it's enough that the boost date is within the range.
                     | (criteria$IsClosed==1 | criteria$Term=="Terminated"))
                        ]<-"Yes"

criteria$Include2015<-factor(criteria$Include2015, levels=c("Yes","No"))
summary(criteria$Include2015)

late_signed<-criteria %>%filter(MaxBoostDate>LastCurrentCompletionDate)


save(criteria,late_signed,file="../data/semi_clean/end_research.rdta")



summary(factor(late_signed$IsClosed))
summary(late_signed$Term)
summary(factor(late_signed$Include2015))
sum(late_signed$Action_Obligation)
sum(criteria$Action_Obligation)
```

# Close Out
## Analysis with Excluded Contracts
### Totals
```{r CloseOutAll}
CloseOutAll<-criteria %>% dplyr::filter(IsClosed==1)


# summary(CloseOutAll)
summary(CloseOutAll$MaxClosedDate)
summary(CloseOutAll$ObligatedAfterMaxClosedDate)

sum(CloseOutAll$ObligatedAfterMaxClosedDate)

CloseOutAll$PostCloseFloor0<-CloseOutAll$ObligatedAfterMaxClosedDate
CloseOutAll$PostCloseFloor0[CloseOutAll$PostCloseFloor0<0]<-0

CloseOutAll$LastCurrentCompletionDate<-as.Date(CloseOutAll$LastCurrentCompletionDate)

CloseOutAll$LastCurrentCompletionDate<-na_nonsense_dates(CloseOutAll$LastCurrentCompletionDate)

summary(factor(CloseOutAll$Include2015))
gridExtra::grid.arrange(ggplot(CloseOutAll, aes(x=StartFY, fill=Include2015))+geom_bar(),
ggplot(CloseOutAll, aes(x=StartFY, y=Action_Obligation, fill=Include2015))+geom_col()
)
(
CloseOutCeilObl<-ggplot(CloseOutAll,aes(x=PostCloseFloor0+1)) +#,color=qHighCeiling
  stat_ecdf(geom = "step")+stat_ecdf(geom = "step",aes(x=PostCloseFloor0+1))+
    coord_cartesian(ylim=c(0.85,1))+#+,xlim=c(0,1e8)
  scale_x_log10(label=comma)+
  labs(title="Cumulative Distribution of Terminated Contracts",
       y="% of Category's Terminated Contracts",
       x="Obligations After Close Out",
       color="Initial Ceiling")+
  scale_y_continuous(label=percent)+facet_grid(Term~Include2015)
)
```

### After Close Out with all
```{r CloseOutDurAll}

summary(CloseOutAll$MaxClosedDate)

CloseOutAll$PreCloseLength<-CloseOutAll$MaxClosedDate-CloseOutAll$MinOfSignedDate
CloseOutAll$PostCloseSignedLength<-CloseOutAll$MaxBoostDate-CloseOutAll$MaxClosedDate
CloseOutAll$PostCloseCurrentLength<-CloseOutAll$LastCurrentCompletionDate-CloseOutAll$MaxClosedDate

summary(CloseOutAll$PreCloseLength)


(
CloseDurSignedAnnual<-ggplot(CloseOutAll,aes(x=PostCloseSignedLength,color=Include2015))+ #,color=ClosePctCat)) + #
  stat_ecdf(geom = "step")+
    coord_cartesian(ylim=c(0.5,1),xlim=c(0,500))+#+
  # scale_x_log10(label=comma)+
  labs(title="Duration and Close Out Completeness",
       y="Cumulative Distribution % of\nCategory's Closed Out Contracts",
       x="Days Close Out to Final Boost Date",
       color="Close Out Completeness")+
  scale_y_continuous(label=percent)+facet_grid(StartFY~.)+geom_vline(xintercept = 365)+
    theme(legend.position="right")
)

CloseOut<-CloseOutAll %>% filter(Include2015=="Yes")

```

# Termination Examination
The reason for modification code includes both partial and complete terminations. As a way of differentiating complete from partial terminations, we take a closer look at how much spending happened after a contracts last termination. The last termination was used because a contract with both a partial and a complete termination would still qualify as having been completely terminated.


## Analysis with all ontracts

```{r TermInput}
termAll<-criteria %>% dplyr::filter(Term=="Terminated")

summary(termAll$Include2015)

termAll %>% filter(StartFY<=2012 & Include2015=="No")

gridExtra::grid.arrange(
ggplot(termAll, aes(x=StartFY, fill=Include2015))+geom_bar()+facet_wrap(~Include2015),
ggplot(termAll, aes(x=StartFY, y=Action_Obligation, fill=Include2015))+geom_col()+facet_wrap(~Include2015)
)

# summary(termAll)
summary(termAll$ObligatedBeforeMaxTerminatedDate)
summary(termAll$ObligatedAfterMaxTerminatedDate)
summary(termAll$ObligatedOnMaxTerminatedDate)
summary(termAll$MaxTerminatedDate)
sum(termAll$ObligatedBeforeMaxTerminatedDate)
sum(termAll$ObligatedOnMaxTerminatedDate)
sum(termAll$ObligatedAfterMaxTerminatedDate)
sum(termAll$Action_Obligation[termAll$Include2015=="Yes"])
summary(termAll$isDefaultOrCause	)

summary(termAll$qHighCeiling)
  



```
### Calculating Term Percent
```{r TermProcess}

#How often there no net pre-termination obligations
nrow(termAll %>% filter(ObligatedBeforeMaxTerminatedDate<=0))

#How often are contracts terminated on their first day
nrow(termAll %>% filter(MaxTerminatedDate<=MinOfSignedDate) )

termAll$ThroughTerm<-termAll$ObligatedBeforeMaxTerminatedDate+
  termAll$ObligatedOnMaxTerminatedDate[termAll$MaxTerminatedDate<=termAll$MinOfSignedDate]


nrow(termAll %>% filter(ThroughTerm<=0))
nrow(termAll %>% filter(ThroughTerm<ObligatedAfterMaxTerminatedDate))
nrow(termAll %>% filter(ThroughTerm/3<ObligatedAfterMaxTerminatedDate))


termAll$PostTermFloor0<-termAll$ObligatedAfterMaxTerminatedDate
termAll$PostTermFloor0[termAll$PostTermFloor0<0]<-0
termAll$PreTermFloor1<-termAll$ThroughTerm
termAll$PreTermFloor1[termAll$ThroughTerm<1]<-1
termAll$TermPct<-termAll$PostTermFloor0/(termAll$PostTermFloor0+termAll$PreTermFloor1)
summary(termAll$TermPct)
# g<-build_plot(
#   data=termAll, # %>% dplyr::select(PostTermFloor0),
#   chart_geom = "Histogram",
#   share = FALSE,
#   # labels_and_colors=labels_and_colors,
#   # NA, #VAR.ncol
#   x_var="PostTermFloor0", #x_var
#   y_var="Count", #VAR.y.variable
#   # color_var="DecisionTreeDisplay", #color_var
#   # facet_var="DecisionTreeDisplay", #facet_var
#   # column_key=column_key,
#   format=TRUE
# )


termAll$NoPreTermObl<-"Some Net $s Pre-termAll."
termAll$NoPreTermObl[termAll$ObligatedBeforeMaxTerminatedDate<=0]<-"0 Pre-termAll"
termAll$NoPreTermObl<-factor(termAll$NoPreTermObl)


(
TermPct<-ggplot(termAll,aes(x=TermPct,color=Include2015)) +
  stat_ecdf(geom = "step")+
    coord_cartesian(ylim=c(0.9,1),xlim=c(0,1))+
  labs(title="Cumulative Distribution of Terminated Contracts",
       y="% of Terminated Contracts",
       x="Percent of Obligations After Day of Termination"
       )+geom_vline(xintercept = 0.50)
)


(
TermCeilObl<-ggplot(termAll,aes(x=PostTermFloor0+1)) +#,color=qHighCeiling
  stat_ecdf(geom = "step")+stat_ecdf(geom = "step",aes(x=PostTermFloor0+1))+
    coord_cartesian(ylim=c(0.65,1))+#+,xlim=c(0,1e8)
  scale_x_log10(label=comma)+
  labs(title="Cumulative Distribution of Terminated Contracts",
       y="% of Category's Terminated Contracts",
       x="Obligations After Termination",
       color="Initial Ceiling")+
  scale_y_continuous(label=percent)
)+facet_wrap(~Include2015)



```
### Term Percent Categories
```{r TermPCTCat}

termAll$TermPctCat<-Hmisc::cut2(termAll$TermPct,c(0.25,0.5))
summary(termAll$TermPctCat)
# levels(termAll$TermPctCat)[3]<-"[50%+]"
termAll$TermPctCat<-as.character(termAll$TermPctCat)
termAll$TermPctCat[termAll$TermPct==0]<-"[0]"
termAll$TermPctCat[termAll$TermPct==0 & termAll$ObligatedOnMaxTerminatedDate>0]<-"[0]+Last Day Spend"
# termAll$TermPctCat[termAll$TermPct==0 & termAll$ObligatedOnMaxTerminatedDate>0 & termAll$MaxTerminatedDate<=termAll$MinOfSignedDate]<-"[0]+One Day Spend"
termAll$TermPctCat<-factor(termAll$TermPctCat)
summary(termAll$TermPctCat)




levels(termAll$TermPctCat)<-list(
  "[0]+No Last Day Spend"="[0]",
  "[0]+Last Day Spend"="[0]+Last Day Spend",
  "(0%,25%)"="[0.00,0.25)",
  "[25%,50%)"="[0.25,0.50)",
  "[50%+]"="[0.50,1.00]"
)

termAll$TermPartial<-termAll$TermPctCat
levels(termAll$TermPartial)<-list(
  "Complete Termination"=c("[0]+No Last Day Spend","[0]+Last Day Spend","(0%,25%)"),
  "Partial Termination"=c("[25%,50%)","[50%+]")
)
summary(termAll$TermPartial)

termAll$TermPctCat3<-termAll$TermPctCat
levels(termAll$TermPctCat3)<-list(
  "Term Ends Spend"="[0]+No Last Day Spend",
  "Last Day Spend"="[0]+Last Day Spend",
  "Any After"=c("(0%,10%)","[10%,100%)","[100%+]")
)
summary(termAll$TermPctCat)

termAll$FirstDayTerm<-"No"
termAll$FirstDayTerm[termAll$MaxTerminatedDate==termAll$MinOfSignedDate]<-"Yes"

ggplot(termAll, aes(x=StartFY, fill=factor(Include2015)))+geom_bar()+facet_wrap(~TermPctCat,scale="free_y")
ggplot(termAll, aes(x=StartFY, y=Action_Obligation, fill=factor(Include2015)))+geom_col()+facet_wrap(~TermPctCat,scale="free_y")


```

### After Termination Duration

```{r TermPctAll}
termAll$LastCurrentCompletionDate<-na_nonsense_dates(termAll$LastCurrentCompletionDate)
termAll$PreTermLength<-termAll$MaxTerminatedDate-termAll$MinOfSignedDate
termAll$PostTermSignedLength<-termAll$MaxBoostDate-termAll$MaxTerminatedDate
termAll$LastCurrentCompletionDate<-as.Date(termAll$LastCurrentCompletionDate)
termAll$PostTermCurrentLength<-termAll$LastCurrentCompletionDate-termAll$MaxTerminatedDate
# termAll$PreTermLengthFloor1<-termAll$PreTermLength
# termAll$PreTermLengthFloor1[termAll$PreTermLengthFloor1<1]<-1
# termAll$PostTermSignedLengthFloor0<-termAll$PostTermSignedLength
# termAll$PostTermSignedLengthFloor0[termAll$PostTermSignedLengthFloor0<0]<-0


ggplot(termAll,aes(x=PostTermCurrentLength,color=TermPctCat)) +
  stat_ecdf(geom = "step")+
    coord_cartesian(ylim=c(0,1),xlim=c(-1000,2500))+#+,xlim=c(0,1e8)
  # scale_x_log10(label=comma)+
  labs(title="Duration and Termination Completeness",
       y="Cumulative Distribution % of\nCategory's Terminated Contracts",
       x="Days from Termination to Current Completion",
       color="Termination Completeness")+facet_wrap(~Include2015)+
  scale_y_continuous(label=percent)+geom_vline(xintercept = 365)#+facet_wrap(~StartFY)




ggplot(termAll,aes(x=PostTermSignedLength)) +
  stat_ecdf(geom = "step")+
    coord_cartesian(ylim=c(0,1),xlim=c(-1000,2500))+#+,xlim=c(0,1e8)
  # scale_x_log10(label=comma)+
  labs(title="Duration and Termination Completeness",
       y="Cumulative Distribution % of\nCategory's Terminated Contracts",
       x="Days from Termination to Last Boost",
       color="Termination Completeness")+facet_wrap(~Include2015)+
  scale_y_continuous(label=percent)+geom_vline(xintercept = 365)#+facet_wrap(~StartFY)




(
TermDur<-ggplot(termAll,aes(x=PostTermSignedLength,color=TermPctCat)) +
  stat_ecdf(geom = "step")+
    coord_cartesian(ylim=c(0,1),xlim=c(-1000,2500))+#+,xlim=c(0,1e8)
  # scale_x_log10(label=comma)+
  labs(title="Duration and Termination Completeness",
       y="Cumulative Distribution % of\nCategory's Terminated Contracts",
       x="Days from Termination to Last Boost",
       color="Termination Completeness")+facet_wrap(~Include2015)+
  scale_y_continuous(label=percent)+geom_vline(xintercept = 365)#+facet_wrap(~StartFY)
)


term<-termAll %>% filter(Include2015=="Yes")
```




### After Term Spend
```{r TermCrosstab}

term$isDefaultOrCause<-factor(term$isDefaultOrCause)

freq_table("TermPctCat",term)

(
  TermSum<-grouped_barplot("TermPctCat",term)+
    labs(title = "Termination Completion Summary")
)

(
  TermSum<-grouped_barplot("isDefaultOrCause",term)+
    labs(title = "Termination Completion Summary")
)


(
TermOblByCeil<-ggplot(term,aes(x=TermPctCat,fill=TermPctCat,y=Action_Obligation)) +
  geom_col()+scale_y_continuous(labels = comma)+
  # facet_wrap(qHighCeiling~.)+
  labs(title="Termination Completeness by Initial Ceiling",
       y="Contract Obligations",
       x="Termination Completeness")+
  theme(legend.position="None",axis.text.x = element_text(angle=90))
)


(
TermOblByCeil<-ggplot(term,aes(x=TermPctCat,fill=TermPctCat,y=Action_Obligation)) +
  geom_col()+scale_y_continuous(labels = comma)+
  facet_grid(isDefaultOrCause~.,scale="free_y")+
  labs(title="Termination Completeness by Initial Ceiling",
       y="Contract Obligations",
       x="Termination Completeness")+
  theme(legend.position="None",axis.text.x = element_text(angle=90))
)

# ggplot(term,aes(x=NoPreTermObl,fill=TermPctCat)) +facet_grid(TermPctCat3~.,scales="free_y")+
#   geom_bar()+scale_y_continuous(labels = comma)

```

## Other Breakouts.
```{r CompVeh}
(
TermComp<-ggplot(term,aes(x=CompOffr,fill=TermPctCat)) +facet_grid(TermPctCat3~.,scales="free_y")+
  geom_bar()+scale_y_continuous(labels = comma)+
  labs(title="Competition and Termination Completeness",
       y="Contract Count",
       x="Termination Completeness",
       fill="Termination Completeness")
)



(
TermVeh<-ggplot(term,aes(x=Veh,fill=TermPctCat)) +facet_grid(TermPctCat3~.,scales="free_y")+
  geom_bar()+scale_y_continuous(labels = comma)+
  labs(title="Vehicle and Termination Completeness",
       y="Contract Count",
       x="Termination Completeness",
       fill="Termination Completeness")
)


term$Veh3<-term$Veh
levels(term$Veh3)=list(
  "Def/Pur"="Def/Pur",
  "S-IDC"="S-IDC",
  "Other IDV"=c("M-IDC","FSS/GWAC","BPA/BOA" )
)

ggsave(TermSum,file="../Output/TermSum.png")
ggsave(TermDur,file="../Output/TermDur.png")


```


### One Day Closures
```{r OneDay}

(
TermDay1<-ggplot(term %>% filter(FirstDayTerm=="Yes" & !is.na(CompOffr) & !is.na(Veh)),
                 aes(x=TermPctCat3,fill=TermPctCat)) +facet_grid(Veh3~CompOffr)+
  geom_bar()+scale_y_continuous(labels = comma)+
  labs(title="Distribution of Day 1 Final Termination Contracts",
       y="Contract Count",
       x="Competition Category",
       fill="Termination Completeness",
       caption="Unlabeled Vehicle and Competition Excluded")+
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 90))+
    scale_fill_discrete(guide=guide_legend(nrow=2))
)

(
TermOblByStart<-ggplot(term,aes(x=TermPctCat,fill=TermPctCat)) +
  geom_bar()+scale_y_continuous(labels = comma)+
  facet_wrap(StartCY~.)+
  labs(title="Termination Completeness by Initial Ceiling",
       y="Contract Obligations",
       x="Termination Completeness")+
  theme(legend.position="None",axis.text.x = element_text(angle=90))
)


ggsave(TermDay1,file="../Output/TermDay1.png")

partialterm<-term %>% group_by() %>% dplyr::select(CSIScontractID,TermPartial)
summary(partialterm)
def<-left_join(def,partialterm)


```

