---
title: "Defense Services Equations"
output:
  word_document: default
  html_document: default
---

# Presentation of Estimatinating Euation
As described in section 4.3, this paper includes five different equations: likelihood some options are exercised; likelihood all options are exercised; likelihood of a ceiling breach; size of ceiling breach given a breach occurring; and likelihood of termination. The variable indicators used in the equations are listed in Appendix B. Each predictor in the equations has a subscript i, which refers to the individual contract or task order.  The level 2, 3, and 4 variables, covered in Table B 3, are listed at the start of each equation with an α coefficient that varies has a different intercept for each value of with the underlying variable (that is, subscripts j, k, l, m, n, o, and p) and whose calculation is described in the corresponding formula at the end of equation. Subscript j refers to the NAICS subsector, subscript k refers to the NAICS detailed industry, subscript l refers to the service area, subscript m refers to the contracting agency, subscript n refers to the contracting office, subscript o refers to the place of performance, and subscript p refers to the calendar year (for those equations that include it).

The remaining variables have β coefficients, with each non-base level of the categorical variables receiving a separate coefficient. 

```{r setup, echo = FALSE, message=FALSE}
# library(csis360)
# library(ggplot2)
# library(dplyr)
# library(arm)
# library(knitr)
# library(foreign)
# library(stargazer)
# library(texreg)
# library(reshape2)
# library(tidyverse)
# source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")

```

# Options

Note that because we use the complete dataset for exercised options, there's no 1 million entry variant.
```{r Model-OptGrowth, echo = FALSE, message=FALSE}
# Deprecated
load("..//Output//b_SomeOpt25Cv3.rda")
# 

load("..//Output//b_AllOpt26A.rda")

# str(b_AllOpt26A)
# b_AllOpt26A@flist
# ?levels
# 
group_n<-function(m,col){
  format(length(levels(m@flist[[col]])),big.mark=",")
}

sample_n<-function(m){
  format(nrow(m@frame),big.mark=",")
}
texreg::screenreg(list(b_SomeOpt25Cv3,b_AllOpt26A),
custom.model.names = c("Some Opt","All Opt"),                  
                  digits=2)
```
## Some Options Likelihood



$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$
$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$
$β_{`r (b<-1)`}Intercept~+~$
$β_{`r (b<-b+1)`}Detailed~Industry~Salary_{i}~+~$
$β_{`r (b<-b+1)`}Service~Code~Inv.~Rate_{i}~+~$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}~+$
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}~+$
$β_{`r (b<-b+1)`}Paired~Years_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Base_{i}~+$
$β_{`r (b<-b+1)`}Initial~Ceiling:Base_{i}~+~$
$β_{`r (b<-b+1)`}Planned~Duration_{i}~+~$
$(~β_{`r (b<-b+1)`}1~Offer_{i}~+~$
$β_{`r (b<-b+1)`}1~Offer_{i}+~$
$β_{`r (b<-b+1)`}5plus~Offers_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Single–Award_{i}~+~$
$β_{`r (b<-b+1)`}Multi–Award_{i}+~$
$β_{`r (b<-b+1)`}FSS–GWAC_{i}+~$
$β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Other~Fixed–Price_{i}~+~$
$β_{`r (b<-b+1)`}Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}UCA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}ARRA_{i}~+~$
$β_{`r (b<-b+1)`}Disaster_{i}~+~$
$β_{`r (b<-b+1)`}OCO_{i}~)~+~$
$β_{`r (b<-b+1)`}Subsector~HHI_{i}~+$
$β_{`r (b<-b+1)`}Subsector~DoD:US {i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~HHI_{i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~DoD:US_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}~+$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+~$\newline\
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}·Office~Obligations_{i}~+~$\newline\
$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·Paired~Share_{i}~+~$
$(~β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Other~Fixed–Price_{i}~+~$
$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Time~\&~Materials_{i}~+~$
$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·UCA_{i}~)~+$\newline\
$β_{`r (b<-b+1)`}Initial~Base_{i}·Initial~Ceiling:Base_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Share_{i}·Office~Obligations_{i}~+~$
$ϵ_{i},~for~i=1~to~`r sample_n(b_SomeOpt25Cv3)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_SomeOpt25Cv3,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_SomeOpt25Cv3,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_SomeOpt25Cv3,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_SomeOpt25Cv3,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_SomeOpt25Cv3,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_SomeOpt25Cv3,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_SomeOpt25Cv3,"StartFY")`$$

## All Options Likelihood

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$
$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$
$β_{`r (b<-1)`}Intercept~+~$
$β_{`r (b<-b+1)`}Detailed~Industry~Salary_{i}~+~$
$β_{`r (b<-b+1)`}Service~Code~Inv.~Rate_{i}~+~$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}~+$
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Years_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Base_{i}~+$
$β_{`r (b<-b+1)`}Initial~Ceiling:Base_{i}~+~$
$β_{`r (b<-b+1)`}Planned~Duration_{i}~+~$
$(~β_{`r (b<-b+1)`}1~Offer_{i}~+~$
$β_{`r (b<-b+1)`}2–4Offers_{i}+~$
$β_{`r (b<-b+1)`}5plus~Offers_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Single–Award_{i}~+~$
$β_{`r (b<-b+1)`}Multi–Award_{i}+~$
$β_{`r (b<-b+1)`}FSS–GWAC_{i}+~$
$β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Other~Fixed–Price_{i}~+$
$β_{`r (b<-b+1)`}Incentive~Fee_{i}~+$
$β_{`r (b<-b+1)`}Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}UCA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}ARRA_{i}~+~$
$β_{`r (b<-b+1)`}Disaster_{i}~+~$
$β_{`r (b<-b+1)`}OCO_{i}~)~+~$
$β_{`r (b<-b+1)`}Subsector~HHI_{i}~+$
$β_{`r (b<-b+1)`}Subsector~DoD:US {i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~HHI_{i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~DoD:US_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}~+$
$β_{`r (b<-b+1)`}Office~Focus_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+~$
$(~β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Other~Fixed–Price_{i}~+$
$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Comb–Other_{i}~+$\newline\
$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·UCA_{i}~)~+~$
$β_{`r (b<-b+1)`}cln\_OffPSC7_{i}·Office~Focus_{i}~+$\newline\
$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·Paired~Share_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}·Office~Focus_{i}~+~$\newline\
$ϵ_{i},~for~i=1~to~`r sample_n(b_AllOpt26A)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_AllOpt26A,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_AllOpt26A,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_AllOpt26A,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_AllOpt26A,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_AllOpt26A,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_AllOpt26A,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_AllOpt26A,"StartFY")`$$



# Ceiling Breach

```{r Model-CBre, echo = FALSE, message=FALSE}
if(file.exists("..//Output//b_CBre29AB.rda")) load("..//Output//b_CBre29AB.rda")


if(file.exists("..//Output//CBre25A.rda")) load("..//Output//CBre25A.rda")

texreg::screenreg(list(b_CBre29B,n_CBre25A),
                  custom.model.names = c("Breach Likelihood","BreachSize"),                  
                  digits=2)

```

## Breach Likelihood

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$
$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$
$β_{`r (b<-1)`}Intercept~+~$
$β_{`r (b<-b+1)`}Detailed~Industry~Salary_{i}~+~$
$β_{`r (b<-b+1)`}Service~Code~Inv.~Rate_{i}~+~$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}~+$
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Years_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Base_{i}~+$
$β_{`r (b<-b+1)`}Initial~Ceiling:Base_{i}~+~$
$β_{`r (b<-b+1)`}Planned~Duration_{i}~+~$
$(~β_{`r (b<-b+1)`}1~Offer_{i}~+~$
$β_{`r (b<-b+1)`}2–4Offers_{i}+~$
$β_{`r (b<-b+1)`}5plus~Offers_{i}~)~+$
$(~β_{`r (b<-b+1)`}Single–Award_{i}~+~$
$β_{`r (b<-b+1)`}Multi–Award_{i}+~$
$β_{`r (b<-b+1)`}FSS–GWAC_{i}+~$
$β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Other~Fixed–Price_{i}~+$
$β_{`r (b<-b+1)`}Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}UCA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}ARRA_{i}~+~$
$β_{`r (b<-b+1)`}Disaster_{i}~+~$
$β_{`r (b<-b+1)`}OCO_{i}~)~+~$
$β_{`r (b<-b+1)`}Subsector~DoD:US {i}~+$
$β_{`r (b<-b+1)`}Detailed~Ind.~HHI_{i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~DoD:US_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}~+~$
$β_{`r (b<-b+1)`}Office~Focus_{i}~+$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+~$
$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·Paired~Actions_{i}~+$\newline\
$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·Planned~Duration_{i}~+~$
$ϵ_{i},~for~i=  1~to~`r sample_n(b_CBre29B)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_CBre29B,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_CBre29B,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_CBre29B,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_CBre29B,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_CBre29B,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_CBre29B,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_CBre29B,"StartFY")`$$

## Breach Size

$Estimated~Log(y_i)~=~α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+~α^{NAICS6:NAICS3:ServArea}_{l[i]}~+$
$α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+~α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+~$
$β_{`r (b<-1)`}Intercept~+$
$β_{`r (b<-b+1)`}Detailed~Industry~Salary_{i}~+~$
$β_{`r (b<-b+1)`}Service~Code~Inv.~Rate_{i}~+~$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}~+~$
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}~+$
$β_{`r (b<-b+1)`}Paired~Years_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Base_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Ceiling:Base_{i}~+$
$β_{`r (b<-b+1)`}Planned~Duration_{i}~+~$
$(~β_{`r (b<-b+1)`}1~Offer_{i}~+~$
$β_{`r (b<-b+1)`}2–4Offers_{i}+~$
$β_{`r (b<-b+1)`}5plus~Offers_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Single–Award_{i}~+$
$β_{`r (b<-b+1)`}Multi–Award_{i}~+~$
$β_{`r (b<-b+1)`}FSS–GWAC_{i}+~$
$β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Other~Fixed–Price_{i}~+~$
$β_{`r (b<-b+1)`}Incentive~Fee_{i}~+$
$β_{`r (b<-b+1)`}Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Time~\&~Materials_{i}~+~$
$β_{`r (b<-b+1)`}UCA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}ARRA_{i}~+~$
$β_{`r (b<-b+1)`}Disaster_{i}~+~$
$β_{`r (b<-b+1)`}OCO_{i}~)~+~$
$β_{`r (b<-b+1)`}Subsector~DoD:US {i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~HHI_{i}~+$
$β_{`r (b<-b+1)`}Detailed~Ind.~DoD:US_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}~+~$
$β_{`r (b<-b+1)`}Office~Focus_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}·Paired~Actions_{i}~+~ϵ_{i}~+~$\newline\
$ϵ_{i},~for~i=  1~to~`r sample_n(n_CBre25A)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(n_CBre25A,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(n_CBre25A,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(n_CBre25A,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(n_CBre25A,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(n_CBre25A,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(n_CBre25A,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(n_CBre25A,"StartFY")`$$

#Terminations

```{r Model-Term, echo = FALSE, message=FALSE}
 load("..//Output//term25B.rdata")

texreg::screenreg(list(term25B),
                  custom.model.names = c("Termination Likelihood"),                  
                  digits=2)

```

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$
$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$
$β_{`r (b<-1)`}Intercept_{i}~+~$
$β_{`r (b<-b+1)`}Detailed~Industry~Salary_{i}~+~$
$β_{`r (b<-b+1)`}Service~Code~Inv.~Rate_{i}~+~$
$β_{`r (b<-b+1)`}Office~Perf.-Based_{i}~+$
$β_{`r (b<-b+1)`}Office~Serv.~Code~Exp.~\%_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Years_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Actions_{i}~+~$
$β_{`r (b<-b+1)`}Initial~Base_{i}~+$
$β_{`r (b<-b+1)`}Initial~Ceiling:Base_{i}~+$
$β_{`r (b<-b+1)`}Planned~Duration_{i}~+~$
$(~β_{`r (b<-b+1)`}1~Offer_{i}~+~$
$β_{`r (b<-b+1)`}2–4Offers_{i}+~$
$β_{`r (b<-b+1)`}5plus~Offers_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Single–Award_{i}~+~$
$β_{`r (b<-b+1)`}Multi–Award_{i}+~$
$β_{`r (b<-b+1)`}FSS–GWAC_{i}+~$
$β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}Other~Fixed–Price_{i}~+$
$β_{`r (b<-b+1)`}Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}Comb–Other_{i}~+~$
$β_{`r (b<-b+1)`}Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}UCA_{i}~)~+~$
$(~β_{`r (b<-b+1)`}ARRA_{i}~+~$
$β_{`r (b<-b+1)`}Disaster_{i}~+~$
$β_{`r (b<-b+1)`}OCO_{i}~)~+~$
$β_{`r (b<-b+1)`}Subsector~HHI_{i}~+$
$β_{`r (b<-b+1)`}Subsector~DoD:US {i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~HHI_{i}~+~$
$β_{`r (b<-b+1)`}Detailed~Ind.~DoD:US_{i}~+~$
$β_{`r (b<-b+1)`}Office~Obligations_{i}~+$
$β_{`r (b<-b+1)`}Office~Focus_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Share_{i}~+~$
$(~β_{`r (b<-b+1)`}Paired~Years_{i}·Other~Fixed–Price_{i}~+$
$β_{`r (b<-b+1)`}Paired~Years_{i}·Incentive~Fee_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Years_{i}·Comb–Other_{i}~+$
$β_{`r (b<-b+1)`}Paired~Years_{i}·Other~Cost–Based_{i}~+~$
$β_{`r (b<-b+1)`}Paired~Years_{i}·Time~\&~Materials_{i}~+$
$β_{`r (b<-b+1)`}Paired~Years_{i}·UCA_{i}~)~+~ϵ_{i}~+~ϵ_{i},~~~~for~i=1~to~`r sample_n(term25B)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(term25B,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(term25B,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(term25B,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(term25B,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(term25B,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(term25B,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(term25B,"StartFY")`$$
