---
title: "Defense Services Equations"
output:
  word_document: default
  html_document: default
---

# Setup
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.
```{r Libraries, echo = FALSE, message=FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(knitr)
library(foreign)
library(stargazer)
library(texreg)
library(reshape2)
library(tidyverse)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")

```

# Options

Note that because we use the complete dataset for exercised options, there's no 1 million entry variant.
```{r Model-OptGrowth, echo = FALSE, message=FALSE}
# Deprecated
load("..//Output//b_SomeOpt25Cv3.rda")
# 

load("..//Output//b_AllOpt26A.rda")

# str(b_AllOpt26A)
# b_AllOpt26A@flist
# ?levels
# 
group_n<-function(m,col){
  format(length(levels(m@flist[[col]])),big.mark=",")
}

sample_n<-function(m){
  format(nrow(m@frame),big.mark=",")
}
texreg::screenreg(list(b_SomeOpt25Cv3,b_AllOpt26A),
custom.model.names = c("Some Opt","All Opt"),                  
                  digits=2)
```
## Some Options Likelihood



$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$

$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$

$β_{`r (b<-1)`}Intercept~+~β_{`r (b<-b+1)`}cln\_US6sal_{i}~+~β_{`r (b<-b+1)`}cln\_PSCrate_{i}~+~β_{`r (b<-b+1)`}cp\_OffPerf7_{i}~+$

$β_{`r (b<-b+1)`}cp\_OffPSC7_{i}~+β_{`r (b<-b+1)`}cn\_PairHist7_{i}~+~β_{`r (b<-b+1)`}cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_Base_{i}~+$

$β_{`r (b<-b+1)`}clr\_Ceil2Base_{i}~+~β_{`r (b<-b+1)`}cln\_Days_{i}~+~(~β_{`r (b<-b+1)`}1Offr_{i}~+~β_{`r (b<-b+1)`}2–4Offr_{i}+~β_{`r (b<-b+1)`}5plusOffr_{i}~)~+$

$(~β_{`r (b<-b+1)`}SIDC_{i}~+~β_{`r (b<-b+1)`}MIDC_{i}+~β_{`r (b<-b+1)`}FSS–GWAC_{i}+~β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+(~β_{`r (b<-b+1)`}Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}Incentive_{i}~+~β_{`r (b<-b+1)`}Comb–Other_{i}~+~β_{`r (b<-b+1)`}Other\_CB_{i}~+~β_{`r (b<-b+1)`}TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}UCA_{i}~)~+~(~+~β_{`r (b<-b+1)`}ARRA_{i}~+~β_{`r (b<-b+1)`}Disaster_{i}~+~β_{`r (b<-b+1)`}OCO_{i}~)~+~β_{`r (b<-b+1)`}cln\_Def3HHI_{i}~+$

$β_{`r (b<-b+1)`}clr\_Def3toUS{i}~+~β_{`r (b<-b+1)`}cln\_Def6HHI_{i}~+~β_{`r (b<-b+1)`}clr\_Def6toUS_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}~+$

$β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+~β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+~β_{`r (b<-b+1)`}cp\_OffPSC7_{i}·cln\_OffObl7_{i}~+$

$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·cp\_PairObl7_{i}~+$

$(~β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Other\_FP_{i}~+~β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Incentive_{i}~+$

$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Comb–Other_{i}~+~β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·Other\_CB_{i}~+$

$β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·TM–LH–FPLOE_{i}~+~β_{`r (b<-b+1)`}cn\_OffPerf7_{i}·UCA_{i}~)~+$

$β_{`r (b<-b+1)`}cln\_Base_{i}·clr\_Ceil2Base_{i}~+~β_{`r (b<-b+1)`}cp\_PairObl7_{i}·cln\_OffObl7_{i}~+~ϵ_{i},$

$for~i=1~to~`r sample_n(b_SomeOpt25Cv3)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_SomeOpt25Cv3,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_SomeOpt25Cv3,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_SomeOpt25Cv3,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_SomeOpt25Cv3,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_SomeOpt25Cv3,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_SomeOpt25Cv3,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_SomeOpt25Cv3,"StartFY")`$$

## All Options Likelihood

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$

$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$

$β_{`r (b<-1)`}Intercept~+~β_{`r (b<-b+1)`}cln\_US6sal_{i}~+~β_{`r (b<-b+1)`}cln\_PSCrate_{i}~+~β_{`r (b<-b+1)`}cp\_OffPerf7_{i}~+$

$β_{`r (b<-b+1)`}cp\_OffPSC7_{i}~+~β_{`r (b<-b+1)`}cn\_PairHist7_{i}~+~β_{`r (b<-b+1)`}cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_Base_{i}~+$

$β_{`r (b<-b+1)`}clr\_Ceil2Base_{i}~+~β_{`r (b<-b+1)`}cln\_Days_{i}~+~(~β_{`r (b<-b+1)`}1Offr_{i}~+~β_{`r (b<-b+1)`}2–4Offr_{i}+~β_{`r (b<-b+1)`}5plusOffr_{i}~)~+$

$(~β_{`r (b<-b+1)`}SIDC_{i}~+~β_{`r (b<-b+1)`}MIDC_{i}+~β_{`r (b<-b+1)`}FSS–GWAC_{i}+~β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+(~β_{`r (b<-b+1)`}Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}Incentive_{i}~+β_{`r (b<-b+1)`}Comb–Other_{i}~+~β_{`r (b<-b+1)`}Other\_CB_{i}~+~β_{`r (b<-b+1)`}TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}UCA_{i}~)~+~(~β_{`r (b<-b+1)`}ARRA_{i}~+~β_{`r (b<-b+1)`}Disaster_{i}~+~β_{`r (b<-b+1)`}OCO_{i}~)~+~β_{`r (b<-b+1)`}cln\_Def3HHI_{i}~+$

$β_{`r (b<-b+1)`}clr\_Def3toUS{i}~+~β_{`r (b<-b+1)`}cln\_Def6HHI_{i}~+~β_{`r (b<-b+1)`}clr\_Def6toUS_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}~+$

$β_{`r (b<-b+1)`}cln\_OffFocus_{i}~+~β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+~(~β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Incentive_{i}~+~β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Comb–Other_{i}~+$

$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·Other\_CB_{i}~+~β_{`r (b<-b+1)`}cn\_PSCrate_{i}·TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}cn\_PSCrate_{i}·UCA_{i}~)~+~β_{`r (b<-b+1)`}cln\_OffPSC7_{i}·cln\_OffFocus_{i}~+$

$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·cp\_PairObl7_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}·cln\_OffFocus_{i}~+~ϵ_{i},$

$for~i=1~to~`r sample_n(b_AllOpt26A)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_AllOpt26A,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_AllOpt26A,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_AllOpt26A,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_AllOpt26A,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_AllOpt26A,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_AllOpt26A,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_AllOpt26A,"StartFY")`$$



# Ceiling Breach

```{r Model-CBre, echo = FALSE, message=FALSE}
if(file.exists("..//Output//b_CBre29AB.rda")) load("..//Output//b_CBre29AB.rda")


if(file.exists("..//Output//CBre25A.rda")) load("..//Output//CBre25A.rda")

stargazer(b_CBre29B,n_CBre25A,type="text",digits=2)
texreg::screenreg(list(b_CBre29B,n_CBre25A),
                  custom.model.names = c("Breach Likelihood","BreachSize"),                  
                  digits=2)

```

## Breach Likelihood

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$

$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$

$β_{`r (b<-1)`}Intercept~+~β_{`r (b<-b+1)`}cln\_US6sal_{i}~+~β_{`r (b<-b+1)`}cln\_PSCrate_{i}~+~β_{`r (b<-b+1)`}cp\_OffPerf7_{i}~+$

$β_{`r (b<-b+1)`}cp\_OffPSC7_{i}~+~β_{`r (b<-b+1)`}cn\_PairHist7_{i}~+~β_{`r (b<-b+1)`}cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_Base_{i}~+$

$β_{`r (b<-b+1)`}clr\_Ceil2Base_{i}~+~β_{`r (b<-b+1)`}cln\_Days_{i}~+~(~β_{`r (b<-b+1)`}1Offr_{i}~+~β_{`r (b<-b+1)`}2–4Offr_{i}+~β_{`r (b<-b+1)`}5plusOffr_{i}~)~+$

$(~β_{`r (b<-b+1)`}SIDC_{i}~+~β_{`r (b<-b+1)`}MIDC_{i}+~β_{`r (b<-b+1)`}FSS–GWAC_{i}+~β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+(~β_{`r (b<-b+1)`}Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}Incentive_{i}~+~β_{`r (b<-b+1)`}Comb–Other_{i}~+~β_{`r (b<-b+1)`}Other\_CB_{i}~+~β_{`r (b<-b+1)`}TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}UCA_{i}~)~+~(~β_{`r (b<-b+1)`}ARRA_{i}~+~β_{`r (b<-b+1)`}Disaster_{i}~+~β_{`r (b<-b+1)`}OCO_{i}~)~+~β_{`r (b<-b+1)`}clr\_Def3toUS{i}~+$

$β_{`r (b<-b+1)`}cln\_Def6HHI_{i}~+~β_{`r (b<-b+1)`}clr\_Def6toUS_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}~+~β_{`r (b<-b+1)`}cln\_OffFocus_{i}~+$

$β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+~β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·cln\_PairCA_{i}~+$

$β_{`r (b<-b+1)`}cln\_OffPerf7_{i}·cln\_Days_{i}~+~ϵ_{i},~~~for~i=  1~to~`r sample_n(b_CBre29B)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(b_CBre29B,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(b_CBre29B,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(b_CBre29B,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(b_CBre29B,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(b_CBre29B,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(b_CBre29B,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(b_CBre29B,"StartFY")`$$

## Breach Size

$Estimated~Log(y_i)~=~α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+~α^{NAICS6:NAICS3:ServArea}_{l[i]}~+$

$α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+~α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+~β_{`r (b<-1)`}Intercept~+$

$β_{`r (b<-b+1)`}cln\_US6sal_{i}~+~β_{`r (b<-b+1)`}cln\_PSCrate_{i}~+~β_{`r (b<-b+1)`}cp\_OffPerf7_{i}~+~β_{`r (b<-b+1)`}cp\_OffPSC7_{i}~+$

$β_{`r (b<-b+1)`}cn\_PairHist7_{i}~+~β_{`r (b<-b+1)`}cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_Base_{i}~+~β_{`r (b<-b+1)`}clr\_Ceil2Base_{i}~+$

$β_{`r (b<-b+1)`}cln\_Days_{i}~+~(~β_{`r (b<-b+1)`}1Offr_{i}~+~β_{`r (b<-b+1)`}2–4Offr_{i}+~β_{`r (b<-b+1)`}5plusOffr_{i}~)~+~(~β_{`r (b<-b+1)`}SIDC_{i}~+$

$β_{`r (b<-b+1)`}MIDC_{i}~+~β_{`r (b<-b+1)`}FSS–GWAC_{i}+~β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+(~β_{`r (b<-b+1)`}Other\_FP_{i}~+~β_{`r (b<-b+1)`}Incentive_{i}~+$

$β_{`r (b<-b+1)`}Comb–Other_{i}~+~β_{`r (b<-b+1)`}Other\_CB_{i}~+~β_{`r (b<-b+1)`}TM–LH–FPLOE_{i}~+~β_{`r (b<-b+1)`}UCA_{i}~)~+$

$(~β_{`r (b<-b+1)`}ARRA_{i}~+~β_{`r (b<-b+1)`}Disaster_{i}~+~β_{`r (b<-b+1)`}OCO_{i}~)~+~β_{`r (b<-b+1)`}clr\_Def3toUS{i}~+~β_{`r (b<-b+1)`}cln\_Def6HHI_{i}~+$

$β_{`r (b<-b+1)`}clr\_Def6toUS_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}~+~β_{`r (b<-b+1)`}cln\_OffFocus_{i}~+~β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+$

$β_{`r (b<-b+1)`}cp\_OffPerf7_{i}·cln\_PairCA_{i}~+~ϵ_{i}~+~ϵ_{i}, for~i=  1~to~`r sample_n(n_CBre25A)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(n_CBre25A,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(n_CBre25A,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(n_CBre25A,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(n_CBre25A,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(n_CBre25A,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(n_CBre25A,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(n_CBre25A,"StartFY")`$$

#Terminations

```{r Model-Term, echo = FALSE, message=FALSE}
 load("..//Output//term25B.rdata")

stargazer(term25B,type="text",digits=2)
texreg::screenreg(list(term25B),
                  custom.model.names = c("Termination Likelihood"),                  
                  digits=2)

```

$Estimated~Probability(y_i = 1)~=~Logit^{-1}(α~+~α^{NAICS3}_{j[i]}~+~α^{NAICS6:NAICS3}_{k[i]}~+$

$α^{NAICS6:NAICS3:ServArea}_{l[i]}~+~α^{Agency}_{m[i]}~+~α^{Office:Agency}_{n[i]}~+α^{Place}_{o[i]}~+~α^{StartFY}_{p[i]}~+$

$β_{`r (b<-1)`}Intercept_{i}~+~β_{`r (b<-b+1)`}cln\_US6sal_{i}~+~β_{`r (b<-b+1)`}cln\_PSCrate_{i}~+~β_{`r (b<-b+1)`}cp\_OffPerf7_{i}~+$

$β_{`r (b<-b+1)`}cp\_OffPSC7_{i}~+~β_{`r (b<-b+1)`}cn\_PairHist7_{i}~+~β_{`r (b<-b+1)`}cln\_PairCA_{i}~+~β_{`r (b<-b+1)`}cln\_Base_{i}~+$

$β_{`r (b<-b+1)`}clr\_Ceil2Base_{i}~+~β_{`r (b<-b+1)`}cln\_Days_{i}~+~(~β_{`r (b<-b+1)`}1Offr_{i}~+~β_{`r (b<-b+1)`}2–4Offr_{i}+~β_{`r (b<-b+1)`}5plusOffr_{i}~)~+$

$(~β_{`r (b<-b+1)`}SIDC_{i}~+~β_{`r (b<-b+1)`}MIDC_{i}+~β_{`r (b<-b+1)`}FSS–GWAC_{i}+~β_{`r (b<-b+1)`}BPA–BOA_{i}~)~+(~β_{`r (b<-b+1)`}Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}Incentive_{i}~+~β_{`r (b<-b+1)`}Comb–Other_{i}~+~β_{`r (b<-b+1)`}Other\_CB_{i}~+~β_{`r (b<-b+1)`}TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}UCA_{i}~)~+~(~β_{`r (b<-b+1)`}ARRA_{i}~+~β_{`r (b<-b+1)`}Disaster_{i}~+~β_{`r (b<-b+1)`}OCO_{i}~)~+~β_{`r (b<-b+1)`}cln\_Def3HHI_{i}~+$

$β_{`r (b<-b+1)`}clr\_Def3toUS{i}~+~β_{`r (b<-b+1)`}cln\_Def6HHI_{i}~+~β_{`r (b<-b+1)`}clr\_Def6toUS_{i}~+~β_{`r (b<-b+1)`}cln\_OffObl7_{i}~+$

$β_{`r (b<-b+1)`}cln\_OffFocus_{i}~+~β_{`r (b<-b+1)`}cp\_PairObl7_{i}~+~(~β_{`r (b<-b+1)`}cn\_PairHist7_{i}·Other\_FP_{i}~+$

$β_{`r (b<-b+1)`}cn\_PairHist7_{i}·Incentive_{i}~+~β_{`r (b<-b+1)`}cn\_PairHist7_{i}·Comb–Other_{i}~+$

$β_{`r (b<-b+1)`}cn\_PairHist7_{i}·Other\_CB_{i}~+~β_{`r (b<-b+1)`}cn\_PairHist7_{i}·TM–LH–FPLOE_{i}~+$

$β_{`r (b<-b+1)`}cn\_PairHist7_{i}·UCA_{i}~)~+~ϵ_{i}~+~ϵ_{i},~~~~for~i=1~to~`r sample_n(term25B)`$

$$a^{NAICS3}_{j}\sim~N(μ_{α},σ^{2}_{α}),~for~j= 1~to~`r group_n(term25B,"NAICS3")`;$$
$$a^{NAICS3:NAICS6}_{k}\sim~N(μ_{α},σ^{2}_{α}),~for~k= 1~to~`r group_n(term25B,"NAICS6:NAICS3")`;$$
$$a^{NAICS3:NAICS6:ServArea}_{l}\sim~N(μ_{α},σ^{2}_{α}),~for~l= 1~to~`r group_n(term25B,"ServArea:(NAICS6:NAICS3)")`;$$
$$a^{Agency}_{m}\sim~N(μ_{α},σ^{2}_{α}),~for~m= 1~to~`r group_n(term25B,"Agency")`$$
$$a^{Agency:Office}_{n}\sim~N(μ_{α},σ^{2}_{α}),~for~n= 1~to~`r group_n(term25B,"Office:Agency")`$$
$$a^{Place}_{o}\sim~N(μ_{α},σ^{2}_{α}),~~~~for~n= 1~to~`r group_n(term25B,"Place")`$$
$$a^{StartFY}_{p}\sim~N(μ_{α},σ^{2}_{α}),~for~o= 1~to~`r group_n(term25B,"StartFY")`$$
