---
title: "Serices Results Summary"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, July 11, 2019"
---

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(readr)
library(texreg)
library(reshape2)
library(tidyverse)
source("C:/Users/JGraham/Documents/CSIS/Vendor/Scripts/DIIGstat.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.


First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.


```{r ReadInData, echo = TRUE}
if(!exists("def_serv")) load("../data/clean/transformed_def_serv.Rdata")
if(!exists("serv_smp")) load(file="../data/clean/def_sample.Rdata")


```

# Pre-Model Graphs
None at present.
# Models
## Loading Models
### Exercised Options
Note that because we use the complete dataset for exercised options, there's no 1 million entry variant.
```{r Model-OptGrowth}
# if(file.exists("..//Output//p_Opt_12C.rdata")) load("..//Output//p_Opt_12C.rdata")
# 
# 
# if(!exists("p_Opt_12C")){
#   p_Opt_12C <- glm (data=serv_opt,
#                     lp_OptGrowth ~  cl_US6_avg_sal_lag1Const + 
#                       cl_CFTE+ c_pPBSC+c_pOffPSC+
#                       c_pairHist+cl_pairCA +
#                       cl_Ceil + capped_cl_Days+
#                       Comp1or5+
#                       Veh+
#                       PricingUCA+
#                       Crisis+
#                       cl_def6_HHI_lag1+cl_def6_ratio_lag1+
#                       cl_def3_HHI_lag1+cl_def3_ratio_lag1+
#                       c_pMarket+
#                       cl_OffVol+cl_office_naics_hhi_k #,
#                     # verbose=1
#                     )
#   glmer_examine(p_Opt_12C)
#   save(p_Opt_12C,file="..//Output//p_Opt_12C.rdata")
# }
# 
# stargazer::stargazer(p_Opt_12C,type="text",
#                      digits=2)

#Considering 
# write.csv(exp(summary(p_Opt_12C)$coefficients[,1])-1,file="../Output/exp_p_Opt_12C.csv")
# p_Opt_12C_exp<-log_analysis(p_Opt_12C)

glmer_examine(p_Opt_12C,display=TRUE)
stargazer::stargazer(p_Opt_12C,type="text",
                       digits=2)

load("..//Output//b_SomeOpt25A.rda")
load("..//Output//b_AllOpt25A.rda")
glmer_examine(b_SomeOpt25A)
glmer_examine(b_AllOpt25A)

stargazer::stargazer(b_SomeOpt25A, b_AllOpt25A, type = "text", digits = 2)

```


### Ceiling Breach

```{r Model-CBre}
if(file.exists("..//Output//b_CBre28AB.rda")) load("..//Output//b_CBre28AB.rda")

if(!exists("b_CBre28B")){
   b_CBre28A <- glmer(data=serv_smp, b_CBre ~  cl_US6_avg_sal_lag1Const +
                       cl_CFTE+ c_pPBSC+c_pOffPSC+
                       c_pairHist+cl_pairCA+
                       cl_Base + cl_Base2Ceil + cl_Days+
                       Comp1or5+
                       Veh+
                       PricingUCA+
                       Crisis+
                       cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                       #cl_def3_HHI_lag1+
                       cl_def3_ratio_lag1+
                       c_pMarket+
                       cl_OffVol+
                       #cl_office_naics_hhi_k+
                       c_pPBSC:cl_pairCA+
                       #c_pPBSC:c_pMarket+
                       c_pPBSC:cl_Days+
                       # cl_Base2Ceil:cl_Base+
                       (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+
                       (1 | Agency/Office) +
                       (1 | PlaceCountryISO3)+
                       (1 | StartFY),
                     family=binomial(link="logit"),
                     verbose=TRUE)

  b_CBre28B <- glmer(data=serv_smp1m, b_CBre ~  cl_US6_avg_sal_lag1Const +
                       cl_CFTE+ c_pPBSC+c_pOffPSC+
                       c_pairHist+cl_pairCA+
                       cl_Base + cl_Base2Ceil + cl_Days+
                       Comp1or5+
                       Veh+
                       PricingUCA+
                       Crisis+
                       cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                       #cl_def3_HHI_lag1+
                       cl_def3_ratio_lag1+
                       c_pMarket+
                       cl_OffVol+
                       #cl_office_naics_hhi_k+
                       c_pPBSC:cl_pairCA+
                       #c_pPBSC:c_pMarket+
                       c_pPBSC:cl_Days+
                       # cl_Base2Ceil:cl_Base+
                       (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+
                       (1 | Agency/Office) +
                       (1 | PlaceCountryISO3)+
                       (1 | StartFY),
                     family=binomial(link="logit"),
                     verbose=TRUE)
  save(b_CBre28A,b_CBre28B,file="..\\output\\b_CBre28AB.rda")

}
glmer_examine(b_CBre28B)

if(file.exists("..//Output//CBre25A.rda")) load("..//Output//CBre25A.rda")

if(!exists("n_CBre25A")){
    
  n_CBre25A <- lmer(data=serv_breach, ln_CBre ~ cln_US6sal + 
                      cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                      cn_PairHist7+cln_PairCA+
                      cln_Base + clr_Ceil2Base + cln_Days+
                      Comp+
                      Veh+
                      Pricing+
                      Crisis+
                      cln_Def6HHI+clr_Def6toUS+
                      #cln_Def3HHI+
                      clr_Def3toUS+
                      cp_PairObl7+
                      cln_OffObl7+ 
                      #cl_office_NAICS6_hhi_kc+
                      cp_OffPerf7:cln_PairCA+
                      (1 | NAICS3/NAICS6/ServArea)+  
                      (1 | Agency/Office) +
                      (1 | Place)+ 
                      (1 | StartFY),
                    verbose=TRUE)
  
  save(n_CBre25A,file="..\\output\\n_CBre25A.rda")
}


glmer_examine(n_CBre25A)

# if(!exists("b_CBre28B_restart")){
#   pars<-get_pars(b_CBre25A)
#   b_CBre25A_restart <- update(b_CBre25A, 
#                                      start=pars,
#                                      verbose=1)
#   save(b_CBre25A,
#        b_CBre25A_restart,
#        file="..//output//b_CBre25A.rdata")
# }
# glmer_examine(b_CBre25A_restart)



# 
# save(b_CBre25A,
#      b_CBre25A.devfun,
#      CBre_Cons_13_scgrad,
#      b_CBre25A.restart,
#      CBre_Comp_13B,
#      CBre_Comp_13B.devfun,
#      CBre_Comp_13B.restart,
#      file="..//output//b_CBre25A.rdata")

# source(system.file("utils", "allFit.R", package="lme4"))
# b_CBre25A.all <- allFit(b_CBre25A)
# b_CBre25A_ss_cons <- summary(b_CBre25A.all)



# glmer_examine(b_CBre25A.restart,display=TRUE)
# odds_ratio(b_CBre25A.restart,"b_CBre25A")

```
"Model failed to converge with max|grad| = 0.00135328 (tol = 0.001, component 1)"" - AllOpt25A


### Termination

```{r Model-Term}
if(file.exists("..//Output//term25B.rdata")) load("..//Output//term25B.rdata")

if(!exists("term25B")){
  term25A <- glmer(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                     cl_CFTE+ c_pPBSC+c_pOffPSC+
                     c_pairHist+cl_pairCA +
                     cl_Base + cl_Days+ cl_Base2Ceil+
                     Comp1or5+
                     Veh+
                     PricingUCA+
                     Crisis+
                     cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                     cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                     c_pMarket+
                     cl_OffVol+cl_office_naics_hhi_k +
                     c_pairHist:PricingUCA+ 
                     # cl_Base2Ceil:cl_Ceil+
                     (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  
                     (1 | Agency/Office) +
                     (1 | PlaceCountryISO3)+ 
                     (1 | StartFY),
                   family=binomial(link="logit"),
                   verbose=TRUE)
  glmer_examine(term25A,display = TRUE)
  
  term25B <- glmer(data=serv_smp1m, b_Term ~ cl_US6_avg_sal_lag1Const + 
                     cl_CFTE+ c_pPBSC+c_pOffPSC+
                     c_pairHist+cl_pairCA +
                     cl_Base + cl_Days+ cl_Base2Ceil+
                     Comp1or5+
                     Veh+
                     PricingUCA+
                     Crisis+
                     cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                     cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                     c_pMarket+
                     cl_OffVol+cl_office_naics_hhi_k +
                     c_pairHist:PricingUCA+ 
                     (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  
                     (1 | Agency/Office) +
                     (1 | PlaceCountryISO3)+ 
                     (1 | StartFY),
                   family=binomial(link="logit"),
                   verbose=TRUE)
  
  save(term25A,term25B,file="..\\output\\term25AB.rdata")
}

glmer_examine(term25A)

```

## Tables for Conference Paper
```{r CoefficientList}
study_coef_list<-get_coef_list(limit="services")

all_coef_list<-get_coef_list()

```

### Study Variables Only
```{r StudyVariableSummary}

texreg::htmlreg(list(p_Opt_12C,b_CBre12C_1m,term25A),file="..//Output//study_var_model_lvl1.html",
                single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                #groups = list(
                 #             "Services Complexity" = 2:3,
                  #            "Office Capacity" =4:5,
                   #           "Past Relationship"=6:7
                    #          ),
                custom.coef.map=study_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 6: Study Variables and Outcomes",
                caption.above=TRUE)

```


### All Level 1 Variables

```{r AllVariableSummary}

#Absolute Exercised Options
  stargazer::stargazer(#p_Opt_12C,
                       b_CBre12C_1m,term25A,
                       single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(p_Opt_12C,b_CBre12C_1m,term25A),file="..//Output//all_var_model_lvl1.html",
                single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                              "Services Complexity" = 2:3,
                              "Office Capacity" =4:5,
                              "Past Relationship"=6:7,
                              "Contract Characteristics"=8:25,
                              "NAICS Characteristics" =26:29,
                                                            "Office Characteristics" =30:32
                              
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 7: All Variables and Outcomes",
                caption.above=TRUE)



```
## Tables for Final Paper

### Exercised Options

### Ceiling Breach
```{r CeilingResults}

  stargazer::stargazer(#p_Opt_12C,
                       b_CBre28B,n_CBre25A,
                       single.row = TRUE,
                custom.model.name=c("Breach Frequency (Logit)","Breach Size for Breached Contracts (Regression"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(b_CBre28B,n_CBre25A),file="..//Output//ceiling_breaches.html",
                single.row = TRUE,
                custom.model.name=c("Likelihood\n(Logit)","Size Given Breach\n(Regression)"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                              # "Services Complexity" = 2:3,
                              # "Office Capacity" =4:5,
                              # "Past Relationship"=6:7,
                  "Services Complexity"=2:7,
                              "Contract Characteristics"=8:26,
                                                "NAICS/Office Characteristics" =27:31,

                              # "NAICS Characteristics" =27:29,
                              # "Office Characteristics" =30:31,
                              "Interactions"=32:33
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 8: Ceiling Breaches",
                caption.above=TRUE)



```

### Terminations

```{r AllVariableSummary}

#Absolute Exercised Options
  stargazer::stargazer(#p_Opt_12C,
                       term25B,
                       single.row = TRUE,
                custom.model.name=c("Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(term25B),file="..//Output//terminations.html",
                single.row = TRUE,
                custom.model.name=c("Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                              "Services Complexity" = 2:3,
                              "Office Capacity" =4:5,
                              "Past Relationship"=6:7,
                              "Contract Characteristics"=8:26,
                              "NAICS Characteristics" =27:30,
                              "Office Characteristics" =31:33,
                              "Interactions"=34:39
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 7: Terminations",
                caption.above=TRUE)



```

### Exercised Options
```{r OptionsTableGeneration}
stargazer::stargazer(b_SomeOpt25A, b_AllOpt25A,
                       single.row = TRUE,
                custom.model.name=c("Exercised Options"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(b_SomeOpt25A, b_AllOpt25A),file="..//Output//options.html",
                single.row = TRUE,
                custom.model.name=c("Some Options Exercised", "All Options Exercised"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                               "Services Complexity" = 2:3,
                               "Office Capacity" =4:5,
                               "Past Relationship"=6:7,
                               "Contract Characteristics"=8:26,
                               "NAICS Characteristics" =27:30,
                               "Office Characteristics" =31:33,
                               "Interactions"=34:39
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 6: Exercised Options",
                caption.above=TRUE)
```


## Odds Ratios

### Exercised Options
```{r Odds-Opt}


# comp.or<-odds_ratio(b_CBre28B,"b_CBre28B","Both","Both")
# write.csv(get_study_variables_odds_ratio(comp.or),file="..//output//ceiling_breach_study_odds_ratio.csv",row.names=FALSE)
# get_icc(b_CBre28B)
# 
# #https://www.lcampanelli.org/mixed-effects-modeling-lme4/
# gridExtra::grid.arrange(dotplot(ranef(b_CBre28B, condVar = T), strip = T, scales=list(relation='free'))$Agency,
#              nrow=1)

comp.or<-odds_ratio(b_SomeOpt25A,"b_SomeOpt25A","Both","Both")
write.csv(get_study_variables_odds_ratio(comp.or),file="..//output//some_exer_opt_study_odds_ratio.csv",row.names=FALSE)
get_icc(b_SomeOpt25A)

#https://www.lcampanelli.org/mixed-effects-modeling-lme4/
gridExtra::grid.arrange(dotplot(ranef(b_SomeOpt25A, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)


```

### Ceiling Breach 
```{r Odds-Term}
comp_or<-odds_ratio(b_CBre28B,output="Breach Likelihood",rename_list=all_coef_list)
  comp_or_walds<-odds_ratio(b_CBre28B,"b_CBre28B",output="Breach Likelihood",walds=TRUE,rename_list=all_coef_list)
# save(comp.or,file="..//Output//comp.or.rdata")
write.csv(get_study_variables_odds_ratio(comp_or_walds,study="services"),file="..//output//ceiling_breach_study_odds_ratio_walds.csv",row.names=FALSE)
get_icc(b_CBre28B)

#https://www.lcampanelli.org/mixed-effects-modeling-lme4/
gridExtra::grid.arrange(dotplot(ranef(b_CBre28B, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)


```


### Terminations 

```{r Odds-Term}


  term_or_walds<-odds_ratio(term25A,"term25A",output="Termination Likelihood",walds=TRUE,rename_list=all_coef_list)
# save(term.or,file="..//Output//term.or.rdata")
write.csv(get_study_variables_odds_ratio(term_or_walds,study="services"),file="..//output//termination_study_odds_ratio_walds.csv",row.names=FALSE)
get_icc(term25A)


gridExtra::grid.arrange(dotplot(ranef(term25A, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)
dotplot(ranef(term25A, condVar = T), strip = T, scales=list(relation='free'))$NAICS3
 

```


## Residuals Plot


```{r Residuals, fig.width=7.5 , fig.height=8.5}

(
  terminations_residual<-gridExtra::grid.arrange(
    binned_fitted_versus_residuals(term25B,bins=50)+
      labs(title="Ceiling Breach Binned Actuals",caption=NULL,
           x="Estimated Pr(Terminations)",y="Actual Pr(Terminations)"),
    residuals_plot(term25B, bins=50)+labs(title="Terminations Binned Residual Plot")
    )
)


(
  ceiling_breach_residual<-gridExtra::grid.arrange(
    binned_fitted_versus_residuals(b_CBre28B,bins=50)+
      labs(title="Ceiling Breach Binned Actuals",caption=NULL,
           x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
    residuals_plot(b_CBre28B, bins=50)+labs(title="Ceiling Breach Binned Residual Plot"),
    binned_fitted_versus_residuals(n_CBre25A,bins=50)+
      labs(title="Termination Binned Actuals Plot",caption=NULL,
           x="Estimated Size of Breach when Breach Occurs",y="Actual Average Size of Breach when Breach Occurs"),
    residuals_plot(n_CBre25A, bins=50)+labs(title="Ceiling Binned Residual Plot")
  )
)



options_residual<-gridExtra::grid.arrange(
    residuals_plot(term25A, bins=50)+labs(title="Termination Residuals Plot"),
    binned_fitted_versus_residuals(p_Opt_12C,bins=50)+
      labs(title="Exercised Options Actuals",
           caption=NULL,
           x="Estimated % Exercised Option Growth",y="Actual % Exercised Option Growth"),
    residuals_plot(p_Opt_12C, bins=50)+labs(title="Exercised Options Binned Residuals Plot")
    ,ncol=2)


ggsave(residual_logit,file="..//output//residual_logit.png",width=7.5, height=8.5)
ggsave(residual_logit,file="..//output//residual_logit.png",width=7.5, height=8.5)

```
