---
title: "Serices Results Summary"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, July 11, 2019"
---

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(readr)
library(texreg)
library(reshape2)
library(tidyverse)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..


First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from   FPDS.


```{r ReadInData, echo = TRUE}
if(!exists("def_serv")) load("data/clean/transformed_def_serv.Rdata")
if(!exists("serv_smp")) load(file="data/clean/def_sample.Rdata")


```

# Pre-Model Graphs

### Platform Portfolio
```{r Platform, fig.width=6.5 , fig.height=3.25}

annual_platform_summary<-read_csv(file="output//annual_platform_summary.csv")
colnames(annual_platform_summary)[colnames(annual_platform_summary)=="platformPortfolio"]<-"PlatformPortfolio"

platform_no_na<-subset(annual_platform_summary,!is.na(PlatformPortfolio))
labels_and_colors<-csis360::prepare_labels_and_colors(platform_no_na,"PlatformPortfolio")



platform_no_na$plat_short <-swr(platform_no_na$PlatformPortfolio,nwrap = 21)
platform_no_na<-subset(platform_no_na,Fiscal.Year>=2000 & Fiscal.Year<=2017)

 

# plat<-ggplot(platform_no_na,
#        aes(x=Fiscal.Year,y=hh_index))+#color=NAICS_Code
#   geom_line()+
#   scale_y_continuous(label=scales::comma)+ 
#   # scale_x_continuous(breaks=c(2006,2009,2011,2014))+
#   labs(x="Fiscal Year",y="Herfindahl-Herschman Index")+ 
#   geom_hline(yintercept=c(1500,2500),linetype="dotted")+
#   facet_wrap(~plat_short)
# add_preassigned_scales(plat,labels_and_colors = labels_and_colors)

# str(platform_no_na)
# summary(platform_no_na$Fiscal.Year)
#
# undebug(add_preassigned_scales)
plat<-build_plot(
  data=platform_no_na,
  chart_geom = "Line Chart",
  share = FALSE,
  x_var="Fiscal.Year",
  y_var="hh_index", #Name of variable to plot on y-axis
  color_var="PlatformPortfolio",       # name of coloration variable, as string
  facet_var="PlatformPortfolio",        # name of facet variable, as string
  legend=FALSE, #Include a legend
  caption=FALSE, #Include a source caption
  labels_and_colors=labels_and_colors,
  column_key=NULL
)


# add_preassigned_scales(plat, labels_and_colors,  var="PlatformPortfolio"

plat<-plat+geom_hline(yintercept=c(1500,2500),linetype="dotted")+
  labs(x="Fiscal Year",y="Herfindahl-Herschman Indetx")
plat
ggsave(plat+geom_line(aes(x=Fiscal.Year,y=hh_index,color=PlatformPortfolio),size=1),filename="Output//platform_hhi.png",height=3.25, width=6.5)
ggsave(plat+geom_line(aes(x=Fiscal.Year,y=hh_index)),filename="Output//platform_hhi_bw.png",height=3.25, width=6.5)
ggsave(plat+geom_line(aes(x=Fiscal.Year,y=hh_index,color=PlatformPortfolio),size=1),filename="Output//platform_hhi.eps",height=3.25, width=6.5)
ggsave(plat+geom_line(aes(x=Fiscal.Year,y=hh_index)),filename="Output//platform_hhi_bw.eps",height=3.25, width=6.5)

```


# Models
## Loading Models
### Exercised Options

```{r Model-OptGrowth}
load("Output//Comp_Cons_15D.rdata")





if(!exists("Comp_Cons_15D"))
   
     Comp_Cons_15D <- lmer (data=serv_smp,
                         l_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                         # cl_US3_avg_sal_lag1+
                         cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                         cl_US6_avg_sal_lag1 + 
                         cl_Ceil+capped_cl_Days+
                         Veh+
                         PricingFee+UCA+
                         b_Intl+
                         b_UCA:cl_def6_HHI_lag1 +
                         # cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                         # cl_def6_HHI_lag1:cl_def6_obl_lag1+
                         b_Intl:Veh+
                         # cl_Ceil:PricingFee+
                         # cl_US6_avg_sal_lag1:PricingFee+
                         # b_UCA:capped_cl_Days+
                         # b_UCA:cl_Ceil+
                         (1 | NAICS3/NAICS) + (1 | Agency/Office) + (1 | StartCY),
                         verbose=1)
  
  
  # save(Comp_Cons_15D,file="Output//Comp_Cons_15D.rdata")
  
   Comp_Cons_15D_1m <- lmer (data=serv_smp1m,
                         l_Offr ~cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                         # cl_US3_avg_sal_lag1+
                         cl_def6_HHI_lag1+cl_def6_ratio_lag1+cl_def6_obl_lag1+
                         cl_US6_avg_sal_lag1 + 
                         cl_Ceil+capped_cl_Days+
                         Veh+
                         PricingFee+UCA+
                         b_Intl+
                         b_UCA:cl_def6_HHI_lag1 +
                         # cl_def6_HHI_lag1:cl_def6_ratio_lag1+
                         # cl_def6_HHI_lag1:cl_def6_obl_lag1+
                         b_Intl:Veh+
                         # cl_Ceil:PricingFee+
                         # cl_US6_avg_sal_lag1:PricingFee+
                         # b_UCA:capped_cl_Days+
                         # b_UCA:cl_Ceil+
                         (1 | NAICS3/NAICS) + (1 | Agency/Office) + (1 | StartCY),
                         verbose=1)
   save(Comp_Cons_15D,Comp_Cons_15D_1m,file="Output//Comp_Cons_15D.rdata")



stargazer::stargazer(Comp_Cons_15D,Comp_Cons_15D_1m,type="text",
                       digits=2)

#Considering 
write.csv(exp(summary(Comp_Cons_15D_1m)$coefficients[,1])-1,file="OUtput/exp_Comp_Cons_15D_1m.csv")
Comp_Cons_15D_exp<-log_analysis(Comp_Cons_15D)

glmer_examine(Comp_Cons_15D,display=TRUE)
get_icc(Comp_Cons_15D,summary=TRUE)
```


### Ceiling Breach

```{r Model-CBre}

# load("Output//b_CBre12C.rdata")

if(!exists("b_CBre12C")){
  b_CBre12C <- glm (data=serv_smp,
                 b_CBre ~  cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_hh_index_k , family=binomial(link="logit"),
                 verbose=1)
  
  # save(b_CBre12C,#CBre_Cons_13B,CBre_Cons_13B.restart,
  #      file="Output//b_CBre12C.rdata")
}
glmer_examine(CBre_Cons_13B,display=TRUE)
odds_ratio(CBre_Cons_13B,"CBre_Cons_13B")


# if(!exists("b_CBre12C_restart")){
#   pars<-get_pars(b_CBre12C)
#   b_CBre12C_restart <- update(b_CBre12C, 
#                                      start=pars,
#                                      verbose=1)
#   save(CBre_Cons_13B,
#        CBre_Cons_13B.restart,
#        b_CBre12C,
#        b_CBre12C_restart,
#        file="Output//CBre_Cons_13B.rdata")
# }
# glmer_examine(b_CBre12C_restart)



# 
# save(CBre_Cons_13B,
#      CBre_Cons_13B.devfun,
#      CBre_Cons_13_scgrad,
#      CBre_Cons_13B.restart,
#      CBre_Comp_13B,
#      CBre_Comp_13B.devfun,
#      CBre_Comp_13B.restart,
#      file="Output//CBre_Cons_13B.rdata")

# source(system.file("utils", "allFit.R", package="lme4"))
# CBre_Cons_13B.all <- allFit(CBre_Cons_13B)
# CBre_Cons_13B_ss_cons <- summary(CBre_Cons_13B.all)


# stargazer::stargazer(CBre_Cons_13B,b_CBre12C,type="text",
#                        digits=2)

# glmer_examine(CBre_Cons_13B.restart,display=TRUE)
# odds_ratio(CBre_Cons_13B.restart,"CBre_Cons_13B")

```
"Model failed to converge with max|grad| = 0.00750942 (tol = 0.001, component 1)"



### Termination

```{r Model-Term}
# load("Output//Term_12C.rdata")

if(!exists("Term_12C")){
Term_12C <- glm (data=serv_smp,
                 b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                   c_pairHist+cl_pairCA+
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_hh_index_k, family=binomial(link="logit"),
                 verbose=1)
glmer_examine(Term_12C)
    # save(Term_12C,Term_12C_1m,file="Output//Term_12C.rdata")
}

glmer_examine(Term_12C,display=TRUE)
odds_ratio(Term_12C,"Term_12C")

```

## Tables for Paper
### Exercised Options 
```{r Table-OptGrowth}

# texreg::htmlreg(list(Term_Cons_08A3,
#                   CBre_Cons_08C),#CBre_Cons_08B2
#                 file="Output//ConsModel.html",single.row = TRUE,
#                 custom.model.name=c("Termination",
#                                     "Ceiling Breach"),
#                         stars=c(0.05))




texreg::htmlreg(list(Comp_Cons_15D),file="Output//Offr_Model.html",
                single.row = TRUE,
                custom.model.name=c("Concentration"),
                        stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:3,
                              "NAICS Characteristics" =4:7,
                              "Contract Characteristics"=8:19,
"Interactions" = 20:24),
                custom.coef.map=list("(Intercept)"="(Intercept)",
                "cl_def3_HHI_lag1"="Log(Subsector HHI)",
"cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
"CompOffr1 offer"="Comp=1 offer",
"CompOffr2 offers"="Comp=2 offers",
"CompOffr3-4 offers"="Comp=3-4 offers",
"CompOffr5+ offers"="Comp=5+ offers",
"cl_def3_ratio_lag1"="Log(Subsector Ratio)",
"cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
"cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
"cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
"cl_Ceil"="Log(Init. Ceiling)",
"capped_cl_Days"="Log(Init. Days)",
"VehS-IDC"="Vehicle=S-IDC",
"VehM-IDC"="Vehicle=M-IDC",
"VehFSS/GWAC"="Vehicle=FSS/GWAC",
"VehBPA/BOA"="Vehicle=BPA/BOA",
"PricingFeeOther FP"="Pricing=Other FP",
"PricingFeeIncentive"="Pricing=Incentive Fee",
"PricingFeeCombination or Other"="Pricing=Combination or Other",
"PricingFeeOther CB"="Pricing=Other CB",
"PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
"b_UCA"="UCA",
"b_Intl"="Performed Abroad",
# # "cl_def6_HHI_lag1:capped_cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
# "cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
# # "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)"),
"cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
# "cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
# "CompOffr1 offer:b_UCA"="Comp=1 offer:UCA",
# "CompOffr2 offers:b_UCA"="Comp=2 offers:UCA",
# "CompOffr3-4 offers:b_UCA"="Comp=3-4 offers:UCA",
# "CompOffr5+ offers:b_UCA"="Comp=5+ offers:UCA"
"VehS-IDC:b_Intl"="Vehicle=S-IDC:Performed Abroad",
"VehM-IDC:b_Intl"="Vehicle=M-IDC:Performed Abroad",
"VehFSS/GWAC:b_Intl"="Vehicle=FSS/GWAC:Performed Abroad",
"VehBPA/BOA:b_Intl"="Vehicle=BPA/BOA:Performed Abroad",
"cl_US6_avg_sal_lag1:PricingFeeOther FP"="Pricing=Other FP:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeIncentive"="Pricing=Incentive Fee:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeCombination or Other"="Pricing=Comb./or Other:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeOther CB"="Pricing=Other CB:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE:Log(Det. Ind. U.S. Avg. Salary)"

),
                bold=0.05,
custom.note="%stars. Logged inputs are rescaled. For this model, sole source contracts and task orders are treated as having 1 offer.",
caption="Table 1: Regression Model of Log(Number of Offfers)",
caption.above=TRUE)


texreg::htmlreg(list(Comp_Cons_15D_1m),file="Output//Offr_Model_1m.html",
                single.row = TRUE,
                custom.model.name=c("Concentration"),
                        stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:3,
                              "NAICS Characteristics" =4:7,
                              "Contract Characteristics"=8:20,
"Interactions" = 21:25),
                custom.coef.map=list("(Intercept)"="(Intercept)",
                "cl_def3_HHI_lag1"="Log(Subsector HHI)",
"cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
"CompOffr1 offer"="Comp=1 offer",
"CompOffr2 offers"="Comp=2 offers",
"CompOffr3-4 offers"="Comp=3-4 offers",
"CompOffr5+ offers"="Comp=5+ offers",
"cl_def3_ratio_lag1"="Log(Subsector Ratio)",
"cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
"cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
"cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
"cl_Ceil"="Log(Init. Ceiling)",
"capped_cl_Days"="Log(Init. Days)",
"VehS-IDC"="Vehicle=S-IDC",
"VehM-IDC"="Vehicle=M-IDC",
"VehFSS/GWAC"="Vehicle=FSS/GWAC",
"VehBPA/BOA"="Vehicle=BPA/BOA",
"PricingFeeOther FP"="Pricing=Other FP",
"PricingFeeIncentive"="Pricing=Incentive Fee",
"PricingFeeCombination or Other"="Pricing=Combination or Other",
"PricingFeeOther CB"="Pricing=Other CB",
"PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
"b_UCA"="UCA",
"UCAUCA"="UCA",
"b_Intl"="Performed Abroad",
# # "cl_def6_HHI_lag1:capped_cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
# "cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
# # "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)"),
"cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
# "cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
# "CompOffr1 offer:b_UCA"="Comp=1 offer:UCA",
# "CompOffr2 offers:b_UCA"="Comp=2 offers:UCA",
# "CompOffr3-4 offers:b_UCA"="Comp=3-4 offers:UCA",
# "CompOffr5+ offers:b_UCA"="Comp=5+ offers:UCA"
"VehS-IDC:b_Intl"="Vehicle=S-IDC:Performed Abroad",
"VehM-IDC:b_Intl"="Vehicle=M-IDC:Performed Abroad",
"VehFSS/GWAC:b_Intl"="Vehicle=FSS/GWAC:Performed Abroad",
"VehBPA/BOA:b_Intl"="Vehicle=BPA/BOA:Performed Abroad",
"cl_US6_avg_sal_lag1:PricingFeeOther FP"="Pricing=Other FP:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeIncentive"="Pricing=Incentive Fee:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeCombination or Other"="Pricing=Comb./or Other:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeOther CB"="Pricing=Other CB:Log(Det. Ind. U.S. Avg. Salary)",
"cl_US6_avg_sal_lag1:PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE:Log(Det. Ind. U.S. Avg. Salary)"

),
                bold=0.05,
custom.note="%stars. Logged inputs are rescaled. For this model, sole source contracts and task orders are treated as having 1 offer.",
caption="Table 1: Regression Model of Log(Number of Offfers)",
caption.above=TRUE)

get_icc(Comp_Cons_15D_1m)


  # OR_m1SD <- exp(fixef(FM_m1SD))
  # CI_m1SD <- exp(confint(FM_m1SD,parm="beta_")) 
  # 
  # OR_p1SD <- exp(fixef(FM_p1SD))
  # CI_p1SD <- exp(confint(FM_p1SD,parm="beta_")) 
  # 
  # OR.CI<-rbind(cbind(OR,CI), cbind(OR_m1SD,CI_m1SD)[3,], cbind(OR_p1SD,CI_p1SD)[3,])
  # rownames(OR.CI)<-c(rownames(cbind(OR,CI)), "teacher_fan_c_m1SD", "teacher_fan_c_p1SD")
  # OR.CI


gridExtra::grid.arrange(dotplot(ranef(Comp_Cons_15D, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)

```

### Ceiling Breach 
```{r Output-CBre}
stargazer::stargazer(b_CBre12C,CBre_Comp_13C_1m,CBre_Cons_Comp_15A_1m,type="text",
                       digits=2)
# texreg::htmlreg(list(Term_Cons_08A3,
#                   CBre_Cons_08C),#CBre_Cons_08B2
#                 file="Output//ConsModel.html",single.row = TRUE,
#                 custom.model.name=c("Termination",
#                                     "Ceiling Breach"),
#                         stars=c(0.05))


# texreg::htmlreg(list(CBre_Cons_13B,CBre_Comp_13C,CBre_Cons_Comp_15A),file="Output//CBre_Model.html",single.row = TRUE,
#                 custom.model.name=c("Consolidation",
#                                     "Competition",
#                                     "Both"),
#                         stars=c(0.05,0.01,0.001))


texreg::htmlreg(list(CBre_Cons_13B.restart,CBre_Comp_13C,CBre_Cons_Comp_15A),file="Output//CBre_Model.html",
                single.row = TRUE,
                custom.model.name=c("Concentration",
                                    "Competition",
                                    "Both"),
                        stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:7,
                              "NAICS Characteristics" = 8:11,
                              "Contract Characteristics"=12:24,
"Interactions" = 25:31),
                custom.coef.map=list("(Intercept)"="(Intercept)",
                "cl_def3_HHI_lag1"="Log(Subsector HHI)",
"cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
"CompOffr1 offer"="Comp=1 offer",
"CompOffr2 offers"="Comp=2 offers",
"CompOffr3-4 offers"="Comp=3-4 offers",
"CompOffr5+ offers"="Comp=5+ offers",
"cl_def3_ratio_lag1"="Log(Subsector Ratio)",
"cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
"cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
"cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
"cl_Ceil"="Log(Init. Ceiling)",
"capped_cl_Days"="Log(Init. Days)",
"VehS-IDC"="Vehicle=S-IDC",
"VehM-IDC"="Vehicle=M-IDC",
"VehFSS/GWAC"="Vehicle=FSS/GWAC",
"VehBPA/BOA"="Vehicle=BPA/BOA",
"PricingFeeOther FP"="Pricing=Other FP",
"PricingFeeIncentive"="Pricing=Incentive Fee",
"PricingFeeCombination or Other"="Pricing=Combination or Other",
"PricingFeeOther CB"="Pricing=Other CB",
"PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
"b_UCA"="UCA",
"b_Intl"="Performed Abroad",
# "cl_def6_HHI_lag1:capped_cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
"cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
# "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)"),
"cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
"cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
"CompOffr1 offer:b_UCA"="Comp=1 offer:UCA",
"CompOffr2 offers:b_UCA"="Comp=2 offers:UCA",
"CompOffr3-4 offers:b_UCA"="Comp=3-4 offers:UCA",
"CompOffr5+ offers:b_UCA"="Comp=5+ offers:UCA"
),
                bold=0.05,
custom.note="%stars. Logged inputs are rescaled.",
caption="Table 2: Logit Model Results for Ceiling Breaches",
caption.above=TRUE)



texreg::htmlreg(list(b_CBre12C,CBre_Comp_13C_1m,CBre_Cons_Comp_15A_1m),file="Output//CBre_Model_1m.html",
                single.row = TRUE,
                custom.model.name=c("Concentration",
                                    "Competition",
                                    "Both"),
                        stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:7,
                              "NAICS Characteristics" = 8:11,
                              "Contract Characteristics"=12:24,
"Interactions" = 25:31),
                custom.coef.map=list("(Intercept)"="(Intercept)",
                "cl_def3_HHI_lag1"="Log(Subsector HHI)",
"cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
"CompOffr1 offer"="Comp=1 offer",
"CompOffr2 offers"="Comp=2 offers",
"CompOffr3-4 offers"="Comp=3-4 offers",
"CompOffr5+ offers"="Comp=5+ offers",
"cl_def3_ratio_lag1"="Log(Subsector Ratio)",
"cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
"cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
"cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
"cl_Ceil"="Log(Init. Ceiling)",
"capped_cl_Days"="Log(Init. Days)",
"VehS-IDC"="Vehicle=S-IDC",
"VehM-IDC"="Vehicle=M-IDC",
"VehFSS/GWAC"="Vehicle=FSS/GWAC",
"VehBPA/BOA"="Vehicle=BPA/BOA",
"PricingFeeOther FP"="Pricing=Other FP",
"PricingFeeIncentive"="Pricing=Incentive Fee",
"PricingFeeCombination or Other"="Pricing=Combination or Other",
"PricingFeeOther CB"="Pricing=Other CB",
"PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
"b_UCA"="UCA",
"b_Intl"="Performed Abroad",
# "cl_def6_HHI_lag1:capped_cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
"cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
# "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)"),
"cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
"cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
"CompOffr1 offer:b_UCA"="Comp=1 offer:UCA",
"CompOffr2 offers:b_UCA"="Comp=2 offers:UCA",
"CompOffr3-4 offers:b_UCA"="Comp=3-4 offers:UCA",
"CompOffr5+ offers:b_UCA"="Comp=5+ offers:UCA"
),
                bold=0.05,
custom.note="%stars. Logged inputs are rescaled.",
caption="Table 2: Logit Model Results for Ceiling Breaches",
caption.above=TRUE)




or1<-odds_ratio(CBre_Cons_13B.restart,"CBre_Cons_13B","Concentration","Ceiling Breaches")
or2<-odds_ratio(CBre_Comp_13C,"CBre_Comp_13C","Competition","Ceiling Breaches")
or3<-odds_ratio(CBre_Cons_Comp_15A,"CBre_Cons_Comp_15A","Both","Ceiling Breaches")
comp.or<-rbind(or1,or2,or3)

write.csv(get_study_variables_odds_ratio(comp.or),file="Output//ceiling_breach_study_odds_ratio.csv",row.names=FALSE)



or1<-odds_ratio(b_CBre12C,"b_CBre12C","Concentration","Ceiling Breaches")
or2<-odds_ratio(CBre_Comp_13C_1m,"CBre_Comp_13C_1m","Competition","Ceiling Breaches")
or3<-odds_ratio(CBre_Cons_Comp_15A_1m,"CBre_Cons_Comp_15A_1m","Both","Ceiling Breaches")
comp.or<-rbind(or1,or2,or3)

write.csv(get_study_variables_odds_ratio(comp.or),file="Output//ceiling_breach_study_odds_ratio_1m.csv",row.names=FALSE)
get_icc(CBre_Cons_Comp_15A_1m)

#https://www.lcampanelli.org/mixed-effects-modeling-lme4/
gridExtra::grid.arrange(dotplot(ranef(CBre_Cons_13B.restart, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             dotplot(ranef(CBre_Comp_13C, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             dotplot(ranef(CBre_Cons_Comp_15A, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)


```


### Terminations 
#### Regression Tables
```{r Output-CBre}

# texreg::htmlreg(list(Term_Cons_08A3,
#                   CBre_Cons_08C),#CBre_Cons_08B2
#                 file="Output//ConsModel.html",single.row = TRUE,
#                 custom.model.name=c("Termination",
#                                     "Ceiling Breach"),
#                         stars=c(0.05))



texreg::htmlreg(list(Term_12C,Term_Comp_13F,Term_Cons_Comp_14C),file="Output//Term_Model.html",
                single.row = TRUE,
                custom.model.name=c("Concentration",
                                    "Competition",
                                    "Both"
                ),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:7,
                              "NAICS Characteristics" = 8:11,
                              "Contract Characteristics"=12:24,
                              # "Contract Initial Scope" = 12:13,
                              # "Contract Vehicle (Baseline=def_serv. Award" = 14:18,
                              # "Contract Pricing (Baseline=FFP)" = 19:24,
                              # "Place of Performance" = 25,
                              "Interactions" = 25:27),
                custom.coef.map=list(
                  "(Intercept)"="(Intercept)",
                  
                  "cl_def3_HHI_lag1"="Log(Subsector HHI)",
                  "cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
                  
                  "CompOffr1 offer"="Comp=1 offer",
                  "CompOffr2 offers"="Comp=2 offers",
                  "CompOffr3-4 offers"="Comp=3-4 offers",
                  "CompOffr5+ offers"="Comp=5+ offers",
                  "cl_def3_ratio_lag1"="Log(Subsector Ratio)",
                  "cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
                  "cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
                  "cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_Ceil"="Log(Init. Ceiling)",
                  "cl_Days"="Log(Init. Days)",
                  "VehS-IDC"="Vehicle=S-IDC",
                  "VehM-IDC"="Vehicle=M-IDC",
                  "VehFSS/GWAC"="Vehicle=FSS/GWAC",
                  "VehBPA/BOA"="Vehicle=BPA/BOA",
                  "PricingFeeOther FP"="Pricing=Other FP",
                  "PricingFeeIncentive"="Pricing=Incentive Fee",
                  "PricingFeeCombination or Other"="Pricing=Combination or Other",
                  "PricingFeeOther CB"="Pricing=Other CB",
                  "PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
                  "b_UCA"="UCA",
                  "b_Intl"="Performed Abroad",
                  "cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
                  "cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
                  "cl_def6_HHI_lag1:cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
                  "cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
                  "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)",
                  "cl_def6_HHI_lag1:cl_def6_ratio_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. Ratio)",
                  "cl_US6_avg_sal_lag1:PricingFeeOther FP"="Pricing=Other FP:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeIncentive"="Pricing=Incentive Fee:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeCombination or Other"=
                    "Pricing=Comb./or Other:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeOther CB"="Pricing=Other CB:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeT&M/LH/FPLOE"=
                    "Pricing=T&M/LH/FP:LoE:Log(Det. Ind. U.S. Avg. Salary)"
                  
                ),
                bold=0.05,
                custom.note="%stars. Logged inputs are rescaled.",
                caption="Table 3: Logit Model Results for Terminations",
                caption.above=TRUE)

                       #  b_UCA:cl_Ceil+
                       #  b_UCA:cl_def6_HHI_lag1 +
                       # PricingFee:cl_US6_avg_sal_lag1+


# texreg::htmlreg(list(Term_12C,Term_Comp_13E2,Term_Cons_Comp_14C,Term_Cons_Comp_14C_1m),file="Output//Term_Model_1m.html",
#                 single.row = TRUE,
#                 custom.model.name=c("Concentration",
#                                     "Competition",
#                                     "Both",
#                                     "Both 1m"
texreg::htmlreg(list(Term_12C_1m,Term_Comp_13F_1m,Term_Cons_Comp_14C_1m),file="Output//Term_Model_1m.html",
                single.row = TRUE,
                custom.model.name=c("Concentration",
                                    "Competition",
                                    "Both"
                ),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list("Study Variables" = 2:7,
                              "NAICS Characteristics" = 8:11,
                              "Contract Characteristics"=12:24,
                              # "Contract Initial Scope" = 12:13,
                              # "Contract Vehicle (Baseline=def_serv. Award" = 14:18,
                              # "Contract Pricing (Baseline=FFP)" = 19:24,
                              # "Place of Performance" = 25,
                              "Interactions" = 25:27),
                custom.coef.map=list(
                  "(Intercept)"="(Intercept)",
                  
                  "cl_def3_HHI_lag1"="Log(Subsector HHI)",
                  "cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
                  
                  "CompOffr1 offer"="Comp=1 offer",
                  "CompOffr2 offers"="Comp=2 offers",
                  "CompOffr3-4 offers"="Comp=3-4 offers",
                  "CompOffr5+ offers"="Comp=5+ offers",
                  "cl_def3_ratio_lag1"="Log(Subsector Ratio)",
                  "cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
                  "cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
                  "cl_US6_avg_sal_lag1"="Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_Ceil"="Log(Init. Ceiling)",
                  "cl_Days"="Log(Init. Days)",
                  "VehS-IDC"="Vehicle=S-IDC",
                  "VehM-IDC"="Vehicle=M-IDC",
                  "VehFSS/GWAC"="Vehicle=FSS/GWAC",
                  "VehBPA/BOA"="Vehicle=BPA/BOA",
                  "PricingFeeOther FP"="Pricing=Other FP",
                  "PricingFeeIncentive"="Pricing=Incentive Fee",
                  "PricingFeeCombination or Other"="Pricing=Combination or Other",
                  "PricingFeeOther CB"="Pricing=Other CB",
                  "PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
                  "b_UCA"="UCA",
                  "b_Intl"="Performed Abroad",
                  "cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
                  "cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
                  "cl_def6_HHI_lag1:cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
                  "cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
                  "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)",
                  "cl_def6_HHI_lag1:cl_def6_ratio_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. Ratio)",
                  "cl_US6_avg_sal_lag1:PricingFeeOther FP"="Pricing=Other FP:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeIncentive"="Pricing=Incentive Fee:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeCombination or Other"=
                    "Pricing=Comb./or Other:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeOther CB"="Pricing=Other CB:Log(Det. Ind. U.S. Avg. Salary)",
                  "cl_US6_avg_sal_lag1:PricingFeeT&M/LH/FPLOE"=
                    "Pricing=T&M/LH/FP:LoE:Log(Det. Ind. U.S. Avg. Salary)"
                  
                ),
                bold=0.05,
                custom.note="%stars. Logged inputs are rescaled.",
                caption="Table 3: Logit Model Results for Terminations",
                caption.above=TRUE)

                       #  b_UCA:cl_Ceil+
                       #  b_UCA:cl_def6_HHI_lag1 +
                       # PricingFee:cl_US6_avg_sal_lag1+


gridExtra::grid.arrange(dotplot(ranef(Term_12C, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             dotplot(ranef(Term_Comp_13E2, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             dotplot(ranef(Term_Cons_Comp_14A, condVar = T), strip = T, scales=list(relation='free'))$Agency,
             nrow=1)
dotplot(ranef(Term_12C, condVar = T), strip = T, scales=list(relation='free'))$NAICS3


or1<-odds_ratio(Term_12C,"Term_12C","Concentration","Ceiling Breaches")
or2<-odds_ratio(Term_Comp_13E2,"Term_Comp_13E2","Competition","Ceiling Breaches")
or3<-odds_ratio(Term_Cons_Comp_14C,"Term_Cons_Comp_14C","Both","Ceiling Breaches")
term.or<-rbind(or1,or2,or3)

write.csv(get_study_variables_odds_ratio(term.or),file="Output//termination_study_odds_ratio.csv",row.names=FALSE)

or1<-odds_ratio(Term_12C_1m,"Term_12C_1m","Concentration","Ceiling Breaches")
  or2<-odds_ratio(Term_Comp_13E2,"Term_Comp_13F_1m","Competition","Ceiling Breaches")
or3<-odds_ratio(Term_Cons_Comp_14C_1m,"Term_Cons_Comp_14C_1m","Both","Ceiling Breaches")
term.or<-rbind(or1,or2,or3)

write.csv(get_study_variables_odds_ratio(term.or),file="Output//termination_study_odds_ratio_1m.csv",row.names=FALSE)


```


#### Odds Ratios 

```{r Consolidation}
or_ceil<-odds_ratio(CBre_Cons_Comp_15A,"CBre_Cons_Comp_15A","Both","Ceiling Breaches")
or_term<-odds_ratio(Term_Cons_Comp_14B,"Term_Cons_Comp_14B","Both","Terminations")

cons.or<-rbind(or_ceil,or_term)

write.csv(get_study_variables_odds_ratio(subset(cons.or,variable %in% c("cl_def3_HHI_lag1","cl_def6_HHI_lag1"))),
          file="Output//consolidation_odds_ratio.csv",row.names=FALSE)


or_ceil<-odds_ratio(CBre_Cons_Comp_15A_1m,"CBre_Cons_Comp_15A_1m","Both","Ceiling Breaches")
or_term<-odds_ratio(Term_Cons_Comp_14C_1m,"Term_Cons_Comp_14C_1m","Both","Terminations")

cons.or<-rbind(or_ceil,or_term)

write.csv(get_study_variables_odds_ratio(subset(cons.or,variable %in% c("cl_def3_HHI_lag1","cl_def6_HHI_lag1"))),
          file="Output//consolidation_odds_ratio_1m.csv",row.names=FALSE)


# centered_description(serv_smp1m$def6_HHI_lag1,"subsector HHI score")
# centered_log_description(serv_smp1m$l_def6_HHI_lag1,"detailed industrial HHI score")
# 
# 
# centered_description(serv_smp1m$def3_HHI_lag1,"subsector HHI score")
# centered_log_description(serv_smp1m$l_def3_HHI_lag1,"detailed industrial HHI score")





```


## Residuals Plot


```{r Residuals, fig.width=7.5 , fig.height=8.5}

residual_cbre<-gridExtra::grid.arrange(
  binned_fitted_versus_residuals(CBre_Cons_13B.restart,bins=50)+
    labs(title="Concentration Binned Actuals",caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
  residuals_plot(CBre_Cons_13B.restart, bins=50)+labs(title="Concentration Binned Residual Plot"),
  binned_fitted_versus_residuals(CBre_Comp_13C,bins=50)+
    labs(title="Competition Binned Actuals Plot",caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
residuals_plot(CBre_Comp_13C, bins=50)+labs(title="Competition Binned Residuals Plot"),
binned_fitted_versus_residuals(CBre_Cons_Comp_15A,bins=50)+
  labs(title="Both Binned Actuals",
       caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
residuals_plot(CBre_Cons_Comp_15A, bins=50)+labs(title="Both Binned Residuals Plot"),ncol=2)

residual_cbre
ggsave(residual_cbre,file="Output//residual_cbre.png",width=7.5, height=8.5)
ggsave(residual_cbre,file="Output//residual_cbre.eps",width=7.5, height=8.5)

residual_term<-gridExtra::grid.arrange(
  binned_fitted_versus_residuals(Term_12C,bins=50)+
    labs(title="Concentration Binned Actuals",caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
  residuals_plot(Term_12C, bins=50)+labs(title="Binned Residual Plot"),
  binned_fitted_versus_residuals(Term_Cons_Comp_14B,bins=50)+
    labs(title="Competition Binned Actuals Plot",caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
residuals_plot(Term_Cons_Comp_14B, bins=50)+labs(title="Binned Residuals Plot"),
binned_fitted_versus_residuals(Term_Cons_Comp_14B,bins=50)+
  labs(title="Both Binned Actuals",
       caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
residuals_plot(Term_Cons_Comp_14B, bins=50)+labs(title="Binned Residuals Plot"),ncol=2)


residual_term
ggsave(residual_term,file="Output//residual_term.png",width=7.5, height=8.5)
ggsave(residual_term,file="Output//residual_term.eps",width=7.5, height=8.5)



# debug(residuals_plot)
gridExtra::grid.arrange(residuals_plot(Term_12C, bins=50)+labs(title="Concentration Binned Residuals Plot"),
residuals_plot(Term_Comp_13E2, bins=50)+labs(title="Competition Binned Residuals Plot"),
residuals_plot(Term_Cons_Comp_14B, bins=50)+labs(title="Both Binned Residuals Plot"),ncol=1)
```


```{r Residuals_250k, fig.width=7.5 , fig.height=8.5}

residual_cbre<-gridExtra::grid.arrange(
  binned_fitted_versus_residuals(b_CBre12C,bins=50)+
    labs(title="Concentration Binned Actuals",caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
  residuals_plot(b_CBre12C, bins=50)+labs(title="Concentration Binned Residual Plot"),
  binned_fitted_versus_residuals(CBre_Comp_13C_1m,bins=50)+
    labs(title="Competition Binned Actuals Plot",caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
residuals_plot(CBre_Comp_13C_1m, bins=50)+labs(title="Competition Binned Residuals Plot"),
binned_fitted_versus_residuals(CBre_Cons_Comp_15A_1m,bins=50)+
  labs(title="Both Binned Actuals",
       caption=NULL,
         x="Estimated Pr(Ceiling Breach)",y="Actual Pr(Ceiling Breach)"),
residuals_plot(CBre_Cons_Comp_15A_1m, bins=50)+labs(title="Both Binned Residuals Plot"),ncol=2)

residual_cbre
ggsave(residual_cbre,file="Output//residual_cbre_1m.png",width=7.5, height=8.5)
ggsave(residual_cbre,file="Output//residual_cbre_1m.eps",width=7.5, height=8.5)

residual_term<-gridExtra::grid.arrange(
  binned_fitted_versus_residuals(Term_12C_1m,bins=50)+
    labs(title="Concentration Binned Actuals",caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
  residuals_plot(Term_12C_1m, bins=50)+labs(title="Binned Residual Plot"),
  binned_fitted_versus_residuals(Term_Comp_13F_1m,bins=50)+
    labs(title="Competition Binned Actuals Plot",caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
residuals_plot(Term_Comp_13F_1m, bins=50)+labs(title="Binned Residuals Plot"),
binned_fitted_versus_residuals(Term_Cons_Comp_14C_1m,bins=50)+
  labs(title="Both Binned Actuals",
       caption=NULL,
         x="Estimated Pr(Termination)",y="Actual Pr(Termination)"),
residuals_plot(Term_Cons_Comp_14C_1m, bins=50)+labs(title="Binned Residuals Plot"),ncol=2)


residual_term
ggsave(residual_term,file="Output//residual_term_1m.png",width=7.5, height=8.5)
ggsave(residual_term,file="Output//residual_term_1m.eps",width=7.5, height=8.5)


# debug(residuals_plot)
gridExtra::grid.arrange(residuals_plot(Term_12C, bins=50)+labs(title="Concentration Binned Residuals Plot"),
residuals_plot(Term_Comp_13E2, bins=50)+labs(title="Competition Binned Residuals Plot"),
residuals_plot(Term_Cons_Comp_14B, bins=50)+labs(title="Both Binned Residuals Plot"),ncol=1)
```