---
title: "Serices Results Summary"
output:
  html_document:
    keep_md: yes
    toc: yes
date: "Wednesday, July 11, 2019"
---

#Setup


First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(dplyr)
library(arm)
library(R2WinBUGS)
library(knitr)
library(foreign)
library(stargazer)
library(readr)
library(texreg)
library(reshape2)
library(tidyverse)
# source("C:/Users/JGraham/Documents/CSIS/Vendor/Scripts/DIIGstat.r")
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")

axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40

study_coef_list<-get_coef_list(limit="services")

all_coef_list<-get_coef_list()


if(!exists("def_serv")) load("../data/clean/transformed_def_serv.Rdata")
if(!exists("serv_smp")) load(file="../data/clean/def_sample.Rdata")

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.

# Pre-Model Graphs
None at present.
# Models
## Loading Models
### Exercised Options
Note that because we use the complete dataset for exercised options, there's no 1 million entry variant.
```{r Model-OptGrowth}

if(file.exists("..//Output//p_Opt_12C.rdata")) load("..//Output//p_Opt_12C.rdata")

if(!exists("p_Opt_12C")){
  p_Opt_12C <- glm (data=serv_opt,
                    lp_OptGrowth ~  cl_US6_avg_sal_lag1Const +
                      cl_CFTE+ c_pPBSC+c_pOffPSC+
                      c_pairHist+cl_pairCA +
                      cl_Ceil + capped_cl_Days+
                      Comp1or5+
                      Veh+
                      PricingUCA+
                      Crisis+
                      cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                      cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                      c_pMarket+
                      cl_OffVol+cl_office_naics_hhi_k #,
                    # verbose=1
                    )
  glmer_examine(p_Opt_12C)
  save(p_Opt_12C,file="..//Output//p_Opt_12C.rdata")
}

#Considering 
# write.csv(exp(summary(p_Opt_12C)$coefficients[,1])-1,file="../Output/exp_p_Opt_12C.csv")
# p_Opt_12C_exp<-log_analysis(p_Opt_12C)

glmer_examine(p_Opt_12C)

# Deprecated
if(file.exists("..//Output//b_SomeOpt25Cv3.rda")) load("..//Output//b_SomeOpt25Cv3.rda")
# 
if(!exists("b_SomeOpt25Cv3")){
  #Create the model

  b_SomeOpt25Cv3 <- glmer(data=serv_opt, b_SomeOpt ~  cln_US6sal +
                            cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                            cn_PairHist7+cln_PairCA+
                            cln_Base + clr_Ceil2Base + cln_Days+
                            Comp+
                            Veh+
                            Pricing+
                            Crisis+
                            cln_Def6HHI+clr_Def6toUS+
                            cln_Def3HHI+
                            clr_Def3toUS+
                            cp_PairObl7+
                            cln_OffObl7+
                            cln_OffFocus+
                            cp_OffPerf7:cp_PairObl7 +
                            cp_OffPerf7:cln_PairCA +
                            cn_PairHist7:Pricing +
                            cp_PairObl7:cln_OffObl7 +
                            clr_Ceil2Base:cln_Base +
                            pOffPSC:cln_OffObl7 +
                            (1 | NAICS3/NAICS6/ServArea)+
                            (1 | Agency/Office) +
                            (1 | Place)+
                            (1 | StartFY),
                          family=binomial(link="logit"),
                          verbose=TRUE)
  save(b_SomeOpt25Cv3, file="..\\Output\\b_SomeOpt25Cv3.rda")
}

glmer_examine(b_SomeOpt25Cv3)



if(file.exists("..//Output//b_AllOpt26A.rda")) load("..//Output//b_AllOpt26A.rda")

if(!exists("b_AllOpt26A")){
  #Create the model
  

  b_AllOpt26A <- glmer(data=serv_exeropt,
                       b_AllOpt ~  cln_US6sal + 
                   cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                 cn_PairHist7+cln_PairCA+
                 cln_Base + clr_Ceil2Base + cln_Days+
                 Comp+
                   Veh+
                   Pricing+
                   Crisis+
                 cln_Def6HHI+clr_Def6toUS+
                 cln_Def3HHI+
                   clr_Def3toUS+
                 cp_PairObl7+
                   cln_OffObl7+ 
                 cln_OffFocus+
                   cp_OffPerf7:cp_PairObl7 + 
                  # cp_OffPerf7:cln_PairCA + 
                   cp_OffPSC7:cln_OffFocus+
                   
                   Pricing:cln_PSCrate+
                      # cp_OffPerf7:cln_Days+
                 # Pricing:cln_PSCrate+
                   cln_OffObl7:cln_OffFocus+
                      (1 | NAICS3/NAICS6/ServArea)+  
                      (1 | Agency/Office) +
                      (1 | Place)+ 
                      (1 | StartFY),
                      family=binomial(link="logit"),
                      verbose=TRUE)
  
  save(b_AllOpt26A,file="..\\output\\b_AllOpt26A.rda")

}

glmer_examine(b_AllOpt26A)

# glmer_examine(p_Opt_12C,display=TRUE)
# stargazer::stargazer(p_Opt_12C,type="text",
#                        digits=2)

glmer_examine(b_SomeOpt25Cv3)
```


### Ceiling Breach

```{r Model-CBre}
if(file.exists("..//Output//b_CBre29AB.rda")) load("..//Output//b_CBre29AB.rda")

if(!exists("b_CBre29B")){
    b_CBre29A <- glmer(data=serv_smp, b_CBre ~  cln_US6sal +
                       cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                       cn_PairHist7+cln_PairCA+
                       cln_Base + clr_Ceil2Base + cln_Days+
                       Comp+
                       Veh+
                       Pricing+
                       Crisis+
                       cln_Def6HHI+clr_Def6toUS+
                       cln_Def3HHI+
                       clr_Def3toUS+
                       cp_PairObl7+
                       cln_OffObl7+
                       cln_OffFocus+
                       cp_OffPerf7:cln_PairCA+
                       #cp_OffPerf7:cp_PairObl7+
                       cp_OffPerf7:cln_Days+
                       # clr_Ceil2Base:cln_Base+
                       (1 | NAICS3/NAICS6/ServArea)+
                       (1 | Agency/Office) +
                       (1 | Place)+
                       (1 | StartFY),
                     family=binomial(link="logit"),
                     verbose=TRUE)
  save(b_CBre29A,file="..\\output\\b_CBre29A.rda")
  
  b_CBre29B <- glmer(data=serv_smp1m, b_CBre ~  cln_US6sal +
                       cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                       cn_PairHist7+cln_PairCA+
                       cln_Base + clr_Ceil2Base + cln_Days+
                       Comp+
                       Veh+
                       Pricing+
                       Crisis+
                       cln_Def6HHI+clr_Def6toUS+
                       #cln_Def3HHI+
                       clr_Def3toUS+
                       cp_PairObl7+
                       cln_OffObl7+
                       cln_OffFocus+
                       cp_OffPerf7:cln_PairCA+
                       #cp_OffPerf7:cp_PairObl7+
                       cp_OffPerf7:cln_Days+
                       # clr_Ceil2Base:cln_Base+
                       (1 | NAICS3/NAICS6/ServArea)+
                       (1 | Agency/Office) +
                       (1 | Place)+
                       (1 | StartFY),
                     family=binomial(link="logit"),
                     verbose=TRUE)
  save(b_CBre29A,b_CBre29B,file="..\\output\\b_CBre29AB.rda")

}
glmer_examine(b_CBre29B)

if(file.exists("..//Output//CBre25A.rda")) load("..//Output//CBre25A.rda")

if(!exists("n_CBre25A")){
    
  n_CBre25A <- lmer(data=serv_breach, ln_CBre ~ cln_US6sal + 
                      cln_PSCrate+ cp_OffPerf7+cp_OffPSC7+
                      cn_PairHist7+cln_PairCA+
                      cln_Base + clr_Ceil2Base + cln_Days+
                      Comp+
                      Veh+
                      Pricing+
                      Crisis+
                      cln_Def6HHI+clr_Def6toUS+
                      #cln_Def3HHI+
                      clr_Def3toUS+
                      cp_PairObl7+
                      cln_OffObl7+ 
                      #cl_office_NAICS6_hhi_kc+
                      cp_OffPerf7:cln_PairCA+
                      (1 | NAICS3/NAICS6/ServArea)+  
                      (1 | Agency/Office) +
                      (1 | Place)+ 
                      (1 | StartFY),
                    verbose=TRUE)
  
  save(n_CBre25A,file="..\\output\\n_CBre25A.rda")
}


glmer_examine(n_CBre25A)

# if(!exists("b_CBre29B_restart")){
#   pars<-get_pars(b_CBre25A)
#   b_CBre25A_restart <- update(b_CBre25A, 
#                                      start=pars,
#                                      verbose=1)
#   save(b_CBre25A,
#        b_CBre25A_restart,
#        file="..//output//b_CBre25A.rdata")
# }
# glmer_examine(b_CBre25A_restart)



# 
# save(b_CBre25A,
#      b_CBre25A.devfun,
#      CBre_Cons_13_scgrad,
#      b_CBre25A.restart,
#      CBre_Comp_13B,
#      CBre_Comp_13B.devfun,
#      CBre_Comp_13B.restart,
#      file="..//output//b_CBre25A.rdata")

# source(system.file("utils", "allFit.R", package="lme4"))
# b_CBre25A.all <- allFit(b_CBre25A)
# b_CBre25A_ss_cons <- summary(b_CBre25A.all)



# glmer_examine(b_CBre25A.restart,display=TRUE)
# odds_ratio(b_CBre25A.restart,"b_CBre25A")

```
"Model failed to converge with max|grad| = 0.00135328 (tol = 0.001, component 1)"" - AllOpt25A


### Termination

```{r Model-Term}
if(file.exists("..//Output//term25B.rdata")) load("..//Output//term25B.rdata")

if(!exists("term25B")){

  term25B <- glmer(data=serv_smp1m, b_Term ~ cl_US6_avg_sal_lag1Const + 
                     cl_CFTE+ c_pPBSC+c_pOffPSC+
                     c_pairHist+cl_pairCA +
                     cl_Base + cl_Days+ cl_Base2Ceil+
                     Comp1or5+
                     Veh+
                     PricingUCA+
                     Crisis+
                     cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                     cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                     c_pMarket+
                     cl_OffVol+cl_office_naics_hhi_k +
                     c_pairHist:PricingUCA+ 
                     (1 | NAICS3/NAICS/CrisisProductOrServiceArea)+  
                     (1 | Agency/Office) +
                     (1 | PlaceCountryISO3)+ 
                     (1 | StartFY),
                   family=binomial(link="logit"),
                   verbose=TRUE)
  
  save(term25A,term25B,file="..\\output\\term25AB.rdata")
}

glmer_examine(term25B)

```

### Study Variables Only
```{r StudyVariableSummary}

texreg::htmlreg(list(p_Opt_12C,b_CBre12C_1m,term25B),file="..//Output//study_var_model_lvl1.html",
                single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                #groups = list(
                 #             "Services Complexity" = 2:3,
                  #            "Office Capacity" =4:5,
                   #           "Past Relationship"=6:7
                    #          ),
                custom.coef.map=study_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 6: Study Variables and Outcomes",
                caption.above=TRUE)

```


### All Level 1 Variables

```{r AllVariableSummary}

#Absolute Exercised Options
  stargazer::stargazer(#p_Opt_12C,
                       b_CBre12C_1m,term25B,
                       single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(p_Opt_12C,b_CBre12C_1m,term25B),file="..//Output//all_var_model_lvl1.html",
                single.row = TRUE,
                custom.model.name=c("Exercised Option","Ceiling Breach","Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                              "Services Complexity" = 2:3,
                              "Office Capacity" =4:5,
                              "Past Relationship"=6:7,
                              "Contract Characteristics"=8:25,
                              "NAICS Characteristics" =26:29,
                                                            "Office Characteristics" =30:32
                              
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 7: All Variables and Outcomes",
                caption.above=TRUE)



```
## Results by Dependent Variable

### Exercised Options
```{r OptionsTableGeneration}
#MODELS - b_SomeOpt25Cv3; b_AllOpt26A

stargazer::stargazer(b_SomeOpt25Cv3, b_AllOpt26A,
                       single.row = TRUE,
                custom.model.name=c("Exercised Options"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)

#Chart for report:

texreg::htmlreg(list(b_SomeOpt25Cv3, b_AllOpt26A),file="..//Output//options.html",
                single.row = TRUE,
                custom.model.name=c("Some Options Exercised Model", "All Options Exercised Model"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                  "Study Variables" = 2:7,
                  # "Services Complexity" = 2:3,
                  # "Office Capacity" =4:5,
                  # "Past Relationship"=6:7,
                  # "Past Relationship"=6:7,
                  "Contract Characteristics"=8:26,
                  "NAICS/Office Characteristics" =27:33,
                  # "NAICS Characteristics" =27:30,
                  # "Office Characteristics" =31:33,
                  "Interactions"=34:52
                ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 6: Exercised Options",
                caption.above=TRUE)
?


```

### Ceiling Breach
```{r CeilingResults}

  stargazer::stargazer(#p_Opt_12C,
                       b_CBre29B,n_CBre25A,
                       single.row = TRUE,
                custom.model.name=c("Breach Frequency (Logit)","Breach Size for Breached Contracts (Regression"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(b_CBre29B,n_CBre25A),file="..//Output//ceiling_breaches.html",
                single.row = TRUE,
                custom.model.name=c("Likelihood\n(Logit)","Size Given Breach\n(Regression)"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                                                "Study Variables" = 2:7,
                              # "Services Complexity" = 2:3,
                              # "Office Capacity" =4:5,
                              # "Past Relationship"=6:7,
                              "Contract Characteristics"=8:26,
                                                "NAICS/Office Characteristics" =27:32,
                              "Interactions"=33:34
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 8: Ceiling Breaches",
                caption.above=TRUE)



```

### Terminations

```{r AllVariableSummary}

#Absolute Exercised Options
  stargazer::stargazer(#p_Opt_12C,
                       term25B,
                       single.row = TRUE,
                custom.model.name=c("Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                       type="text",
                       digits=2)


texreg::htmlreg(list(term25B),file="..//Output//terminations.html",
                single.row = TRUE,
                custom.model.name=c("Termination"),
                stars=c(0.1,0.05,0.01,0.001),
                groups = list(
                              "Study Variables" = 2:7,
                              "Contract Characteristics"=8:26,
                              "NAICS Characteristics" =27:30,
                              "Office Characteristics" =31:33,
                              "Interactions"=34:39
                              ),
                custom.coef.map=all_coef_list,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 10: Terminations",
                caption.above=TRUE)



```




## Odds Ratios

### Exercised Options
```{r Odds-Opt}


# comp.or<-odds_ratio(b_CBre29B,"b_CBre29B","Both","Both")
# write.csv(get_study_variables_odds_ratio(comp.or),file="..//output//ceiling_breach_study_odds_ratio.csv",row.names=FALSE)
# get_icc(b_CBre29B)
# 
# #https://www.lcampanelli.org/mixed-effects-modeling-lme4/
# gridExtra::grid.arrange(dotplot(ranef(b_CBre29B, condVar = T), strip = T, scales=list(relation='free'))$Agency,
#              nrow=1)

comp.or<-odds_ratio(b_SomeOpt25Cv3,"b_SomeOpt25Cv3",output = "Some Options Exercised Likelihood", walds = TRUE, rename_list=all_coef_list)
write.csv(get_study_variables_odds_ratio(comp.or, study = "services"),file="..//output//some_exer_opt_study_odds_ratio.csv",row.names=FALSE)
get_icc(b_SomeOpt25Cv3)

# #https://www.lcampanelli.org/mixed-effects-modeling-lme4/
# gridExtra::grid.arrange(dotplot(ranef(b_SomeOpt25A, condVar = T), strip = T, scales=list(relation='free'))$Agency,
#              nrow=1)

comp.or<-odds_ratio(b_AllOpt26A,"b_AllOpt26A",output = "All Options Exercised Likelihood", walds = TRUE, rename_list=all_coef_list)
write.csv(get_study_variables_odds_ratio(comp.or, study = "services"),file="..//output//all_exer_opt_study_odds_ratio.csv",row.names=FALSE)
get_icc(b_AllOpt26A)

```

### Ceiling Breach 
```{r Odds-Term}
# comp_or<-odds_ratio(b_CBre29B,output="Breach Likelihood",rename_list=all_coef_list)
  comp_or_walds<-odds_ratio(b_CBre29B,"b_CBre29B",output="Breach Likelihood",walds=TRUE,rename_list=all_coef_list)
# save(comp.or,file="..//Output//comp.or.rdata")
write.csv(get_study_variables_odds_ratio(comp_or_walds,study="services"),file="..//output//ceiling_breach_study_odds_ratio_walds.csv",row.names=FALSE)
get_icc(b_CBre29B)

#https://www.lcampanelli.org/mixed-effects-modeling-lme4/
# gridExtra::grid.arrange(dotplot(ranef(b_CBre29B, condVar = T), strip = T, scales=list(relation='free'))$Agency,
#              nrow=1)


```


### Terminations 

```{r Odds-Term}


  term_or_walds<-odds_ratio(term25B,"term25B",output="Termination Likelihood",walds=TRUE,rename_list=all_coef_list)
# save(term.or,file="..//Output//term.or.rdata")
write.csv(get_study_variables_odds_ratio(term_or_walds,study="services"),file="..//output//termination_study_odds_ratio_walds.csv",row.names=FALSE)
get_icc(term25B)


# gridExtra::grid.arrange(dotplot(ranef(term25B, condVar = T), strip = T, scales=list(relation='free'))$Agency,
#              nrow=1)
# dotplot(ranef(term25B, condVar = T), strip = T, scales=list(relation='free'))$NAICS3
 

```


## Discussion by Study Variable
### Service Complexity
```{r CeilingResults}

complex_coef<-all_coef_list[c(grep("cln_US6sal",names(all_coef_list)),
                              grep("cl_US6_avg_sal_lag1Const",names(all_coef_list)),
                              grep("cl_CFTE",names(all_coef_list)),
                              grep("cln_PSCrate",names(all_coef_list))
                              )]
                              

texreg::htmlreg(list(b_SomeOpt25Cv3,b_AllOpt26A,b_CBre29B,n_CBre25A,term25B),file="..//Output//service_complexity.html",
                single.row = TRUE,
                custom.model.name=c("Some Options\nExercised\n(Logit)",
                                    "All Options\nExercised\n(Logit)",
                                    "Ceiling Breach\nLikelihood\n(Logit)",
                                    "Ceiling Breach\nSize Given Breach\n(Regression)",
                                    "Termination\n(Logit)"),
                stars=c(0.1,0.05,0.01,0.001),
                # groups = list(
                #               "Services Complexity" = 1:2,
                #               # "Office Capacity" =4:5,
                #               # "Past Relationship"=6:7,
                #   # "Services Complexity"=2:7,
                #               # "Contract Characteristics"=8:26,
                #                                 # "NAICS/Office Characteristics" =27:31,
                # 
                #               # "NAICS Characteristics" =27:29,
                #               # "Office Characteristics" =30:31,
                #               "Interactions"=3:4
                #               ),
                custom.coef.map=complex_coef,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 9: Ceiling Breaches",
                caption.above=TRUE)



```


### Office Capacity
```{r CeilingResults}


office_coef<-all_coef_list[sort(unique(c(grep("c_pPBSC",names(all_coef_list)),
                              grep("cp_OffPerf7",names(all_coef_list)),
                              grep("c_pOffPSC",names(all_coef_list)),
                              grep("pOffPSC",names(all_coef_list)),
                              grep("cp_OffPSC7",names(all_coef_list))
                              )))]
                              

texreg::htmlreg(list(b_SomeOpt25Cv3,b_AllOpt26A,b_CBre29B,n_CBre25A,term25B),
                file="..//Output//office_capacity.html",
                single.row = TRUE,
                custom.model.name=c("Some Options\nExercised\n(Logit)",
                                    "All Options\nExercised\n(Logit)",
                                    "Ceiling Breach\nLikelihood\n(Logit)",
                                    "Ceiling Breach\nSize Given Breach\n(Regression)",
                                    "Termination\n(Logit)"),
                stars=c(0.1,0.05,0.01,0.001),
                # groups = list(
                #               "Services Complexity" = 1:2,
                #               # "Office Capacity" =4:5,
                #               # "Past Relationship"=6:7,
                #   # "Services Complexity"=2:7,
                #               # "Contract Characteristics"=8:26,
                #                                 # "NAICS/Office Characteristics" =27:31,
                # 
                #               # "NAICS Characteristics" =27:29,
                #               # "Office Characteristics" =30:31,
                #               "Interactions"=3:4
                #               ),
                custom.coef.map=office_coef,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 10: Office Capacity",
                caption.above=TRUE)



```



### Partner History
```{r CeilingResults}


pair_coef<-all_coef_list[sort(c(grep("c_pairHist",names(all_coef_list)),
                              grep("cn_PairHist7",names(all_coef_list)),
                              grep("cl_pairCA",names(all_coef_list)),
                              grep("cln_PairCA",names(all_coef_list))
                              ))]
                              

texreg::htmlreg(list(b_SomeOpt25Cv3,b_AllOpt26A,b_CBre29B,n_CBre25A,term25B),
                file="..//Output//pair_history.html",
                single.row = TRUE,
                custom.model.name=c("Some Options\nExercised\n(Logit)",
                                    "All Options\nExercised\n(Logit)",
                                    "Ceiling Breach\nLikelihood\n(Logit)",
                                    "Ceiling Breach\nSize Given Breach\n(Regression)",
                                    "Termination\n(Logit)"),
                stars=c(0.1,0.05,0.01,0.001),
                # groups = list(
                #               "Services Complexity" = 1:2,
                #               # "Office Capacity" =4:5,
                #               # "Past Relationship"=6:7,
                #   # "Services Complexity"=2:7,
                #               # "Contract Characteristics"=8:26,
                #                                 # "NAICS/Office Characteristics" =27:31,
                # 
                #               # "NAICS Characteristics" =27:29,
                #               # "Office Characteristics" =30:31,
                #               "Interactions"=3:4
                #               ),
                custom.coef.map=pair_coef,
                bold=0.05,
                custom.note="%stars. Numerical inputs are rescaled.",
                caption="Table 11: Past Relationship",
                caption.above=TRUE)



```


## Residuals Plot


```{r Residuals, fig.width=7.5 , fig.height=8.5}
 
(
options_residual<-gridExtra::grid.arrange(
  binned_fitted_versus_residuals(b_SomeOpt25Cv3,bins=50)+
      labs(title="Some Options Binned Actuals",
           caption=NULL,
            x="Estimated Pr(Some Options)",y="Actual Pr(Some Options)"),
    residuals_binned(b_SomeOpt25Cv3, bins=50)+labs(title="Some Options Binned Residuals",
                                                  x="Estimated Pr(Some Options)",y="Residuals"),
    
    
    binned_fitted_versus_residuals(b_AllOpt26A,bins=50)+
      labs(title="All Options Binned Actuals",
           caption=NULL,
           x="Estimated Pr(All Options | Some Options)",y="Actual Pr(All Options | Some Options)"),
  residuals_binned(b_AllOpt26A, bins=50)+labs(title="All Options Binned Residuals",
                                                  x="Estimated Pr(All Options | Some Options)",
                                              y="Residuals"),
    ncol=2)
)

ggsave(options_residual,file="..//output//opt_residual.png",width=6.5*1.2, height=8*1.2)


(
  ceiling_breach_residual<-gridExtra::grid.arrange(
    binned_fitted_versus_residuals(b_CBre29B,bins=50)+
      labs(title="Ceiling Breach Likelihood Binned Actuals",caption=NULL,
           x="Estimated Pr(Breach)",y="Actual Pr(Breach)"),
    residuals_binned(b_CBre29B, bins=50)+labs(title="Ceiling Breach Binned Residual",
                                              x="Estimated Pr(Breach)",y="Residuals"),
    binned_fitted_versus_residuals(n_CBre25A,bins=50)+
      labs(title="Ceiling Breach Likelihood Actuals",caption=NULL,
           x="Estimated Mean(Log(Breach Size) | Breach)",y="Actual Mean(Log(Breach Size) | Breach)"),
    resid_plot(n_CBre25A,sample=25000)+labs(title="Sample of 25,000 Breach Size Residuals",
                                            x="Estimated Log(Breach Size) | Breach")
  )
)
ggsave(ceiling_breach_residual,file="..//output//cbre_residual.png",width=6.5*1.2, height=8*1.2)



(
  terminations_residual<-gridExtra::grid.arrange(
    binned_fitted_versus_residuals(term25B,bins=100)+
      labs(title="Terminations Binned Actuals",caption=NULL,
           x="Estimated Pr(Terminations)",y="Actual Pr(Terminations)"),
    residuals_binned(term25B, bins=100)+labs(title="Terminations Binned Residual"),
    ncol=2
    )
)
  ggsave(terminations_residual,file="..//output//term_residual.png",width=6.5*1.2, height=4*1.2)

 

``` 
