---
title: "Testing Interaction Terms for Contract Terminations"
output: html_document
---

#Setup
```{r Libraries, echo = FALSE}
library(csis360)
library(ggplot2)
library(arm)
library(R2WinBUGS)
library(dplyr)
library(Hmisc)
library(stargazer)
library(dummies)
library(optimx)
source("https://raw.githubusercontent.com/CSISdefense/Vendor/master/Scripts/DIIGstat.r")
axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12
main.text.size<-1
note.text.size<-1.40
```

##Load Data
First we load the data. The dataset used is a U.S. Defense Contracting dataset derived from FPDS.

```{r ReadInData, echo = TRUE}
load("~/Services/data/clean/def_sample.Rdata")
```

## Study Variables Alone

```{r StudyVariableAlone}
 # !is.na(def_serv$cl_US6_avg_sal_lag1)&
 #  !is.na(def_serv$cl_CFTE)&
 #  !is.na(def_serv$c_pPBSC)&
 #  !is.na(def_serv$c_pOffPSC)&
 #  !is.na(def_serv$c_pairHist)&
 #  !is.na(def_serv$cl_pairCA)&
study_coef_list<-list("(Intercept)"="(Intercept)",
                      "cl_US6_avg_sal_lag1Const"="Log(Det. Ind. Salary)",
                      "cl_CFTE"="Log(Service Invoice Rate)",
                      "c_pPBSC"="Office Perf.-Based %",
                      "c_pOffPSC"="Office Service Exp. %",
                      "c_pairHist"="Paired Years",
                      "cl_pairCA"="Log(Paired Actions)"
)
all_coef_list<-list("(Intercept)"="(Intercept)",
                    "cl_US6_avg_sal_lag1Const"="Log(Det. Ind. Salary)",
                    "cl_CFTE"="Log(Service Invoice Rate)",
                    "c_pPBSC"="Office Perf.-Based %",
                    "c_pOffPSC"="Office Service Exp. %",
                    "c_pairHist"="Paired Years",
                    "cl_pairCA"="Log(Paired Actions)",
                    
                    #Contract Controls
                    
                    "Comp1or51 offer"="Comp=1 offer",
                    "Comp1or52-4 offers"="Comp=2-4 offers",
                    "Comp1or55+ offers"="Comp=5+ offers",
                    
                    "CompOffr1 offer"="Comp=1 offer",
                    "CompOffr2 offers"="Comp=2 offers",
                    "CompOffr3-4 offers"="Comp=3-4 offers",
                    "CompOffr5+ offers"="Comp=5+ offers",
                    
                    "cl_Ceil"="Log(Init. Ceiling)",
                    "capped_cl_Days"="Log(Init. Days)",
                    "VehS-IDC"="Vehicle=S-IDC",
                    "VehM-IDC"="Vehicle=M-IDC",
                    "VehFSS/GWAC"="Vehicle=FSS/GWAC",
                    "VehBPA/BOA"="Vehicle=BPA/BOA",
                    "PricingUCAFFP"="Pricing=FFP",
                    "PricingUCAOther FP"="Pricing=Other FP",
                    "PricingUCAIncentive"="Pricing=Incentive Fee",
                    "PricingUCACombination or Other"="Pricing=Combination or Other",
                    "PricingUCAOther CB"="Pricing=Other CB",
                    "PricingUCAT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
                    "PricingUCAUCA"="Pricing=UCA",
                    
                    "PricingFeeOther FP"="Pricing=Other FP",
                    "PricingFeeIncentive"="Pricing=Incentive Fee",
                    "PricingFeeCombination or Other"="Pricing=Combination or Other",
                    "PricingFeeOther CB"="Pricing=Other CB",
                    "PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE",
                    "b_UCA"="UCA",
                    "CrisisARRA"="Crisis=ARRA",
                    "CrisisDis"="Crisis=Disaster",
                    "CrisisOCO"="Crisis=OCO",
                    "b_Intl"="Performed Abroad",
                    #NAICS
                    "cl_def3_HHI_lag1"="Log(Subsector HHI)",
                    "cl_def6_HHI_lag1"="Log(Det. Ind. HHI)",
                    "cl_def3_ratio_lag1"="Log(Subsector Ratio)",
                    "cl_def6_obl_lag1"="Log(Det. Ind. DoD Obl.)",
                    "cl_def6_ratio_lag1"="Log(Det. Ind. Ratio)",
                    #Office
                    "c_pMarket"="Percent Market",
                    "cl_OffVol"="Office Volume",
                    "cl_office_naics_hhi_k"="Office Concentration",
                    
                    
                    #interations
                    # # "cl_def6_HHI_lag1:capped_cl_Days"="Log(Det. Ind. HHI):Log(Init. Days)",
                    # "cl_def6_HHI_lag1:cl_def6_obl_lag1"="Log(Det. Ind. HHI):Log(Det. Ind. DoD Obl.)",
                    # # "cl_def3_HHI_lag1:cl_def3_ratio_lag1"="Log(Subsector HHI):Log(Subsector Ratio)"),
                    "cl_def6_HHI_lag1:b_UCA"="Log(Det. Ind. HHI):UCA",
                    # "cl_Ceil:b_UCA"="Log(Init. Ceiling):UCA",
                    # "CompOffr1 offer:b_UCA"="Comp=1 offer:UCA",
                    # "CompOffr2 offers:b_UCA"="Comp=2 offers:UCA",
                    # "CompOffr3-4 offers:b_UCA"="Comp=3-4 offers:UCA",
                    # "CompOffr5+ offers:b_UCA"="Comp=5+ offers:UCA"
                    "VehS-IDC:b_Intl"="Vehicle=S-IDC:Performed Abroad",
                    "VehM-IDC:b_Intl"="Vehicle=M-IDC:Performed Abroad",
                    "VehFSS/GWAC:b_Intl"="Vehicle=FSS/GWAC:Performed Abroad",
                    "VehBPA/BOA:b_Intl"="Vehicle=BPA/BOA:Performed Abroad",
                    "cl_US6_avg_sal_lag1:PricingFeeOther FP"="Pricing=Other FP:Log(Det. Ind. U.S. Avg. Salary)",
                    "cl_US6_avg_sal_lag1:PricingFeeIncentive"="Pricing=Incentive Fee:Log(Det. Ind. U.S. Avg. Salary)",
                    "cl_US6_avg_sal_lag1:PricingFeeCombination or Other"="Pricing=Comb./or Other:Log(Det. Ind. U.S. Avg. Salary)",
                    "cl_US6_avg_sal_lag1:PricingFeeOther CB"="Pricing=Other CB:Log(Det. Ind. U.S. Avg. Salary)",
                    "cl_US6_avg_sal_lag1:PricingFeeT&M/LH/FPLOE"="Pricing=T&M/LH/FP:LoE:Log(Det. Ind. U.S. Avg. Salary)"
)
```

####Cumulative Non-Interaction Model
```{r Model13B}
#Model
Term_13B <- glm(data=serv_smp,
                 b_Term ~  cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + cl_Base2Ceil)
glmer_examine(Term_13B)
```

####15A: Average U.S. Salaries (logged):Contract Pricing
```{r}
#Create the models
term_salary_pricing_15A_no_interact <- glm(data=serv_smp, b_Term ~ PricingUCA + cl_US6_avg_sal_lag1)
glmer_examine(term_salary_pricing_15A_no_interact)

term_salary_pricing_15A <- glm(data=serv_smp, b_Term ~ PricingUCA + cl_US6_avg_sal_lag1 + PricingUCA:cl_US6_avg_sal_lag1)
glmer_examine(term_salary_pricing_15A)


#compare the models

stargazer::stargazer(term_salary_pricing_15A_no_interact, term_salary_pricing_15A, type="text", digits=2)

summary_residual_compare(term_salary_pricing_15A_no_interact, term_salary_pricing_15A, bins=5)
```

####15B: Cumulative
```{r}
#Create the model
term_salary_pricing_15B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + PricingUCA:cl_US6_avg_sal_lag1)

#Compare the models
stargazer::stargazer(term_salary_pricing_15B, Term_13B, type="text", digits=2)

summary_residual_compare(term_salary_pricing_15B, Term_13B, bins=5)

```

####16A: Office Partnership:Actions
```{r}
#Create the models
term_partnership_actions_16A_no_interact <- glm(data=serv_smp, b_Term ~ c_pPBSC + cl_pairCA)
glmer_examine(term_partnership_actions_16A_no_interact)

term_partnership_actions_16A <- glm(data=serv_smp, b_Term ~ c_pPBSC + cl_pairCA + c_pPBSC:cl_pairCA)
glmer_examine(term_partnership_actions_16A)


#compare the models

stargazer::stargazer(term_partnership_actions_16A_no_interact, term_partnership_actions_16A, type="text", digits=2)

summary_residual_compare(term_partnership_actions_16A_no_interact, term_partnership_actions_16A, bins=5)

```

####16B: Cumulative
```{r}
#Create the model
term_partnership_actions_16B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + c_pPBSC:cl_pairCA)

#Compare the models
stargazer::stargazer(term_partnership_actions_16B, Term_13B, type="text", digits=2)

summary_residual_compare(term_partnership_actions_16B, Term_13B, bins=5)
```

####17A: Office Partnership:Market Vendor Share for that Office
```{r}
#Define the models
term_partnership_share_17A_no_interact <- glm(data=serv_smp, b_Term ~ c_pPBSC + c_pMarket)
glmer_examine(term_partnership_share_17A_no_interact)

term_partnership_share_17A <- glm(data=serv_smp, b_Term ~ c_pPBSC + c_pMarket + c_pPBSC:c_pMarket)
glmer_examine(term_partnership_share_17A)

#Compare the models
stargazer::stargazer(term_partnership_share_17A_no_interact, term_partnership_share_17A, type="text", digits=2)

summary_residual_compare(term_partnership_share_17A_no_interact, term_partnership_share_17A, bins=5)
```

####17B: Cumulative
```{r}
#Create the model
term_partnership_share_17B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + c_pPBSC:c_pMarket)

#Compare the models
stargazer::stargazer(term_partnership_share_17B, Term_13B, type="text", digits=2)

summary_residual_compare(term_partnership_share_17B, Term_13B, bins=5)
```

####18A: Office Partnership:Initial Contract Duration (logged)
```{r}
#Create the Model
term_partnership_duration_18A_no_interact <- glm(data=serv_smp , b_Term ~ c_pPBSC + capped_cl_Days)
glmer_examine(term_partnership_duration_18A_no_interact)

term_partnership_duration_18A <- glm(data=serv_smp, b_Term ~ c_pPBSC + capped_cl_Days + c_pPBSC: capped_cl_Days)
glmer_examine(term_partnership_duration_18A)

#Compare the models
stargazer::stargazer(term_partnership_duration_18A_no_interact, term_partnership_duration_18A, type="text", digits=2)

summary_residual_compare(term_partnership_duration_18A_no_interact, term_partnership_duration_18A, bins=5)
```

####18B: Cumulative
```{r}
#Create the model
term_partnership_duration_18B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + c_pPBSC:capped_cl_Days)

#Compare the models
stargazer::stargazer(term_partnership_duration_18B, Term_13B, type="text", digits=2)

summary_residual_compare(term_partnership_duration_18B, Term_13B, bins=5)
```

####19A: Past Years:Contract Pricing
```{r}
#Create the models
term_history_pricing_19A_no_interact <- glm(data=serv_smp, b_Term ~ c_pairHist + PricingUCA)
glmer_examine(term_history_pricing_19A_no_interact)

term_history_pricing_19A <- glm(data=serv_smp, b_Term ~ c_pairHist + PricingUCA + c_pairHist:PricingUCA)
glmer_examine(term_history_pricing_19A)

#Compare the models
stargazer::stargazer(term_history_pricing_19A_no_interact, term_history_pricing_19A, type="text", digits=2)

summary_residual_compare(term_history_pricing_19A_no_interact, term_history_pricing_19A, bins=5)
```

####19B: Cumulative
```{r}
#Create the model
term_history_pricing_19B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + c_pairHist:PricingUCA)

#Compare the models
stargazer::stargazer(term_history_pricing_19B, Term_13B, type="text", digits=2)

summary_residual_compare(term_history_pricing_19B, Term_13B, bins=5)
```

####20A: Competition:NAICS Detailed Industry (Level 6)
```{r}
#Create the models
term_competition_naics_20A_no_interact <- glm(data=serv_smp, b_Term ~ Comp1or5 + cl_def6_HHI_lag1)
glmer_examine(term_competition_naics_20A_no_interact)

term_competition_naics_20A <- glm(data=serv_smp, b_Term ~ Comp1or5 + cl_def6_HHI_lag1 + Comp1or5:cl_def6_HHI_lag1)
glmer_examine(term_competition_naics_20A)

#Compare the models
stargazer::stargazer(term_competition_naics_20A_no_interact, term_competition_naics_20A, type="text", digits=2)

summary_residual_compare(term_competition_naics_20A_no_interact, term_competition_naics_20A, bins=5)
```

####20B: Cumulative
```{r}
#Create the model
term_competition_naics_20B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + Comp1or5:cl_def6_HHI_lag1)

#Compare the models
stargazer::stargazer(term_competition_naics_20B, Term_13B, type="text", digits=2)

summary_residual_compare(term_competition_naics_20B, Term_13B, bins=5)
```

####21A: Ratio Initial Base to Ceiling Ratio (logged):Initial Contract Ceiling (logged)
```{r}
#Create the models
term_base2ceil_ceiling_21A_no_interact <- glm(data=serv_smp, b_Term ~ cl_Base2Ceil + cl_Ceil)
glmer_examine(term_base2ceil_ceiling_21A_no_interact)

term_base2ceil_ceiling_21A <- glm(data=serv_smp, b_Term ~ cl_Base2Ceil + cl_Ceil + cl_Base2Ceil:cl_Ceil)
glmer_examine(term_base2ceil_ceiling_21A)

#Compare the Models
stargazer::stargazer(term_base2ceil_ceiling_21A_no_interact, term_base2ceil_ceiling_21A, type="text", digits=2)

summary_residual_compare(term_base2ceil_ceiling_21A_no_interact, term_base2ceil_ceiling_21A, bins=5)
```

####21B: Cumulative
```{r}
#Create the model
term_base2ceil_ceiling_21B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + cl_Base2Ceil:cl_Ceil)

#Compare the models
stargazer::stargazer(term_base2ceil_ceiling_21B, Term_13B, type="text", digits=2)

summary_residual_compare(term_base2ceil_ceiling_21B, Term_13B, bins=5)
```

####22A: Available Options:Initial Contract Duration (logged)
```{r}
term_base2ceil_duration_22A_no_interact <- glm(data=serv_smp, b_Term ~ cl_Base2Ceil + capped_cl_Days)
glmer_examine(term_base2ceil_duration_22A_no_interact)

term_base2ceil_duration_22A <- glm(data=serv_smp, b_Term ~ cl_Base2Ceil + capped_cl_Days + cl_Base2Ceil:capped_cl_Days)
glmer_examine(term_base2ceil_duration_22A)

#Compare the Models
stargazer::stargazer(term_base2ceil_duration_22A_no_interact, term_base2ceil_duration_22A, type="text", digits=2)

summary_residual_compare(term_base2ceil_duration_22A_no_interact, term_base2ceil_duration_22A, bins=5)
```

####22B: Cumulative
```{r}
#Create the model
term_base2ceil_duration_22B <- glm(data=serv_smp, b_Term ~ cl_US6_avg_sal_lag1Const + 
                   cl_CFTE+ c_pPBSC+c_pOffPSC+
                 c_pairHist+cl_pairCA +
                   cl_Ceil + capped_cl_Days+
                   Comp1or5+
                   Veh+
                   PricingUCA+
                   Crisis+
                   cl_def6_HHI_lag1+cl_def6_ratio_lag1+
                   cl_def3_HHI_lag1+cl_def3_ratio_lag1+
                   c_pMarket+
                   cl_OffVol+cl_office_naics_hhi_k + cl_Base2Ceil:capped_cl_Days)

#Compare the models
stargazer::stargazer(term_base2ceil_duration_22B, Term_13B, type="text", digits=2)

summary_residual_compare(term_base2ceil_duration_22B, Term_13B, bins=5)
```
